### 2016-06-24 papers/hrr-paper/paper.tex
Fixed initial commit to add folder content

%% bare_conf.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

\documentclass[conference]{IEEEtran}
% Some Computer Society conferences also require the compsoc mode option,
% but others use the standard conference format.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

\usepackage{subcaption}

% *** CITATION PACKAGES ***
%
\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
\usepackage{amsmath}
\usepackage{mathabx}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

%\usepackage{asmfonts}

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Semantic Holographic Memories}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Igor Peric, Stefan Ulbrich, Alexandru Lesi, R{\"u}diger Dillman, Marius Z{\"o}llner}
\IEEEauthorblockA{FZI Forschungszentrum Informatik\\
Karlsruhe, Germany\\
Email: $\{$peric, ulbrich, dillmann, zoellner$\}$@fzi.de}
}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Vector Symbolic Architectures (VSA) define a set of operations for storage (compression), manipulation and retrieval of symbolic concepts, represented as fixed-length vectors. A specific instance of VSA, Holographic Reduced Representations (HRR), has proven to exhibit properties similar to human short-term memory and is, as such, interesting for computational modeling.

In this paper we extend HRR approach by introducing topology-preserving, invertible encoding/decoding procedure for all major data types used in robotics and engineering. These encoding schemes play the role of otherwise used clean-up modules after memory retrieval (e.g. self-organizing maps), thus eliminating necessity for them.

We test our memories in three different robotic tasks: mapping and recall, visual object classification and state machine scripting (holographic controllers).
\end{abstract}

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}

Vector Symbolic Architectures (VSA) define a set of operations for storage (compression) and retrieval of symbolic concepts in fixed size vectors. In its basic form every VSA has to implement three basic operations:
\begin{enumerate}
\item association (binding) $\mapsto \otimes$
\item superposition (appending) $\mapsto +$
\item probing (unbinding) $\mapsto \oslash$
\end{enumerate}

In addition, every VSA can be considered as a compression technique, since binary operations on N-element vectors return N-element vectors as well.

\textbf{Association} (also called "binding") is operation of linking two operands together, resulting in a vector of same size which is dissimilar (orthogonal) to both original vectors, but contains scrambled information from both of the operands. For instance, linking property "red" to object "triangle" can be done using binding operation:

\begin{equation}
memory_1 = red \otimes triangle
\end{equation}

\textbf{Superposition} is operation of extending a set of already memorized items with another item (or binding of two or more of them). As an example, a memory of "red triangle and blue circle" can be formed in following way:
\begin{equation}
memory_2 = memory_1 + blue \otimes circle
\end{equation}

\textbf{Probing} is operation of extracting a noisy version of associated item from a joint set memory. I.e. a question "What is the color of triangle?" could be asked like this:

\begin{equation}
red \approx memory_2 \oslash triangle
\end{equation}

Probing operation assumes existence of inverse element to association, so previous equation can be interpreted and explained in following way:
\begin{multline}
memory_2 \otimes triangle'=\\
(red \otimes triangle + blue \otimes circle) \otimes triangle'=\\
red \otimes triangle  \otimes triangle' + blue \otimes circle \otimes triangle' =\\
red + blue \otimes circle \otimes triangle'  = red + noise
\approx red
\end{multline}

where $triangle'$ represents inverse of $triangle$. Resulting vector will be composition of something that is very similar to $red$ and something that doesn't resemble anything meaningful from symbol table, so it can be treated as neglectable noise.

\begin{figure}
\center
\includegraphics[width=0.9\columnwidth]{img/scalar-probe.png}
\caption{Result of $(80 \otimes A) \oslash A$ for HRR from}
\end{figure}

Process of converting noisy result of probing into the closest know symbol is called \textbf{clean-up procedure}. Straightforward way of implementing clean-up memory is using lookup table, while other researchers show that any type of attractor network can be used (e.g. self-organizing maps).

\section{Holographic reduced representations}

Holographic Reduced Representations are VSAs which implement operation of binding as circular convolution:

\begin{equation}
z_i=\sum_{k=0}^{N}{x_iy_{i-k}} //TODO
\end{equation}

where $z$ is the result of convolution, $x$ and $y$ are operands of size $N$. Superposition is implemented as simple element-wise addition. Probing is implemented using inverse of circular convolution - circular correlation:

\begin{equation}
y_i=\sum_{k=0}^{m}{x_iy_{i-k}} //TODO
\end{equation}

- Implementation and building up of HRRs (similarity measures and cosine, lookup table...)

\section{Topology-preserving encoding}

- necessity (benefit of having it, querying smth that was not there)
- implementation

In order to use various types of inputs with HRRs it is necessary to encode them in vectors of fixed size. The basic approach is to generate these vectors randomly for each distinct input and store these pairs in a map. This will consequently take its toll on the space complexity and may become infeasible, depending on the type of input used. The following section presents ways to encode values in a deterministic manner, removing the need to store these, as long as decoding is robust against noise.

\subsection{Scalars}

Encoding scalars is a good example for the necessity of preserving topology. Depending on what dataset is in use it may be required to store mappings for any number of values. Furthermore, using random encoding, there would be no similarity in neighbouring values. As such the following probe will yield no result:

\begin{equation}
(10000 \otimes A) \oslash 10001
\end{equation}

To facilitate these two qualities scalar encoding can be achieved with the help of Gaussian distributions. The encoded vector will simply represent a Gaussian bell sampled over a fixed input range. Figure \ref{no-perm-a} shows how such an encoded vector looks like, and what binding such a  Unfortunately

\begin{figure}
\begin{subfigure}{1\columnwidth}
\includegraphics[width=\columnwidth]{img/scalar-pre-perm.png}
\caption{Binging}
\label{no-perm-a}
\end{subfigure}
\begin{subfigure}{1\columnwidth}
\includegraphics[width=\columnwidth]{img/scalar-pre-perm-probe.png}
\caption{Probing}
\label{no-perm-b}
\end{subfigure}
\caption{Plot of vector values. Figure \ref{no-perm-a} shows the binding of the value 8 on a scale to 10 with the symbolic representation of "ball", which is random. In figure \ref{no-perm-b} "ball" is being probed, and the expected result is a Gaussian bell for 8, mixed with some noise.}
\end{figure}

Since however circular convolution is based on Fourier transformations the lack of frequencies present in the encoding becomes apparent in Fourier space as well. All the information of a Gaussian bell is crammed into the lowest and highest values of the Fourier transformation. In these circumstances, when probing for a scalar, the vector received is in turn recreated of too few frequencies and does not come close to resembling the original Gaussian.

\begin{figure}
\includegraphics[width=\columnwidth]{img/scalar-pre-perm-fft.png}
\caption{Plot of vector values. Left plots are done without permutation, right ones are done with. Both columns represent the same operations: first row is encoding of value 8 on a scale to 10. Second is the real part of the Fourier transformation of the previously encoded vector. Final row is the result of probing for the value 8.}
\label{no-perm}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{img/scalar-perm-step.png}
\includegraphics[width=\columnwidth]{img/scalar-post-perm-fft.png}
\caption{Plot of vector values. Left plots are done without permutation, right ones are done with. Both columns represent the same operations: first row is encoding of value 8 on a scale to 10. Second is the real part of the Fourier transformation of the previously encoded vector. Final row is the result of probing for the value 8.}
\label{no-perm}
\end{figure}

This inconvenience is removed with the help of permutations. Depending on the size of the memory vectors used a fixed permutation is generated. Whenever a scalar is encoded the Gaussian bell is first sampled over the range, after which the sampled values swap places accordingly. As such the resulting vector will present lots of jumps in value, which have a significant impact on the Fourier space. Working with such a vector makes it possible to probe for scalars and receive a Gaussian bell overlapped with some noise. All of this can be seen in Figure \ref{scalar-encoder}.

\begin{figure}
\includegraphics[width=\columnwidth]{img/scalar-post-perm.png}
\includegraphics[width=\columnwidth]{img/scalar-post-perm-probe.png}
\caption{Plot of vector values. Left plots are done without permutation, right ones are done with. Both columns represent the same operations: first row is encoding of value 8 on a scale to 10. Second is the real part of the Fourier transformation of the previously encoded vector. Final row is the result of probing for the value 8.}
\label{no-perm}
\end{figure}

\subsection{Coordinate encoder}

\subsection{String encoder}

\section{Properties of SHM}

- you can't extract the items memorized, number of them, you can just query
- they are probabilistic
- you can modify them online (no separate learning/probing phases)
\subsection{Capacity}
\subsubsection{SHM size vs. number of items}
\subsubsection{Model of human forgetting}
\subsubsection{Model of intentional forgetting}

\subsection{Fan-out effect - multiple probing outputs}

\subsection{Limitations}

- introducing problem of lookup (symbol grounding)
- solution using implicit encoding and decoding

\section{Experiments}

\subsection{Visual object classification}
- SIFT + label
\subsection{Localization and mapping}
- SIFT + location
\subsection{Holographic state machines (holographic controllers)}
- sensory\_data + current\_state + next state
\subsection{Reinforcement learning}
- sensory\_data + action + reward
\subsection{Language understanding}
- TensorFlow (role) + word = question answering
\subsection{Implicit inductive reasoning}

\section{Conclusions}

% use section* for acknowledgment
\section*{Acknowledgment}

% leaving this as is.
The authors would like to thank... Manchester developers. :slowclap:

\bibliographystyle{IEEEtran}

\bibliography{IEEEabrv,bibliography}

% that's all folks
\end{document}

### 2016-06-24 hrr/gui.py

@@ -1,0 +1,4 @@
+
+class HRRVisualizer:
+
+    def 

### 2016-06-24 hrr/hrr.py

@@ -1,0 +1,335 @@
+
+import numpy as np
+import scipy as sp
+import scipy.ndimage
+from scipy.signal import argrelextrema
+from numpy.fft import fft, ifft
+from numpy.linalg import norm
+from numpy import array, sqrt, dot
+import random
+import matplotlib.pyplot as plt
+
+from vsa import VSA
+    
+class HRR(VSA):
+
+    #m = []  # memorry storage
+    mapping = {}  # list of known mappings so far
+    #sz = () # size of the storage
+    size = 20
+    verbose = True
+    
+    stddev = 0.02
+  
+    input_range = np.array([0,100])
+    permutation = {} # indexed by array size
+    
+    ### data changed callbacks
+    
+    #data_changed_callback = None
+    #def data_changed_callback_invoke():
+    #    if self.data_changed_callback != None:
+    #        self.data_changed_callback(self)
+    @classmethod
+    def set_size(self, size):
+        HRR.size = size
+        create_permutation(size)
+    
+    def __init__(self, v, size=None, memory=None):
+        
+        if size == None:
+            size = HRR.size               
+        
+        # init memory with zeros
+        self.size = size
+        self.label = v
+        
+        if memory != None:
+            self.memory = memory 
+        else :
+            self.memory = self.encode(size, v)    
+            
+        assert(self.is_normalized(self.memory))
+    
+    @classmethod
+    def reset_kernel(self):
+        HRR.mapping = {}
+        self.set_size(self.size)            
+        
+    def __add__(self, op):
+        if op.__class__ != self.__class__:
+            op = HRR(op)
+        
+        return HRR('-', memory=self.normalize(self.memory + op.memory))   
+
+    def __sub__(self, op):
+        if op.__class__ != self.__class__:
+            op = HRR(op)
+        return HRR('-', memory=self.normalize(self.memory - op.memory))        
+        
+    def __mul__(self, op):
+        if op.__class__ != self.__class__:
+            op = HRR(op)
+            
+        #perform binding
+        memory = self.circconv(self.memory, op.memory)       
+        
+        return HRR('-', memory=memory)
+    
+    def __mod__(self, op):
+        
+        if op.__class__ != self.__class__:
+            op = HRR(op)
+        
+        # perform unbinding
+        op_dec = self.periodic_corr(self.memory, op.memory)
+        
+        return HRR('-', memory=op_dec)
[…]

### 2016-06-24 hrr/test.py

@@ -1,0 +1,90 @@
+from hrr import *
+#import core
+import numpy as np
+import sys
+
+import matplotlib.pyplot as plt
+
+import cv2
+
+#a = HRR(5) * 6
+#b = HRR(1) * 2
+#k = HRR(4) * 1
+
+#c = a + b + k
+
+#print(c/1)
+
+#sys.exit()
+
+# define list of items to remember
+HRR.reset_kernel()
+HRR.set_default_size(100 * 100 * 3)
+HRR.input_range = [0, 10]
+HRR.stddev = 0.001
+
+# load images from files
+dataset = {}
+dataset[1] = 'circle-red.png'
+dataset[9] = 'circle-green.png'
+
+m = None
+for k in dataset:
+    img = cv2.imread(dataset[k])
+    img = cv2.resize(img, (100,100))
+    img_data = np.array(img).reshape(img.shape[0] * img.shape[1] * img.shape[2])
+    print(max(img_data))
+    img_data /= float(max(img_data))
+    #img_data -= 0.5
+
+    print(max(img_data))
+
+    symbol = HRR(k, memory=img_data) * k
+    if m is not None:
+        m += symbol
+    else:
+        m = symbol
+
+#features = [ "door", "tree", "car", "table", "computer" ]
+#values = [ (10,20), (90,46), (22,31), (50,1), (1,50) ]
+#m = None
+#for i in range(len(features)):
+#    if m is None:
+#        m = HRR(features[i]) * values[i]
+#    else:
+#        new_item = HRR(features[i]) * values[i]
+#        m += new_item
+
+#print("Items memorized.")
+#print(m.memory)
+
+cam = cv2.VideoCapture(0)
+
+#plt.ion()
+#fig = plt.figure()
+#ax = fig.add_subplot(1,1,1)
+while True:
+    ret, img = cam.read(0)
+    
+    rect = ((100,100),(300,300))
+    cv2.rectangle(img, rect[0], rect[1], (0,255,0), 3)
+    
+    img_crop = img[rect[0][0]:rect[1][0], rect[0][1]:rect[1][1]]
+    
+    img_probe = cv2.resize(img_crop, (100,100))
+    img_probe = np.array(img_probe).reshape(img_probe.shape[0] * img_probe.shape[1] * img_probe.shape[2])
+    
+    #print('before {} {}'.format(np.max(img_probe), np.min(img_probe)))
+    img_probe /= float(max(img_probe))
[…]

### 2016-06-24 hrr/test_coordinate_encoder.py

@@ -1,0 +1,24 @@
+from hrr import HRR
+HRR.stddev = 0.1
+HRR.input_range = [0, 10]
+
+A = 2
+B = 8
+
+Pa = [ (0,0), (1,1), (2,2), (3,3), (4,4), (5,5)]
+#Pb = [ (0,4), (1,4), (2,4), (3,4), (4,4), (5,4)]
+items = ["computer", "car", "table", "chair", "door", "book"]
+
+m = None
+for i in range(len(Pa)):
+    a = HRR(Pa[i]) * items[i]
+    #b = HRR(Pb[i]) * B
+    if m is None:
+        m = a
+    else:
+        m += a
+
+
+
+probe = HRR((1,1))
+print(m / probe)

### 2016-06-24 hrr/test_induction.py

@@ -1,0 +1,42 @@
+from hrr import HRR
+import matplotlib.pyplot as plt
+
+import numpy as np
+
+HRR.input_range = [0, 100]
+
+n = 50 # number of items stored
+
+all_rules = [0.0] * HRR.default_size
+w = 0.3
+
+rule = None
+for i in range(n):
+    A = HRR(i)
+    B = HRR(i+10)
+    T = A % B
+    T.memory = T.permute(T.memory)
+    if rule is None:
+        rule = T
+    else:
+        rule -= T
+    all_rules = all_rules - w * (all_rules - T.memory)
+
+#all_rules /= float(n)
+hrr_rule = HRR('-', memory=all_rules)
+
+#hrr_rule.memory = hrr_rule.reverse_permute(hrr_rule.memory)
+plt.figure()
+xx = range(len(hrr_rule.memory))
+plt.plot(xx, hrr_rule.memory)
+plt.show()
+
+cue = HRR(10)
+inference = cue * hrr_rule
+
+inference.memory = inference.reverse_permute(inference.memory)
+
+plt.figure()
+xx = range(len(inference.memory))
+plt.plot(xx, inference.memory)
+plt.show()

### 2016-06-24 hrr/test_path_intersection.py

@@ -1,0 +1,85 @@
+from hrr import HRR, smooth
+import matplotlib.pyplot as plt
+import numpy as np
+import cv2
+
+import os, shutil
+folder = '/Users/peric/dev/hrr/results'
+for the_file in os.listdir(folder):
+    file_path = os.path.join(folder, the_file)
+    try:
+        if os.path.isfile(file_path):
+            os.unlink(file_path)
+        #elif os.path.isdir(file_path): shutil.rmtree(file_path)
+    except Exception as e:
+        print(e)
+       
+HRR.stddev = 0.01
+HRR.input_range = [0, 10]
+HRR.default_size = 10000
+
+labels = [2, 8]
+
+path = []
+path.append([ (3,4), (4,4), (5,4), (6,4), (6,3), (6,2), (6,1), (7,1), (8,1), (8,2)])
+path.append([ (0,0), (1,1), (2,2), (3,3), (4,4), (5,5), (6,6)])
+#items = ["computer", "car", "table", "chair", "door", "book"]
+
+m = None
+m_time = None
+xx, yy = [], []
+for p in range(len(labels)):
+    print("Processing path {}...".format(p))
+    for k in range(len(path[p])):
+        print("Index {}".format(k))
+        path_representation = HRR(path[p][k]) * labels[p]
+        time_representation = HRR(path[p][k]) * labels[p] * k
+        
+        xx.extend([path[p][k][0]])
+        yy.extend([10-path[p][k][1]])
+        
+        if m is None:
+            m = path_representation
+        else:
+            m += path_representation
+        
+        if m_time is None:
+            m_time = time_representation
+        else:
+            m_time += time_representation
+            
+
+# get the intersection coordinates
+A = labels[0]
+B = labels[1]
+int_A = m % HRR(A)
+int_A.memory = int_A.reverse_permute(int_A.memory)
+int_B = m % HRR(B)
+int_B.memory = int_B.reverse_permute(int_B.memory)
+
+int_C = int_A.memory * int_B.memory
+int_C /= np.linalg.norm(int_C) 
+
+#intersection_coords.memory = intersection_coords.reverse_permute(intersection_coords.memory)
+
+plt.figure()
+xx = range(len(int_C))
+plt.plot(xx, int_C)
+plt.show()
+
+#intersection_coords.memory = intersection_coords.permute(intersection_coords.memory)
+
+# get time for path A
[…]

### 2016-06-24 hrr/vsa.py

@@ -1,0 +1,55 @@
+from abc import ABCMeta, abstractmethod
+
+class VSA:
+    
+    @abstractmethod
+    def __init__(self, v, size=None, memory=None):
+        pass    
+    
+    @abstractmethod
+    def reset_kernel(self):
+        pass    
+    
+    @abstractmethod
+    def __mul__(self, op):
+        pass   
+    
+    @abstractmethod
+    def __sub__(self, op):
+        pass   
+    
+    @abstractmethod
+    def __add__(self, op):
+        pass    
+    
+    @abstractmethod
+    def __mod__(self, op):
+        pass  
+    
+    @abstractmethod
+    def __div__(self, op):
+        pass   
+    
+    @abstractmethod
+    def encode(self, sz, op):
+        pass  
+    
+    @abstractmethod
+    def coordinate_encoder(self, x, limits_min, limits_max):
+        pass 
+    
+    @abstractmethod
+    def periodic_corr(self, x, y):
+        pass   
+    
+    @abstractmethod
+    def circconv(self, a, b):
+        pass   
+    
+    @abstractmethod
+    def compare(self,one, other):
+        pass
+    
+    @abstractmethod
+    def distance(self, one, other):
+        pass

### 2016-06-24 papers/hrr-paper/paper.tex
Completed Scalar Encoder Section in hrr-paper

@@
 The encoded vector will simply represent a Gaussian bell sampled over a fixed input range.
-Figure \ref{no-perm-a} shows how such an encoded vector looks like, and what binding such a  Unfortunately
+Figure \ref{no-perm-a} shows how such an encoded vector looks like, and what the result of binding it to a generic random vector is.
+With this result it becomes obvious that lots of information is lost.
+If this result is probed with the same random vector used in binding something similar to the initial Gaussian bell is expected.
+And yet figure \ref{no-perm-b} presents no such outcome.
+While there is a peak at the initial value lots of other peaks also arise, making it impossible to detect which one is correct.
 
@@
 In figure \ref{no-perm-b} "ball" is being probed, and the expected result is a Gaussian bell for 8, mixed with some noise.}
+\label{no-perm}
 \end{figure}
 
-Since however circular convolution is based on Fourier transformations the lack of frequencies present in the encoding becomes apparent in Fourier space as well.
+This effect is due to the fact that circular convolution is based on Fourier transformations and the lack of frequencies present in encoded vectors becomes apparent in Fourier space as well.
+Figure \ref{fft} highlights this.
 All the information of a Gaussian bell is crammed into the lowest and highest values of the Fourier transformation.
@@
 \begin{figure}
+\begin{subfigure}{1\columnwidth}
 \includegraphics[width=\columnwidth]{img/scalar-pre-perm-fft.png}
-\caption{Plot of vector values.
-Left plots are done without permutation, right ones are done with.
-Both columns represent the same operations: first row is encoding of value 8 on a scale to 10.
-Second is the real part of the Fourier transformation of the previously encoded vector.
-Final row is the result of probing for the value 8.}
-\label{no-perm}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{img/scalar-perm-step.png}
-\includegraphics[width=\columnwidth]{img/scalar-post-perm-fft.png}
-\caption{Plot of vector values.
-Left plots are done without permutation, right ones are done with.
-Both columns represent the same operations: first row is encoding of value 8 on a scale to 10.
-Second is the real part of the Fourier transformation of the previously encoded vector.
-Final row is the result of probing for the value 8.}
-\label{no-perm}
+\caption{Scalar}
+\label{fft-a}
+\end{subfigure}
+\begin{subfigure}{1\columnwidth}
+\includegraphics[width=\columnwidth]{img/scalar-random-fft.png}
+\caption{Random}
+\label{fft-b}
+\end{subfigure}
+\caption{.}
+\label{fft}
 \end{figure}
@@
 Whenever a scalar is encoded the Gaussian bell is first sampled over the range, after which the sampled values swap places accordingly.
-As such the resulting vector will present lots of jumps in value, which have a significant impact on the Fourier space.
-Working with such a vector makes it possible to probe for scalars and receive a Gaussian bell overlapped with some noise.
-All of this can be seen in Figure \ref{scalar-encoder}.
+As such the resulting vector will present lots of jumps in value, which have a significant impact on the Fourier space, as can be seen in figure \ref{perm-fft}.
 
 \begin{figure}
+\includegraphics[width=\columnwidth]{img/scalar-perm-step-fft.png}
+\caption{.}
+\label{perm-fft}
+\end{figure}
+
+Working with such a vector makes it possible to successfully probe for scalars and receive a Gaussian bell overlapped with some noise.
+All of this can be seen in figure \ref{perm}, which depicts the exact same operations as figure \ref{no-perm}, but using a permuted version of a Gaussian bell.
+The result in figure \ref{perm-b} clearly shows an according spike.
+This vector can be smoothed out, after which the peak can easily be identified and the initial scalar can be recovered.
+
+\begin{figure}
+\begin{subfigure}{1\columnwidth}
 \includegraphics[width=\columnwidth]{img/scalar-post-perm.png}
+\caption{Binging}
+\label{perm-a}
+\end{subfigure}
+\begin{subfigure}{1\columnwidth}
 \includegraphics[width=\columnwidth]{img/scalar-post-perm-probe.png}
-\caption{Plot of vector values.
-Left plots are done without permutation, right ones are done with.
-Both columns represent the same operations: first row is encoding of value 8 on a scale to 10.
-Second is the real part of the Fourier transformation of the previously encoded vector.
-Final row is the result of probing for the value 8.}
-\label{no-perm}
+\caption{Probing}
+\label{perm-b}
+\end{subfigure}
+\caption{.}
+\label{perm}
 \end{figure}

### 2016-06-24 papers/hrr-paper/paper.tex
Added Captions to Scalar Encoder graphics in hrr-paper. Added experiment for max number of correct bindings added on top of each other in hrr.

@@
 \begin{figure}
-\begin{subfigure}{1\columnwidth}
 \includegraphics[width=\columnwidth]{img/scalar-pre-perm-fft.png}
-\caption{Scalar}
-\label{fft-a}
-\end{subfigure}
-\begin{subfigure}{1\columnwidth}
 \includegraphics[width=\columnwidth]{img/scalar-random-fft.png}
-\caption{Random}
-\label{fft-b}
-\end{subfigure}
-\caption{.}
+\caption{Fourier space conversions of a Gaussian bell and a random vector.}
 \label{fft}
@@
 \includegraphics[width=\columnwidth]{img/scalar-perm-step-fft.png}
-\caption{.}
+\caption{Plots on the effect of permuting a Gaussian bell, and the impact on Fourier space.}
 \label{perm-fft}
@@
 \end{subfigure}
-\caption{.}
+\caption{Figure \ref{perm-a} shows the binding of the permuted Gaussian for value 8 on a scale to 10 with the symbolic representation of "ball", which is random.
+In figure \ref{perm-b} "ball" is being probed, and the expected result is a Gaussian bell for 8, mixed with some noise.}
 \label{perm}

### 2016-06-24 hrr/hrr.py

@@ -7,7 +7,7 @@ from numpy.fft import fft, ifft
 from numpy.linalg import norm
 from numpy import array, sqrt, dot
 import random
-import matplotlib.pyplot as plt
+#import matplotlib.pyplot as plt
 
 from vsa import VSA
     
@@ -95,8 +95,8 @@ class HRR(VSA):
         op_dec = self.periodic_corr(self.memory, op.memory) 
         #op_dec_unperm = smooth(op_dec_unperm, window_len=100)
         
-        print("Output:")
-        self.plot(op_dec)
+        #print("Output:")
+        #self.plot(op_dec)
             
         # cleanup of noisy result by dictionary lookup
         max_sim = {}
@@ -114,17 +114,17 @@ class HRR(VSA):
             if v > 0.1:
                 max_sim[k] = v
         
-        if not max_sim:       
-            print("Output Reverse:")
-            self.plot(self.reverse_permute(op_dec))
-            op_dec = smooth(self.reverse_permute(op_dec),self.size/50)  
-            print("Output Smooth:")
-            self.plot(op_dec)
-            while np.max(op_dec) > 6 * abs(np.mean(op_dec)):
-                max_sim[len(max_sim)] = int(self.reverse_scale(np.argmax(op_dec), len(op_dec)))
-                compensate = self.scalar_encoder(self.reverse_scale(np.argmax(op_dec), len(op_dec)), len(op_dec))
-                compensate[:] = [x * -abs(np.max(op_dec)) for x in compensate]     
-                op_dec += compensate      
+        #if not max_sim:       
+        #    #print("Output Reverse:")
+        #    #self.plot(self.reverse_permute(op_dec))
+        #    op_dec = smooth(self.reverse_permute(op_dec),self.size/50)  
+        #    #print("Output Smooth:")
+        #    #self.plot(op_dec)
+        #    while np.max(op_dec) > 6 * abs(np.mean(op_dec)):
+        #        max_sim[len(max_sim)] = int(self.reverse_scale(np.argmax(op_dec), len(op_dec)))
+        #        compensate = self.scalar_encoder(self.reverse_scale(np.argmax(op_dec), len(op_dec)), len(op_dec))
+        #        compensate[:] = [x * -abs(np.max(op_dec)) for x in compensate]     
+        #        op_dec += compensate      
         
         
         if HRR.verbose:
@@ -154,16 +154,16 @@ class HRR(VSA):
 
             result = np.empty(self.size, dtype=float)
          
[…]

### 2016-06-27 papers/hrr-paper/paper.tex
Added paragraph on normalization to hrr-paper

@@
 
+On a technical note it became apparent that simply sampling Gaussian bells in a vector with all the values greater zero brought up a small issue.
+Adding multiple such bindings on top of each other would constantly increase the values in the resulting vector.
+Due to this, when probing, we would receive vectors which had the correct distance between their values, i.e.
+the correct "shape", but would be shifted on the Y-axis.
+This can be solved by editing the permuted Gaussian bell to have \(\sum_{i=0}^n x_i = 0\), and is achieved with this simple operation:
+
+\[ \forall x_i \in x: x_i = x_i - \frac{\sum_{i=0}^n ||x_i||}{|x|} \]
+
 \subsection{Coordinate encoder}

### 2016-06-27 hrr/hrr.py

@@ -7,7 +7,7 @@ from numpy.fft import fft, ifft
 from numpy.linalg import norm
 from numpy import array, sqrt, dot
 import random
-#import matplotlib.pyplot as plt
+import matplotlib.pyplot as plt
 
 from vsa import VSA
     
@@ -18,6 +18,7 @@ class HRR(VSA):
     #sz = () # size of the storage
     size = 20
     verbose = True
+    visualize = False
     
     stddev = 0.02
   
@@ -48,8 +49,6 @@ class HRR(VSA):
             self.memory = memory 
         else :
             self.memory = self.encode(size, v)    
-            
-        assert(self.is_normalized(self.memory))
     
     @classmethod
     def reset_kernel(self):
@@ -60,12 +59,12 @@ class HRR(VSA):
         if op.__class__ != self.__class__:
             op = HRR(op)
         
-        return HRR('-', memory=self.normalize(self.memory + op.memory))   
+        return HRR('-', memory=self.memory + op.memory)
 
     def __sub__(self, op):
         if op.__class__ != self.__class__:
             op = HRR(op)
-        return HRR('-', memory=self.normalize(self.memory - op.memory))        
+        return HRR('-', memory=self.memory - op.memory)       
         
     def __mul__(self, op):
         if op.__class__ != self.__class__:
@@ -95,8 +94,9 @@ class HRR(VSA):
         op_dec = self.periodic_corr(self.memory, op.memory) 
         #op_dec_unperm = smooth(op_dec_unperm, window_len=100)
         
-        #print("Output:")
-        #self.plot(op_dec)
+        if self.visualize:
+            print("Output:")
+            self.plot(op_dec)
             
         # cleanup of noisy result by dictionary lookup
         max_sim = {}
@@ -114,17 +114,19 @@ class HRR(VSA):
             if v > 0.1:
                 max_sim[k] = v
         
-        #if not max_sim:       
-        #    #print("Output Reverse:")
-        #    #self.plot(self.reverse_permute(op_dec))
-        #    op_dec = smooth(self.reverse_permute(op_dec),self.size/50)  
-        #    #print("Output Smooth:")
-        #    #self.plot(op_dec)
-        #    while np.max(op_dec) > 6 * abs(np.mean(op_dec)):
-        #        max_sim[len(max_sim)] = int(self.reverse_scale(np.argmax(op_dec), len(op_dec)))
-        #        compensate = self.scalar_encoder(self.reverse_scale(np.argmax(op_dec), len(op_dec)), len(op_dec))
[…]

### 2016-06-27 hrr/legend.py
Finished two experiments for hrrs

@@ -1,0 +1,11 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+def getLegend(v,start):
+    sh = len(v)
+    linestyles = ['-', '--', '-.', ':']
+    for i in range(sh):
+        plt.plot(v[i], linestyles[3-i*4/sh], label=start*pow(2,i))
+    plt.axis([0,len(v[0]),0,1.01])
+    legend = plt.legend(loc='upper center', shadow=True, fontsize='x-large')
+    plt.show()

### 2016-11-05 vsa/hrr.py
Implemented Coordinate Encoder and Decoder

@@ -23,7 +23,8 @@ class HRR(VSA):
     permutation = {}                # List of vector permutations, indexed by vector size.
     stddev = 0.02                   # Standard deviation of gaussian bells for scalar encoders.
     incremental_weight = 0.1        # Weight used for induction.
-    peak_min = 10                   # Minimum factor by which a gaussian peak needs be larger than the average of noise.
+    peak_min = 0                    # Absolute value used to detect Gaussian peaks
+    peak_min_ratio =  10            # Minimum factor by which a gaussian peak needs be larger than the average of noise.
     window_ratio = 50		        # Ratio by which window length for smoothing is divided
     valid_range = [0,100]           # Standard valid range for scalar or coordinate encoding
     
@@ -149,22 +150,24 @@ class HRR(VSA):
             
         return VSA.decode(self, memory)
     
-    def deductValue(self, memory, value, input_range):
+    def deductValue(self, memory, value, input_range, dim = 1, height = 1):
       
         #result = self.permute(helpers.normalize(self.coordinate_encoder(input_value, encode_range)))
         assert(input_range is not None)
         # suppress the given values in the memory
         if not isinstance(value, (frozenset, list, np.ndarray, set, tuple)):
             value = [value]
-        compensate = array(self.coordinate_encoder(value, input_range))
+        compensate = self.coordinate_encoder(value, input_range)
         # we have to smooth this to ensure correct alignment with the current memory
+        compensate = helpers.reShape(compensate,dim)
         compensate = helpers.smooth(compensate, self.window_ratio)
-
+        compensate[:] = [x * -height for x in compensate]
+        
         if self.visualize:
             print("Output Supressed Value:")
-            self.plot(compensate)
+            self.plot(np.reshape(compensate,self.size))
 
-        compensate[:] = [x * -abs(np.max(memory)) for x in compensate]
+        
         memory += compensate
         return memory
         #for i, v in enumerate(suppress_value):
@@ -193,6 +196,8 @@ class HRR(VSA):
         if memory == None:
             memory = self.memory
             
+        memory = helpers.normalize(memory)
+            
         if decode_range is None:
             decode_range = self.valid_range
         if decode_range is None:
@@ -204,24 +209,28 @@ class HRR(VSA):
 
         if self.visualize:
             print("Output Reverse:")
-            self.plot(memory)
+            self.plot(np.reshape(memory,self.size))
 
[…]

### 2016-11-07 papers/hrr-paper/paper.tex
Modified title are, abstract and introduction.

@@
 
+\usepackage{cite}
+
 %\usepackage{asmfonts}
@@
 	% Do not put math or special symbols in the title.
-\title{Semantic Holographic Memories}
+	\title{Implicit Holographic Memories}
 
@@
 	% affiliations
-\author{\IEEEauthorblockN{Igor Peric, Stefan Ulbrich, Alexandru Lesi, R{\"u}diger Dillman, Marius Z{\"o}llner}
+	\author{\IEEEauthorblockN{Igor Peric, Stefan Ulbrich, Alexandru Lesi, Daniel Spies, R{\"u}diger Dillman, Marius Z{\"o}llner}
 		\IEEEauthorblockA{FZI Forschungszentrum Informatik\\
 			Karlsruhe, Germany\\
-Email: $\{$peric, ulbrich, dillmann, zoellner$\}$@fzi.de}
+			Email: $\{$peric, ulbrich, lesi, spies, dillmann, zoellner$\}$@fzi.de}
 	}
@@
 	\begin{abstract}
-Vector Symbolic Architectures (VSA) define a set of operations for storage (compression), manipulation and retrieval of symbolic concepts, represented as fixed-length vectors.
+		Vector Symbolic Architectures (VSA) define a set of operations for storage (compression), manipulation and retrieval of symbolic concepts, represented as fixed-length vectors from ${\rm I\!R}^N$.
 A specific instance of VSA, Holographic Reduced Representations (HRR), has proven to exhibit properties similar to human short-term memory and is, as such, interesting for computational modeling.
 
-In this paper we extend HRR approach by introducing topology-preserving, invertible encoding/decoding procedure for all major data types used in robotics and engineering.
-These encoding schemes play the role of otherwise used clean-up modules after memory retrieval (e.g.
-self-organizing maps), thus eliminating necessity for them.
+		In this paper we extend HRR approach by introducing implicit, topology-preserving, encoding/decoding procedure using radial basis functions.
+Extended approach involves randomly chosen permutation (for encoding) and its inverse (for decoding), necessary for uniform distribution of signal in Fourier space in which embedding takes place.
+These novel encoding schemes, together with extended operation pipeline, play the role of so called clean-up modules after memory retrieval (e.g.
+self-organizing maps).
+Effectively, encoding implicitly represents the symbol, so no further lookup is needed.
 
-We test our memories in three different robotic tasks: mapping and recall, visual object classification and state machine scripting (holographic controllers).
+		We show that newly introduced encoding scheme didn't have negative impact on memory capacity in comparison with original author's capacity benchmark.
+We also test our memories in three different robotics tasks: mapping and recall of an area by a mobile agent, top-down visual attention shift and state machine scripting (holographic controllers).
 	\end{abstract}
@@
 	Vector Symbolic Architectures (VSA) define a set of operations for storage (compression) and retrieval of symbolic concepts in fixed size vectors.
-In its basic form every VSA has to implement three basic operations:
+As described in \cite{vsa1}, every VSA has to implement three basic operations:
 	\begin{enumerate}
@@
 
-In addition, every VSA can be considered as a compression technique, since binary operations on N-element vectors return N-element vectors as well.
+	In addition, every VSA can be considered as a lossy compression technique, since binary operations on N-element vectors return N-element vectors as well.
 
-\textbf{Association} (also called "binding") is operation of linking two operands together, resulting in a vector of same size which is dissimilar (orthogonal) to both original vectors, but contains scrambled information from both of the operands.
-For instance, linking property "red" to object "triangle" can be done using binding operation:
+	Depending of the way these three operations are implemented we can distinguish several popular VSAs, such as Holographic Reduced Representations \cite{hrr-1}, Circular HRRs \cite{circular-hrr}, Binary Spatter Codes \cite{bsc-1}, Holographic Graph Neurons\cite{holographic-graph-nouron}, Geometric Algebras\cite{geometric-algebra} and Random Permutations.
+The most widely used ones are HRRs and they are briefly explained in section \ref{sec:hrr}.
+Authors in \cite{learning-language} have used them to solve word embedding problem for extremely large dataset by replacing computationally expensive big matrix factorization with iterative estimation algorithm based on HRRs.
+Some of the other work is centered around pattern recognition \cite{pattern-recognition}, functional large-scale cognitive architecture models \cite{spaun} and representing scene structure \cite{scene-structure}.
+Some preliminary theoretical assumptions have been made about ability to use them as agent controllers\cite{embedding-behaviour}, where a symbolic program is represented with a set of combined symbolic actions associated with actuator symbols and symbolic sensing.
+
+	Authors in \cite{spaun} have demonstrated functional cognitive model Spaun, implemented as HRRs using biologically plausible models of neuron dynamics, is capable of performing 7 different cognitive tasks.
+In serial memory task they show that model of forgetting exhibits similar behavior as human working memory due to limited capacity.
+Besides that, they report similarity between human working memory capacity and average number of items (symbols) that their model is capable of holding in memory.
+This successful model of forgetting is one of the reasons our work is centered around HRRs.
+
+	Second reason is the fact that HRRs are the only VSAs up to date operating on convolution operations in their core.
+This is appealing if we take into consideration numerous recent advancement in deep learning and convolutional neural networks.
+There are two basic reasons for success of these networks: training on big data and using convolution as the main architectural constraint.
+Although description of biophysical mechanism underlying convolution and concept of weight sharing is still missing, it is important to reuse already proven concepts (such as convolutional filtering) in as general way as possible.
+In other words, addressing multiple fundamentally different problems with the same or similar computational principles can be considered as a step towards unified brain processing theory.
+
+	\section{Vector Symbolic Architectures}
+
+	\textbf{Association} (also called "binding") is an operation of linking two operands together, resulting in a vector of the same size which is dissimilar (orthogonal) to both original vectors, but contains scrambled information from both of the operands.
+For instance, linking the property "red" to object "triangle" can be done using binding operation:
 
@@
 	Process of converting noisy result of probing into the closest know symbol is called \textbf{clean-up procedure}.
-Straightforward way of implementing clean-up memory is using lookup table, while other researchers show that any type of attractor network can be used (e.g.
+Straightforward way of implementing clean-up memory is using a lookup table, while other researchers show that any type of attractor network can be used (e.g.
 self-organizing maps).
 
-\section{Holographic reduced representations}
+	\subsection{Holographic reduced representations}
+	\label{sec:hrr}
 
@@
 			\includegraphics[width=\columnwidth]{img/scalar-pre-perm.png}
-\caption{Binging}
+			\caption{Binding}
 			\label{no-perm-a}
@@
 			\includegraphics[width=\columnwidth]{img/scalar-post-perm.png}
-\caption{Binging}
+			\caption{Binding}
 			\label{perm-a}
@@
 	\section{Conclusions}
+	We have introduced a mechanism for intrinsic symbol encoding/decoding for Holographic Reduced Representations.
+As a consequence, our approach eliminates the need for clean-up memories as they are described in literature.
+Instead, result of probing operation directly gives interpretable symbol, which can be decoded in constant computational time.
+In other words, time needed for encoding/decoding is completely ignorant of total number of symbols memorized, allowing memories that can store large corpus of different symbols.
+	A concrete biophysical evidence and theoretical model of implementation of convolution in brain is, unfortunately, still missing.
 
@@
 
-\bibliographystyle{IEEEtran}
-
-\bibliography{IEEEabrv,bibliography}
+	\include{bibliography}
 

### 2016-11-07 vsa/hrr.py
Merge Commit

@@ -9,6 +9,7 @@ from numpy import array, sqrt, dot
 import random
 import matplotlib.pyplot as plt
 import numbers
+from mpl_toolkits.mplot3d import Axes3D
 
 import helpers
 from vsa import VSA
@@ -411,15 +412,16 @@ class HRR(VSA):
     #  @param smooth Boolean that prompts a smoothing operation prior to plotting.
     #  @param unpermute Boolean that widens the margins of the displayed plotting window.
     #  @return The resulting permuted vector.     
-    def plot(self, vect=None, unpermute=False, smooth=False, wide=False):
+    def plot(self, vect=None, unpermute=False, smooth=False, wide=False, multidim=False):
         if vect is None:
             vect = self.memory
         if unpermute:
             vect = self.reverse_permute(vect)
         if smooth:
             vect = helpers.smooth(vect)
-        plt.figure()
-        xx = range(len(vect))
+            
+        fig = plt.figure()
+        
         if wide:
             widen = len(vect) * 0.1 
             down = np.amin(vect)
@@ -428,7 +430,22 @@ class HRR(VSA):
             down -= mean * 0.1
             up += mean * 0.1
             plt.axis([-widen, len(vect) + widen, down, up])
-        plt.plot(xx, vect)
+        
+        if multidim:
+            assert(len(vect.shape) != 3)
+            if (len(vect.shape) == 1):
+                vect = helpers.reShape(vect,2)
+            X = np.arange(0,len(vect),1)
+            Y = np.arange(0,len(vect[0]),1)
+            X, Y = np.meshgrid(X, Y)
+            ax = fig.gca(projection='3d')
+            surf = ax.plot_surface(X, Y, vect, rstride=1, cstride=1, cmap='coolwarm', linewidth=0, antialiased=False)
+            ax.set_zlim(np.min(vect)/3, 1.1*np.max(vect))
+            fig.colorbar(surf, shrink=0.5, aspect=5)
+        else:
+            xx = range(len(vect))
+            plt.plot(xx, vect)
+        
         plt.show()
 
 #    def decode(self):

### 2016-11-07 papers/hrr-paper/bibliography.tex

\begin{thebibliography}{9}
	\bibitem{vsa1}
		"Vector Symbolic Architectures: A New Building Material for Artificial General Intelligence", Simon D. Levy, Ross W Gayler, Frontiers in Artificial Intelligence and Applications, January 2008

		\bibitem{geometric-algebra}
		"Distributed Representations Based on Geometric Algebra: The Continuous Model", Agnieszka Patyk-Lonska, Marek Czachor, Diederik Aerts, Informatica 35(2011), pg. 407 - 417

	\bibitem{pattern-recognition}
	"Pattern Recognition with Vector Symbolic Architectures", Kleyko Denis, Lulea tekniska universitet, Master thesis 2016.

	\bibitem{holographic-graph-nouron}
	"Holographic Graph Neuron: a Bio-Inspired Architecture forPattern Processing", DenisKleyko et. al, IEEE Transactions on Neural Networks and Learning Systems, March 2016
\end{thebibliography}

### 2016-11-07 papers/hrr-paper/paper.tex
Switch bibliography back end to biber

@@
 %
-\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of the IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/pkg/cite
-% The documentation is contained in the cite.sty file itself.
+%% Use biber instead of BibTeX
+%\usepackage[citestyle=numeric,style=numeric,backend=biber]{biblatex}
+\usepackage[
+	hyperref=true,
+	url=false,
+	isbn=false,
+	citestyle=alphabetic,
+	style=alphabetic,
+	maxcitenames=3,
+	maxbibnames=100,
+	backref=true,
+	backend=biber
+]{biblatex}
+\usepackage[babel,german=quotes,english=american]{csquotes}
+
+%TODO check 
+%\appto{\bibsetup}{\raggedright}
+\appto{\bibsetup}{\sloppy}
+\addbibresource{paper.bib}
+
+%\DefineBibliographyStrings{english}{%
+%    backrefpage  = {see p.}, % for single page number
+%    backrefpages = {see pp.} % for multiple page numbers
+%}
 
@@
 
-\usepackage{cite}
-
 %\usepackage{asmfonts}
@@
 	% Do not put math or special symbols in the title.
-	\title{Implicit Holographic Memories}
+	\title{Perceptual symbol grounding in \\holographic memories}
 
@@
 	Vector Symbolic Architectures (VSA) define a set of operations for storage (compression) and retrieval of symbolic concepts in fixed size vectors.
-As described in \cite{vsa1}, every VSA has to implement three basic operations:
+As described in \cite{Levy:2008:VectorSymbolicArchitectures}, every VSA has to implement three basic operations:
 	\begin{enumerate}
@@
 
-	Depending of the way these three operations are implemented we can distinguish several popular VSAs, such as Holographic Reduced Representations \cite{hrr-1}, Circular HRRs \cite{circular-hrr}, Binary Spatter Codes \cite{bsc-1}, Holographic Graph Neurons\cite{holographic-graph-nouron}, Geometric Algebras\cite{geometric-algebra} and Random Permutations.
+	Depending of the way these three operations are implemented we can distinguish several popular VSAs, such as Holographic Reduced Representations \cite{hrr-1}, Circular HRRs \cite{circular-hrr}, Binary Spatter Codes \cite{bsc-1}, Holographic Graph Neurons\cite{Kleyko:2016:HolographicGraphNeuron}, Geometric Algebras\cite{Patyk-Lonska:2011:DistributedRepresentationsBased} and Random Permutations.
 The most widely used ones are HRRs and they are briefly explained in section \ref{sec:hrr}.
 Authors in \cite{learning-language} have used them to solve word embedding problem for extremely large dataset by replacing computationally expensive big matrix factorization with iterative estimation algorithm based on HRRs.
-Some of the other work is centered around pattern recognition \cite{pattern-recognition}, functional large-scale cognitive architecture models \cite{spaun} and representing scene structure \cite{scene-structure}.
+Some of the other work is centered around pattern recognition \cite{Kleyko:2016:PatternRecognitionVector}, functional large-scale cognitive architecture models \cite{spaun} and representing scene structure \cite{scene-structure}.
 Some preliminary theoretical assumptions have been made about ability to use them as agent controllers\cite{embedding-behaviour}, where a symbolic program is represented with a set of combined symbolic actions associated with actuator symbols and symbolic sensing.
+
+	\begin{figure}
+		\center
+		\includegraphics[width=0.9\columnwidth]{img/cover_photo.png}
+		\caption{In-memory representation of top-down attention shift for visual scene short-term  memory}
+	\end{figure}
 
@@
 
-	\include{bibliography}
+	%% Add entry to the table of contents for the bibliography
+	\printbibliography[heading=bibintoc]
 

### 2016-11-07 papers/hrr-paper/paper.tex
Add a line break after every sentence for single-sentence changes in git
Added contrller text to .tex

@@
 Extended approach involves randomly chosen permutation (for encoding) and its inverse (for decoding), necessary for uniform distribution of signal in Fourier space in which embedding takes place.
-These novel encoding schemes, together with extended operation pipeline, play the role of so called clean-up modules after memory retrieval (e.g.
-self-organizing maps).
+These novel encoding schemes, together with extended operation pipeline, play the role of so called clean-up modules after memory retrieval (e.g. self-organizing maps).
 Effectively, encoding implicitly represents the symbol, so no further lookup is needed.
@@
 
-	\textbf{Probing} is operation of extracting a noisy version of associated item from a joint set memory. I.e. a question "What is the color of triangle?" could be asked like this:
+	\textbf{Probing} is operation of extracting a noisy version of associated item from a joint set memory.
+I.e. a question "What is the color of triangle?" could be asked like this:
 
@@
 	Process of converting noisy result of probing into the closest know symbol is called \textbf{clean-up procedure}.
-Straightforward way of implementing clean-up memory is using a lookup table, while other researchers show that any type of attractor network can be used (e.g.
-self-organizing maps).
+Straightforward way of implementing clean-up memory is using a lookup table, while other researchers show that any type of attractor network can be used (e.g. self-organizing maps).
 
@@
 	- SIFT + location
-	\subsection{Holographic state machines (holographic controllers)}
-	- sensory\_data + current\_state + next state
+\subsection{Symbolic scripting (holographic controllers)}
+
+We have used our system to demonstrate a mechanism for encoding neural programs and processes through series of associated action, perception and actuator symbols.
+We call this mechanism for defining controllers using holographic memories "symbolic scripting".
+
+\begin{figure}[th!]
+	\center
+	\begin{subfigure}{1\columnwidth}
+		\includegraphics[width=\columnwidth]{img/control_pipeline.png}
+		\caption{Symbolic scripting pipeline}
+		\label{fig:symbolic-scripting-a}
+	\end{subfigure}
+
+	\begin{subfigure}{0.7\columnwidth}
+		\center
+		\includegraphics[width=\columnwidth]{img/symbol_table.png}
+		\caption{Symbol table}
+		\label{fig:symbolic-scripting-b}
+	\end{subfigure}
+	\begin{subfigure}{1\columnwidth}
+		\includegraphics[width=\columnwidth]{img/controller.png}
+		\caption{Holographic program (script)}
+		\label{fig:symbolic-scripting-c}
+	\end{subfigure}
+	\caption{Symbolic scripting example for light following behavior of a two-wheeled robot}
+	\label{fig:symbolic-scripting}
+\end{figure}
+
+The basic idea is centered around symbolic representations of all three parts involved:
+\begin{enumerate}
+	\item \textbf{actions} are symbolic constants representing groups of control signals, such as "forward", "backward", "stop", "flex", etc.
+
+	\item \textbf{actuators} are named controllable parts of the system on which actions can be performed on, such as "right\_wheel", "left\_wheel", etc.
+
+	\item \textbf{senses} are preprocessed (classified) sensory stream labels, such as "bright", "dark", "touching", "falling\_down", "rolling", etc.
+\end{enumerate}
+
+An example of this kind of symbolic script is given on figure \ref{fig:symbolic-scripting}. Memory encodes light following behavior.
+
 	\subsection{Reinforcement learning}
@@
 	% leaving this as is.
-	The authors would like to thank... Manchester developers. :slowclap:
+	The authors would like to thank...
+Manchester developers. :slowclap:
 

### 2016-11-07 papers/hrr-paper/paper.tex
Change citation style to numeric
Add option to number citations as they appear

@@
 	isbn=false,
-	citestyle=alphabetic,
-	style=alphabetic,
+	%citestyle=alphabetic,
+	citestyle=numeric,
+	%style=alphabetic,
+	style=numeric,
+	sorting=none,
 	maxcitenames=3,

### 2016-11-07 papers/hrr-paper/paper.tex
Add bibtex entries and fix citations

@@
 
-	Depending of the way these three operations are implemented we can distinguish several popular VSAs, such as Holographic Reduced Representations \cite{hrr-1}, Circular HRRs \cite{circular-hrr}, Binary Spatter Codes \cite{bsc-1}, Holographic Graph Neurons\cite{Kleyko:2016:HolographicGraphNeuron}, Geometric Algebras\cite{Patyk-Lonska:2011:DistributedRepresentationsBased} and Random Permutations.
+	Depending of the way these three operations are implemented we can distinguish several popular VSAs, such as Holographic Reduced Representations \cite{Plate:1995:HolographicReducedRepresentations}, Circular HRRs \cite{circular-hrr}, Binary Spatter Codes \cite{Kanerva:1994:SpatterCodeEncoding}, Holographic Graph Neurons \cite{Kleyko:2016:HolographicGraphNeuron}, Geometric Algebras \cite{Patyk-Lonska:2011:DistributedRepresentationsBased} and Random Permutations.
 The most widely used ones are HRRs and they are briefly explained in section \ref{sec:hrr}.
 Authors in \cite{learning-language} have used them to solve word embedding problem for extremely large dataset by replacing computationally expensive big matrix factorization with iterative estimation algorithm based on HRRs.
-Some of the other work is centered around pattern recognition \cite{Kleyko:2016:PatternRecognitionVector}, functional large-scale cognitive architecture models \cite{spaun} and representing scene structure \cite{scene-structure}.
+Some of the other work is centered around pattern recognition \cite{Kleyko:2016:PatternRecognitionVector}, functional large-scale cognitive architecture models \cite{Eliasmith:2012:LargeScaleModel} and representing scene structure \cite{scene-structure}.
 Some preliminary theoretical assumptions have been made about ability to use them as agent controllers\cite{embedding-behaviour}, where a symbolic program is represented with a set of combined symbolic actions associated with actuator symbols and symbolic sensing.
@@
 
-	Authors in \cite{spaun} have demonstrated functional cognitive model Spaun, implemented as HRRs using biologically plausible models of neuron dynamics, is capable of performing 7 different cognitive tasks.
+	Authors in \cite{Eliasmith:2012:LargeScaleModel} have demonstrated functional cognitive model Spaun, implemented as HRRs using biologically plausible models of neuron dynamics, is capable of performing 7 different cognitive tasks.
 In serial memory task they show that model of forgetting exhibits similar behavior as human working memory due to limited capacity.

### 2016-11-07 vsa/hrr.py
Added Images of encodings and probes for given scene. Also added scene scenario in HRR.ipynb

@@ -412,11 +412,13 @@ class HRR(VSA):
     #  @param smooth Boolean that prompts a smoothing operation prior to plotting.
     #  @param unpermute Boolean that widens the margins of the displayed plotting window.
     #  @return The resulting permuted vector.     
-    def plot(self, vect=None, unpermute=False, smooth=False, wide=False, multidim=False):
+    def plot(self, vect=None, unpermute=False, smooth=False, normalize=True, wide=False, multidim=False):
         if vect is None:
             vect = self.memory
         if unpermute:
             vect = self.reverse_permute(vect)
+        if normalize:
+            vect = helpers.normalize(vect)
         if smooth:
             vect = helpers.smooth(vect)
             
@@ -439,7 +441,7 @@ class HRR(VSA):
             Y = np.arange(0,len(vect[0]),1)
             X, Y = np.meshgrid(X, Y)
             ax = fig.gca(projection='3d')
-            surf = ax.plot_surface(X, Y, vect, rstride=1, cstride=1, cmap='coolwarm', linewidth=0, antialiased=False)
+            surf = ax.plot_surface(X, Y, vect, rstride=1, cstride=1, cmap='coolwarm', linewidth=0, antialiased=True)
             ax.set_zlim(np.min(vect)/3, 1.1*np.max(vect))
             fig.colorbar(surf, shrink=0.5, aspect=5)
         else:

### 2016-11-08 papers/hrr-paper/paper.tex
Added capacity analysis and visual scene experiment.

@@
 	% Do not put math or special symbols in the title.
-	\title{Perceptual symbol grounding in \\holographic memories}
+	\title{Perceptual symbol grounding in \\Holographic memories}
 
@@
 		\includegraphics[width=\columnwidth]{img/scalar-random-fft.png}
-		\caption{Fourier space conversions of a Gaussian bell and a random vector.}
+		\caption{Fourier analysis of 1D symbols: radial basis kernel (top row) and same dimensional vector randomly sampled from normal distribution (bottom row).
+It is obvious that latter is uniformly spread across the whole vector, while the former is concentrated around 2 boundary values leading to increased interference between multiple items stored one over another (when added in Fourier space).}
 		\label{fft}
@@
 
-	\subsection{Coordinate encoder}
+	\section{Properties of holographic memories}
 
-	\subsection{String encoder}
+	Vector Symbolic Architectures in general have following properties:
+	\begin{itemize}
+		\item Number of items stored in a single memory vector is not known based only on it's content.
+		\item Existence of item in memory cannot be explicitly checked. The closest equivalent is probing the memory for item of interest and comparing similarity of decoding result to anything meaningful.
+		\item Chances of successful recall depend on the actual data stored.
+		\item Memories can be changed in online fashion. There is no need to recreate memories from scratch - symbols can be appended to or removed from (if presents) already existing memory vectors.
+	\end{itemize}
 
-	\section{Properties of SHM}
+	\subsection{Capacity}
 
-	- you can't extract the items memorized, number of them, you can just query
-	- they are probabilistic
-	- you can modify them online (no separate learning/probing phases)
-	\subsection{Capacity}
-	\subsubsection{SHM size vs. number of items}
-	\subsubsection{Model of human forgetting}
-	\subsubsection{Model of intentional forgetting}
+	As done by Plate et.
+al.
+in original HRR paper\cite{Plate:1995:HolographicReducedRepresentations} we have tested memory capacity in terms of accuracy of successful recall for variable number of bound pairs.
+Results are show in figure \ref{fig:capacity}.
 
-	\subsection{Fan-out effect - multiple probing outputs}
+		\begin{figure}[th!]
+			\center
+			\includegraphics[width=0.8\columnwidth]{img/capacity.png}
+			\caption{Memory capacity analysis for storing variable number of pair associations in a single memory vector.
+Different lines show vector length, while horizontal axis shows number of pairs and vertical axis accuracy of successful recall.}
+			\label{fig:capacity}
+		\end{figure}
 
-	\subsection{Limitations}
-
-	- introducing problem of lookup (symbol grounding)
-	- solution using implicit encoding and decoding
+	As we can see, a 512 element vector starts decreasing accuracy of recall after 10 pairs stored in a single memory block.
+A 4096 and 8192 element vectors can almost perfectly recall 20 associated pairs, which matches the results of Plate using lookup table and cleanup process.
+As we can see, newly introduced perceptual symbol grounding did not have significant effect on memory capacity.
 
@@
 
-	\subsection{Visual object classification}
-	- SIFT + label
+	\subsection{Visual short term memory and top-down attention model}
+
+	In this experiment a system is given a monocular stream as an input.
+An arbitrary algorithm is used to perform object detection and recognition, resulting in number of 2D coordinates associated with respective object names (figure \ref{fig:object-detection}).
+Object names are strings and are encoded as random vectors of length N, sampled from normal distribution (figure \ref{fig:encoding-object}).
+Locations of object in image plane are 2D coordinates $(x,y)$ and they are perceptually grounded symbols (figure \ref{fig:encoding-coord}).
+
+	\begin{figure}[th!]
+		\center
+		\begin{subfigure}{0.8\columnwidth}
+			\includegraphics[width=\columnwidth]{img/map_original.jpg}
+			\caption{Original scene and set of detected objects}
+			\label{fig:object-detection}
+		\end{subfigure}
+
+		\begin{subfigure}{0.45\columnwidth}
+			\center
+			\includegraphics[width=\linewidth]{img/coord_example_1.png}
+			\caption{Encoding of (x,y) location of an object}
+			\label{fig:encoding-coord}
+		\end{subfigure}
+		\begin{subfigure}{0.45\columnwidth}
+			\center
+			\includegraphics[width=\linewidth]{img/coord_example_2.png}
+			\caption{Encoding of an object ID as randomly sampled vector}
+			\label{fig:encoding-object}
+		\end{subfigure}
+
+				\begin{subfigure}{0.8\columnwidth}
+					\center
+					\includegraphics[width=\linewidth]{img/coord_example_3.png}
+					\caption{Encoding of the complete visual scene, containing information about all 7 objects and their locations}
+					\label{fig:encoding-scene}
+				\end{subfigure}
+
+			\begin{subfigure}{0.45\columnwidth}
+				\center
+				\includegraphics[width=\linewidth]{img/probe_for_mug.png}
+				\caption{Probing for "mug" returns location probability mug}
+				\label{fig:probing-single}
+			\end{subfigure}
+			\begin{subfigure}{0.45\columnwidth}
+				\center
+				\includegraphics[width=\linewidth]{img/probe_for_pen.png}
+				\caption{Probing for "pen" return mixture of Gaussians}
+				\label{fig:probing-double}
+			\end{subfigure}
+
+		\caption{Representation of visual scene in short term symbolic memory. }
+		\label{fig:visual-scene-exp}
+	\end{figure}
+
 	\subsection{Localization and mapping}
-	- SIFT + location
+	- TBD
+
 \subsection{Symbolic scripting (holographic controllers)}
@@
 
-	\subsection{Reinforcement learning}
-	- sensory\_data + action + reward
-	\subsection{Language understanding}
-	- TensorFlow (role) + word = question answering
-	\subsection{Implicit inductive reasoning}
-
 	\section{Conclusions}

### 2016-11-08 papers/hrr-paper/paper.tex
Changed some figure captions for visual scene experiment

@@
 			\includegraphics[width=\linewidth]{img/coord_example_1.png}
-			\caption{Encoding of (x,y) location of an object}
+			\caption{Encoding of (x,y) location for "watch"}
 			\label{fig:encoding-coord}
@@
 			\includegraphics[width=\linewidth]{img/coord_example_2.png}
-			\caption{Encoding of an object ID as randomly sampled vector}
+			\caption{Encoding of "watch" object ID as randomly sampled vector}
 			\label{fig:encoding-object}
@@
 					\includegraphics[width=\linewidth]{img/coord_example_3.png}
-					\caption{Encoding of the complete visual scene, containing information about all 7 objects and their locations}
+					\caption{Representation of the complete visual scene, containing information about all 7 objects and their locations}
 					\label{fig:encoding-scene}

### 2016-11-08 papers/hrr-paper/paper.tex
Fix and add new citations

@@
 
-	Depending of the way these three operations are implemented we can distinguish several popular VSAs, such as Holographic Reduced Representations \cite{Plate:1995:HolographicReducedRepresentations}, Circular HRRs \cite{circular-hrr}, Binary Spatter Codes \cite{Kanerva:1994:SpatterCodeEncoding}, Holographic Graph Neurons \cite{Kleyko:2016:HolographicGraphNeuron}, Geometric Algebras \cite{Patyk-Lonska:2011:DistributedRepresentationsBased} and Random Permutations.
+	Depending of the way these three operations are implemented we can distinguish several popular VSAs, such as Holographic Reduced Representations \cite{Plate:1995:HolographicReducedRepresentations}, Circular HRRs \cite{DeVine:2010:Semanticoscillations}, Binary Spatter Codes \cite{Kanerva:1994:SpatterCodeEncoding}, Holographic Graph Neurons \cite{Kleyko:2016:HolographicGraphNeuron}, Geometric Algebras \cite{Patyk-Lonska:2011:DistributedRepresentationsBased} and Random Permutations \cite{Recchia:2015:EncodingSequentialInformation}.
 The most widely used ones are HRRs and they are briefly explained in section \ref{sec:hrr}.
-Authors in \cite{learning-language} have used them to solve word embedding problem for extremely large dataset by replacing computationally expensive big matrix factorization with iterative estimation algorithm based on HRRs.
+Authors in \cite{Golosio:2015:CognitiveNeuralArchitecture} have used them to solve word embedding problem for extremely large dataset by replacing computationally expensive big matrix factorization with iterative estimation algorithm based on HRRs.
 Some of the other work is centered around pattern recognition \cite{Kleyko:2016:PatternRecognitionVector}, functional large-scale cognitive architecture models \cite{Eliasmith:2012:LargeScaleModel} and representing scene structure \cite{scene-structure}.
-Some preliminary theoretical assumptions have been made about ability to use them as agent controllers\cite{embedding-behaviour}, where a symbolic program is represented with a set of combined symbolic actions associated with actuator symbols and symbolic sensing.
+Some preliminary theoretical assumptions have been made about ability to use them as agent controllers \cite{Levy:2013:LearningBehaviorHierarchies}, where a symbolic program is represented with a set of combined symbolic actions associated with actuator symbols and symbolic sensing.
 
@@
 al.
-in original HRR paper\cite{Plate:1995:HolographicReducedRepresentations} we have tested memory capacity in terms of accuracy of successful recall for variable number of bound pairs.
+in original HRR paper \cite{Plate:1995:HolographicReducedRepresentations} we have tested memory capacity in terms of accuracy of successful recall for variable number of bound pairs.
 Results are show in figure \ref{fig:capacity}.

### 2016-11-08 papers/hrr-paper/paper.tex
Clean up .bib file and filter entries for minimal display
Improved plots, added values for probing bar chart (still require processing)

@@
 
+	FOR BAR CHART:
+
+	Probe at (19,-26.75):
+
+	[('keys', 0.22827929349034107), ('Watch', -0.018549398363469777), ('mug', -0.025309361445942102), ('wallet', -0.034187368731921304), ('pen', 0.2098596398998358), ('mouse', -0.023035819302988644)]
+
+	Probe at (-13,21.5):
+
+[('keys', -0.020032173214673016), ('Watch', -0.034034204029029354), ('mug', 0.03443254630997427), ('wallet', 0.16100011074269183), ('pen', 0.089801145874187763), ('mouse', -0.027742071303527464)]
+
 	\subsection{Localization and mapping}

### 2016-11-09 papers/hrr-paper/paper.tex
Small changes to captions

--- 2016-11-08 papers/hrr-paper/paper.tex
@@
 		\item Number of items stored in a single memory vector is not known based only on it's content.
-		\item Existence of item in memory cannot be explicitly checked. The closest equivalent is probing the memory for item of interest and comparing similarity of decoding result to anything meaningful.
+		\item Existence of an item in memory cannot be explicitly verified.
+The closest equivalent is probing the memory for item of interest and comparing similarity of decoding result to anything meaningful.
 		\item Chances of successful recall depend on the actual data stored.
@@
 					\includegraphics[width=\linewidth]{img/coord_example_3.png}
-					\caption{Representation of the complete visual scene, containing information about all 7 objects and their locations}
+					\caption{Representation of the complete visual scene, containing information about all 7 objects and their locations scrambled together}
 					\label{fig:encoding-scene}
@@
 				\includegraphics[width=\linewidth]{img/probe_for_mug.png}
-				\caption{Probing for "mug" returns location probability mug}
+				\caption{Probing for "mug" returns location probability for a mug}
 				\label{fig:probing-single}

### 2016-11-09 papers/hrr-paper/paper.tex

--- 2016-11-08 papers/hrr-paper/paper.tex
@@
 	hyperref=true,
-	url=false,
-	isbn=false,
 	%citestyle=alphabetic,
@@
 	maxbibnames=100,
-	backref=true,
+	%backref=true,
 	backend=biber
@@
 \usepackage[babel,german=quotes,english=american]{csquotes}
+
+% disable unimportant stuff in bibliography
+\DeclareSourcemap{
+  \maps[datatype=bibtex, overwrite]{
+    \map{
+      \step[fieldset=language, null]
+      \step[fieldset=notes, null]
+      \step[fieldset=issn, null]
+      \step[fieldset=doi, null]
+      \step[fieldset=url, null]
+      \step[fieldset=eprint, null]
+      \step[fieldset=abstract, null]
+      \step[fieldset=pages, null]
+      \step[fieldset=address, null]
+      \step[fieldset=editors, null]
+    }
+  }
+}
 

### 2016-11-09 vsa/hrr.py
Chanced probe images to have transparent background.

@@ -453,7 +453,8 @@ class HRR(VSA):
         else:
             xx = range(len(vect))
             plt.plot(xx, vect)
-        
+            
+        #fig.savefig('temp.png', transparent=True)
         plt.show()
 
 #    def decode(self):

### 2016-11-09 papers/hrr-paper/paper.tex
Created Bar Charts for paper. Still need text.

@@
 
+\usepackage{pgfplots}
+
 % correct bad hyphenation here
@@
 		\item Number of items stored in a single memory vector is not known based only on it's content.
-		\item Existence of an item in memory cannot be explicitly verified.
-The closest equivalent is probing the memory for item of interest and comparing similarity of decoding result to anything meaningful.
+		\item Existence of item in memory cannot be explicitly checked. The closest equivalent is probing the memory for item of interest and comparing similarity of decoding result to anything meaningful.
 		\item Chances of successful recall depend on the actual data stored.
@@
 					\includegraphics[width=\linewidth]{img/coord_example_3.png}
-					\caption{Representation of the complete visual scene, containing information about all 7 objects and their locations scrambled together}
+					\caption{Representation of the complete visual scene, containing information about all 7 objects and their locations}
 					\label{fig:encoding-scene}
@@
 				\includegraphics[width=\linewidth]{img/probe_for_mug.png}
-				\caption{Probing for "mug" returns location probability for a mug}
+				\caption{Probing for "mug" returns location probability mug}
 				\label{fig:probing-single}
@@
 		\caption{Representation of visual scene in short term symbolic memory. }
-		\label{fig:visual-scene-exp}
+
 	\end{figure}
-
-	FOR BAR CHART:
 
@@
 
-	[('keys', 0.22827929349034107), ('Watch', -0.018549398363469777), ('mug', -0.025309361445942102), ('wallet', -0.034187368731921304), ('pen', 0.2098596398998358), ('mouse', -0.023035819302988644)]
-
+	    \begin{tikzpicture}
+        \begin{axis}[
+            symbolic x coords={keys, mouse, mug, pen, wallet, watch},
+            xtick=data
+          ]
+            \addplot[ybar,fill=blue] coordinates {
+                (keys,   0.22827929349034107)
+                (mouse, 0.023035819302988644)
+                (mug, 0.025309361445942102)
+                (pen, 0.2098596398998358)
+                (wallet, 0.034187368731921304)
+                (watch, 0.018549398363469777)
+            };
+        \end{axis}
+    \end{tikzpicture}
 	Probe at (-13,21.5):
 
-[('keys', -0.020032173214673016), ('Watch', -0.034034204029029354), ('mug', 0.03443254630997427), ('wallet', 0.16100011074269183), ('pen', 0.089801145874187763), ('mouse', -0.027742071303527464)]
+	    \begin{tikzpicture}
+        \begin{axis}[
+            symbolic x coords={keys, mouse, mug, pen, wallet, watch},
+            xtick=data
+          ]
+            \addplot[ybar,fill=blue] coordinates {
+                (keys,   0.020032173214673016)
+                (mouse, 0.027742071303527464)
+                (mug, 0.03443254630997427)
+                (pen, 0.089801145874187763)
+                (wallet, 0.16100011074269183)
+                (watch, 0.034034204029029354)
+            };
+        \end{axis}
+    \end{tikzpicture}
+
+		\label{fig:visual-scene-exp}
 

### 2016-11-11 papers/hrr-paper/paper.tex
Replaced the cover photo.

--- 2016-11-09 papers/hrr-paper/paper.tex
@@
 		\center
-		\includegraphics[width=0.9\columnwidth]{img/cover_photo.png}
-		\caption{In-memory representation of top-down attention shift for visual scene short-term  memory}
+		\includegraphics[width=0.9\columnwidth]{img/probe_for_pen_w_img.png}
+		\caption{In-memory representation of top-down attention shift for visual scene short-term memory. Result shows attention distribution for a symbol "pen".}
 	\end{figure}

### 2016-11-22 papers/hrr-paper/paper.tex
Reshaped bar charts, added text to them.

--- 2016-11-11 papers/hrr-paper/paper.tex
@@
 
-	Probe at (19,-26.75):
+	Due to the noisy nature of probing given by the slight loss of information in the binding process each symbol may have some amount of similarity to whatever other symbol it is compared to.
+However, even though this is the case, the similarity measure of bound symbols is consistently higher and can be clearly distinguished from others.
+Chart \ref{pgf:bar1} represents the result of probing at (19, -26.75), which is somewhere in between the keys and the red pen, as seen in figure \ref{fig:object-detection}.
 
-	    \begin{tikzpicture}
+	 As we can see all symbols that are nowhere near the position present similarities well below 5 \%, while both close matches scored over 20 \%.
+Spot on probes may even attain values of over 50 \%.
+The example in chart \ref{pgf:bar2} is for a probe at(-13, 21.5), which is further away from the center of an object region.
+But even though the dark pen and the wallet are further apart the result of probing still yields distinctly higher similarities for them as opposed to objects further away.
+
+	\begin{figure}[th!]
+	\center
+		\begin{subfigure}{0.49\columnwidth}
+	    \begin{tikzpicture}[yscale=0.5, xscale=0.5]
         \begin{axis}[
             symbolic x coords={keys, mouse, mug, pen, wallet, watch},
-            xtick=data
+            xlabel = Symbol,
+            ylabel = Similarity
           ]
@@
     \end{tikzpicture}
-	Probe at (-13,21.5):
-
-	    \begin{tikzpicture}
+        \caption{Probe at (19, -26.75).}
+        \label{pgf:bar1}
+    \end{subfigure}
+		\begin{subfigure}{0.49\columnwidth}
+    	    \begin{tikzpicture}[yscale=0.5, xscale=0.5]
         \begin{axis}[
             symbolic x coords={keys, mouse, mug, pen, wallet, watch},
-            xtick=data
+            xlabel = Symbol,
+            ylabel = Similarity
           ]
@@
     \end{tikzpicture}	
+        \caption{Probe at (-13, 21.5).}
+        \label{pgf:bar2}
+    \end{subfigure}
+    \end{figure}
 

### 2016-12-01 papers/hrr-paper/paper.tex
Polished some paragraphs in HRR section.

--- 2016-11-22 papers/hrr-paper/paper.tex
@@
 	\begin{abstract}
-		Vector Symbolic Architectures (VSA) define a set of operations for storage (compression), manipulation and retrieval of symbolic concepts, represented as fixed-length vectors from ${\rm I\!R}^N$.
+		Vector Symbolic Architectures (VSA) define a set of operations for association, (compressed) storage, manipulation and retrieval of symbolic concepts, represented as fixed-length vectors from ${\rm I\!R}^N$.
 A specific instance of VSA, Holographic Reduced Representations (HRR), has proven to exhibit properties similar to human short-term memory and is, as such, interesting for computational modeling.
@@
 		\includegraphics[width=0.9\columnwidth]{img/probe_for_pen_w_img.png}
-		\caption{In-memory representation of top-down attention shift for visual scene short-term memory. Result shows attention distribution for a symbol "pen".}
+		\caption{In-memory representation of top-down attention shift for visual scene short-term memory.
+Result shows attention distribution for a symbol "pen".
+In probabilistic sense it can be understood as probability of pen being at a certain position.}
 	\end{figure}
@@
 		\includegraphics[width=0.9\columnwidth]{img/scalar-probe.png}
-		\caption{Result of $(80 \otimes A) \oslash A$ for HRR from}
+		\caption{Result of $(80 \otimes A) \oslash A$ for a 2000-element HRR encoding values from range [0,100].}
 	\end{figure}
@@
 
-	where $z$ is the result of convolution, $x$ and $y$ are operands of size $N$.
+	where $z$ is the result of convolution, $x$ and $y$ are symbolic vectors of size $N$.
 Superposition is implemented as simple element-wise addition.
-Probing is implemented using inverse of circular convolution - circular correlation:
+Probing is implemented using inverse of circular convolution (circular correlation):
 
@@
 	\end{equation}
+
+	In order to use various types of inputs with HRRs it is necessary to encode them in vectors of fixed size.
+	The basic approach is to pick these vectors randomly once for each symbol and maintain these pairs in a separate data structure.
+	This will consequently increase space complexity and may become infeasible, depending on the type of input used.
+For example, handling scalar symbolic encoding can be done by discretization of the whole input range into bins and assigning a random vector to each discrete value.
+In order to decode a specific symbolic vector, one must find maximum similarity element from symbol table, which requires O(M), where M is the number of symbols known to the system.
+
+	Usual way of computing similarity is cosine distance:
+
+	(INSERT FORMULA)
+
+	This approach works quite well for object identifiers (names), but has some non-desirable properties when used on scalar encoding. These will be discussed in the following section.
 
@@
 
-	In order to use various types of inputs with HRRs it is necessary to encode them in vectors of fixed size.
-The basic approach is to generate these vectors randomly for each distinct input and store these pairs in a map.
-This will consequently take its toll on the space complexity and may become infeasible, depending on the type of input used.
-The following section presents ways to encode values in a deterministic manner, removing the need to store these, as long as decoding is robust against noise.
-
-	\subsection{Scalars}
+	\subsection{Encoding scalar symbol as p.d.f.}
 
@@
     \end{subfigure}
+
+    			\caption{Test}
     \end{figure}

### 2016-12-02 papers/hrr-paper/paper.tex
Added various formulas
Fixed a typo

@@
 	\begin{equation}
-	z_i=\sum_{k=0}^{N}{x_iy_{i-k}} //TODO
+	z_i=\sum_{j=0}^{N-1}{x_jy_{i-j}} 
 	\end{equation}
@@
 	\begin{equation}
-	y_i=\sum_{k=0}^{m}{x_iy_{i-k}} //TODO
+	y_i=\sum_{j=0}^{N-1}{x_jz_{j+1}} 
 	\end{equation}
@@
 
-	Usual way of computing similarity is cosine distance:
+	Usual way of computing similarity is cosine distance, which for two vectors \pmb x and \pmb y is calculated as follows:
 
-	(INSERT FORMULA)
+	\begin{equation}
+cos(\pmb x, \pmb y) = \frac {\pmb x \cdot \pmb y}{||\pmb x|| \cdot ||\pmb y||}
+	\end{equation}
 
@@
 		\item Number of items stored in a single memory vector is not known based only on it's content.
-		\item Existence of item in memory cannot be explicitly checked. The closest equivalent is probing the memory for item of interest and comparing similarity of decoding result to anything meaningful.
+		\item Existence of an item in memory cannot be explicitly checked.
+The closest equivalent is probing the memory for item of interest and comparing similarity of decoding result to anything meaningful.
 		\item Chances of successful recall depend on the actual data stored.

### 2016-12-12 papers/hrr-paper/paper.tex

@@
 		\item Number of items stored in a single memory vector is not known based only on it's content.
-		\item Existence of an item in memory cannot be explicitly checked.
+		\item Existence of an item in memory cannot be explicitly verified.
 The closest equivalent is probing the memory for item of interest and comparing similarity of decoding result to anything meaningful.

### 2016-12-12 papers/hrr-paper/paper.tex
Rewrote, corrected and rearranged Abstract, Introduction and sections I and II

--- 2016-12-02 papers/hrr-paper/paper.tex
@@
 	% Do not put math or special symbols in the title.
-	\title{Perceptual symbol grounding in \\Holographic memories}
+	\title{Perceptual Symbol Grounding in \\Holographic Memories}
 
@@
 	% affiliations
-	\author{\IEEEauthorblockN{Igor Peric, Stefan Ulbrich, Alexandru Lesi, Daniel Spies, R{\"u}diger Dillman, Marius Z{\"o}llner}
+	\author{\IEEEauthorblockN{Igor Peric, Alexandru Lesi, Daniel Spies, Stefan Ulbrich, R{\"u}diger Dillman, Marius Z{\"o}llner}
 		\IEEEauthorblockA{FZI Forschungszentrum Informatik\\
 			Karlsruhe, Germany\\
-			Email: $\{$peric, ulbrich, lesi, spies, dillmann, zoellner$\}$@fzi.de}
+			Email: $\{$peric, lesi, spies, ulbrich, dillmann, zoellner$\}$@fzi.de}
 	}
@@
 		Vector Symbolic Architectures (VSA) define a set of operations for association, (compressed) storage, manipulation and retrieval of symbolic concepts, represented as fixed-length vectors from ${\rm I\!R}^N$.
-A specific instance of VSA, Holographic Reduced Representations (HRR), has proven to exhibit properties similar to human short-term memory and is, as such, interesting for computational modeling.
+A specific instance of VSA, Holographic Reduced Representations (HRR), has proven to exhibit properties similar to human short-term memory and is, as such, interesting for computational modelling.
 
-		In this paper we extend HRR approach by introducing implicit, topology-preserving, encoding/decoding procedure using radial basis functions.
+		In this paper we extend the HRR approach by introducing implicit, topology-preserving, encoding/decoding procedure using radial basis functions.
 Extended approach involves randomly chosen permutation (for encoding) and its inverse (for decoding), necessary for uniform distribution of signal in Fourier space in which embedding takes place.
@@
 
-		We show that newly introduced encoding scheme didn't have negative impact on memory capacity in comparison with original author's capacity benchmark.
+		We show that this newly introduced encoding scheme didn't have a negative impact on memory capacity in comparison with the original author's capacity benchmark.
 We also test our memories in three different robotics tasks: mapping and recall of an area by a mobile agent, top-down visual attention shift and state machine scripting (holographic controllers). 
@@
 	In addition, every VSA can be considered as a lossy compression technique, since binary operations on N-element vectors return N-element vectors as well.
+These operations will be described in further detail in the following section.
 
-	Depending of the way these three operations are implemented we can distinguish several popular VSAs, such as Holographic Reduced Representations \cite{Plate:1995:HolographicReducedRepresentations}, Circular HRRs \cite{DeVine:2010:Semanticoscillations}, Binary Spatter Codes \cite{Kanerva:1994:SpatterCodeEncoding}, Holographic Graph Neurons \cite{Kleyko:2016:HolographicGraphNeuron}, Geometric Algebras \cite{Patyk-Lonska:2011:DistributedRepresentationsBased} and Random Permutations \cite{Recchia:2015:EncodingSequentialInformation}.
+	Depending on the way these three operations are implemented we can distinguish several popular VSAs, such as Holographic Reduced Representations \cite{Plate:1995:HolographicReducedRepresentations}, Circular HRRs \cite{DeVine:2010:Semanticoscillations}, Binary Spatter Codes \cite{Kanerva:1994:SpatterCodeEncoding}, Holographic Graph Neurons \cite{Kleyko:2016:HolographicGraphNeuron}, Geometric Algebras \cite{Patyk-Lonska:2011:DistributedRepresentationsBased} and Random Permutations \cite{Recchia:2015:EncodingSequentialInformation}.
 The most widely used ones are HRRs and they are briefly explained in section \ref{sec:hrr}.
-Authors in \cite{Golosio:2015:CognitiveNeuralArchitecture} have used them to solve word embedding problem for extremely large dataset by replacing computationally expensive big matrix factorization with iterative estimation algorithm based on HRRs.
+Authors in \cite{Golosio:2015:CognitiveNeuralArchitecture} have used them to solve word embedding problem for extremely large dataset by replacing computationally expensive big matrix factorization with an iterative estimation algorithm based on HRRs.
 Some of the other work is centered around pattern recognition \cite{Kleyko:2016:PatternRecognitionVector}, functional large-scale cognitive architecture models \cite{Eliasmith:2012:LargeScaleModel} and representing scene structure \cite{scene-structure}.
-Some preliminary theoretical assumptions have been made about ability to use them as agent controllers \cite{Levy:2013:LearningBehaviorHierarchies}, where a symbolic program is represented with a set of combined symbolic actions associated with actuator symbols and symbolic sensing.
+Preliminary theoretical assumptions have been made about the ability to use them as agent controllers \cite{Levy:2013:LearningBehaviorHierarchies}, where a symbolic program is represented with a set of combined symbolic actions associated with actuator symbols and symbolic sensing.
 
@@
 
-	Authors in \cite{Eliasmith:2012:LargeScaleModel} have demonstrated functional cognitive model Spaun, implemented as HRRs using biologically plausible models of neuron dynamics, is capable of performing 7 different cognitive tasks.
-In serial memory task they show that model of forgetting exhibits similar behavior as human working memory due to limited capacity.
-Besides that, they report similarity between human working memory capacity and average number of items (symbols) that their model is capable of holding in memory.
-This successful model of forgetting is one of the reasons our work is centered around HRRs.
+	Authors in \cite{Eliasmith:2012:LargeScaleModel} have demonstrated that the functional cognitive model Spaun is capable of performing 7 different cognitive tasks when implemented as HRRs using biologically plausible models of neuron dynamics.
+They further show that in serial working memory tasks the model of forgetting exhibits similar behaviour as human working memory due to limited capacity.
+Lastly they report similarity between the human working memory capacity and the average number of items (symbols) that their model is capable of holding in memory.
 
-	Second reason is the fact that HRRs are the only VSAs up to date operating on convolution operations in their core.
-This is appealing if we take into consideration numerous recent advancement in deep learning and convolutional neural networks.
-There are two basic reasons for success of these networks: training on big data and using convolution as the main architectural constraint.
-Although description of biophysical mechanism underlying convolution and concept of weight sharing is still missing, it is important to reuse already proven concepts (such as convolutional filtering) in as general way as possible.
-In other words, addressing multiple fundamentally different problems with the same or similar computational principles can be considered as a step towards unified brain processing theory.
+	This successful model of forgetting is one of the reasons our work is centred around HRRs.
+Another reason is the fact that HRRs are the only VSAs up to date operating on convolution operations in their core.
+This is appealing if we take the numerous recent advancement in deep learning and convolutional neural networks into consideration.
+These networks succeed due to training on big data and using convolution as the main architectural constraint.
+Although the description of the biophysical mechanism underlying convolution and concept of weight sharing are still missing, it is important to reuse proven concepts, such as convolutional filtering, in as general way as possible.
+In other words, addressing multiple fundamentally different problems with similar computational principles can be considered a step towards a unified brain processing theory.
 
@@
 
-	\textbf{Association} (also called "binding") is an operation of linking two operands together, resulting in a vector of the same size which is dissimilar (orthogonal) to both original vectors, but contains scrambled information from both of the operands.
-For instance, linking the property "red" to object "triangle" can be done using binding operation:
+In order to use VSA operations all types of required inputs need to first be represented as symbols, which are vectors of fixed size.
+The basic approach is to pick these vectors randomly once for each input used in any operation and maintain these pairs in a separate data structure.
+	\\
+
+	\textbf{Association} (also called "binding") is an operation of linking two operands together, resulting in a vector of the same size which is dissimilar (or orthogonal) to the original vectors, but also contains scrambled information from both of them.
+For instance, linking the property "red" to object "triangle" can be done using the binding operation as follows:
 
@@
 
-	\textbf{Superposition} is operation of extending a set of already memorized items with another item (or binding of two or more of them).
+	\textbf{Superposition} is the operation of extending a set of items that have already been memorized with another item (or binding of two or more of them).
 As an example, a memory of "red triangle and blue circle" can be formed in following way:
@@
 
-	\textbf{Probing} is operation of extracting a noisy version of associated item from a joint set memory.
-I.e. a question "What is the color of triangle?" could be asked like this:
+	\textbf{Probing} is the operation of extracting a noisy version of an associated item from a joint set memory.
+I.e. in this scenario the question "What color is the triangle?" could be asked like this:
 
@@
 
-	Probing operation assumes existence of inverse element to association, so previous equation can be interpreted and explained in following way:
+	The probing operation assumes the existence of an inverse element to association, so the previous equation can be interpreted and explained in following way:
 	\begin{multline}
@@
 	where $triangle'$ represents inverse of $triangle$.
-Resulting vector will be composition of something that is very similar to $red$ and something that doesn't resemble anything meaningful from symbol table, so it can be treated as neglectable noise.
+The resulting vector will be a composition of something that is very similar to $red$ and something that doesn't resemble anything meaningful from the symbol table, so it can be treated as negligible noise.	A usual way of computing similarity is the cosine distance, which for two vectors \pmb x and \pmb y is calculated as follows:
+
+	\begin{equation}
+cos(\pmb x, \pmb y) = \frac {\pmb x \cdot \pmb y}{||\pmb x|| \cdot ||\pmb y||}
+	\end{equation}
 
@@
 
-	Process of converting noisy result of probing into the closest know symbol is called \textbf{clean-up procedure}.
-Straightforward way of implementing clean-up memory is using a lookup table, while other researchers show that any type of attractor network can be used (e.g. self-organizing maps).
+	Obtained values of similarity clearly distinguish the matching vectors. Concrete values that highlight this will be later presented in section \ref{sec:experiments}.
+
+	The process of converting a noisy result of probing into the closest known symbol is called the \textbf{clean-up procedure}.
+A straightforward way of implementing clean-up memory is using a lookup table, while other researchers show that any type of attractor network can be used (e.g. self-organizing maps).
+
+	In the case of look-up tables, in order to decode a specific symbolic vector, the elements from a symbol table are iterated over, the similarity to each of the entries is calculated and the symbol which presented maximum similarity is returned.
+A threshold for the similarity value is also used in order to exclude false-positives.
+This look-up requires O(M), where M is the number of symbols known to the system.
+This approach works quite well for object identifiers (names), but has some non-desirable properties when used on scalar encoding.
+	//TODO Lookup Example
+
+	This will consequently increase space complexity and may become infeasible, depending on the type of input used.
+While looking for existing elements may not require the entire table to be checked probing for non-existent ones will always traverse all entries only to show up empty at the end.When handling scalars symbolic encoding can be done by discretization of the whole input range into bins and assigning a random vector to each discrete value.
+This however may often prove to not satisfy the task needs any more.
 
@@
 
-	Holographic Reduced Representations are VSAs which implement operation of binding as circular convolution:
+	Holographic Reduced Representations are VSAs which implement the operation of binding as circular convolution:
 
@@
 
-	where $z$ is the result of convolution, $x$ and $y$ are symbolic vectors of size $N$.
-Superposition is implemented as simple element-wise addition.
+	where $z$ is the result of convolution, and $x$ and $y$ are symbolic vectors of size $N$.
+Superposition is implemented as a simple element-wise vector addition.
 Probing is implemented using inverse of circular convolution (circular correlation):
@@
 	\end{equation}
-
-	In order to use various types of inputs with HRRs it is necessary to encode them in vectors of fixed size.
-	The basic approach is to pick these vectors randomly once for each symbol and maintain these pairs in a separate data structure.
-	This will consequently increase space complexity and may become infeasible, depending on the type of input used.
-For example, handling scalar symbolic encoding can be done by discretization of the whole input range into bins and assigning a random vector to each discrete value.
-In order to decode a specific symbolic vector, one must find maximum similarity element from symbol table, which requires O(M), where M is the number of symbols known to the system.
-
-	Usual way of computing similarity is cosine distance, which for two vectors \pmb x and \pmb y is calculated as follows:
-
-	\begin{equation}
-cos(\pmb x, \pmb y) = \frac {\pmb x \cdot \pmb y}{||\pmb x|| \cdot ||\pmb y||}
-	\end{equation}
-
-	This approach works quite well for object identifiers (names), but has some non-desirable properties when used on scalar encoding. These will be discussed in the following section.
 
@@
 	\section{Experiments}
-
+	\label{sec:experiments}
 	\subsection{Visual short term memory and top-down attention model}

### 2016-12-12 papers/hrr-paper/paper.tex
Forgot to save the document before pushing

@@
 	In the case of look-up tables, in order to decode a specific symbolic vector, the elements from a symbol table are iterated over, the similarity to each of the entries is calculated and the symbol which presented maximum similarity is returned.
-A threshold for the similarity value is also used in order to exclude false-positives.
-This look-up requires O(M), where M is the number of symbols known to the system.
+With the help of a threshold for the similarity value false-positives can be excluded.
+A look-up requires O(M), where M is the number of symbols known to the system.
 This approach works quite well for object identifiers (names), but has some non-desirable properties when used on scalar encoding.

### 2016-12-13 papers/hrr-paper/paper.tex
Edit and format abstract

@@
 	\begin{abstract}
-		Vector Symbolic Architectures (VSA) define a set of operations for association, (compressed) storage, manipulation and retrieval of symbolic concepts, represented as fixed-length vectors from ${\rm I\!R}^N$.
-A specific instance of VSA, Holographic Reduced Representations (HRR), has proven to exhibit properties similar to human short-term memory and is, as such, interesting for computational modelling.
+		Vector Symbolic Architectures (VSAs) define a set of operations
+		for association, (compressed) storage, manipulation and retrieval
+		of symbolic concepts, represented as fixed-length vectors in
+		${\rm I\!R}^N$.
+		A subset of VSAs, Holographic Reduced Representations (HRRs),
+		have proven to exhibit properties similar to human short-term
+		memory and are, as such, interesting for computational modeling.
 
-		In this paper we extend the HRR approach by introducing implicit, topology-preserving, encoding/decoding procedure using radial basis functions.
-Extended approach involves randomly chosen permutation (for encoding) and its inverse (for decoding), necessary for uniform distribution of signal in Fourier space in which embedding takes place.
-These novel encoding schemes, together with extended operation pipeline, play the role of so called clean-up modules after memory retrieval (e.g. self-organizing maps).
-Effectively, encoding implicitly represents the symbol, so no further lookup is needed.
+		In this paper we extend the HRR approach by introducing implicit,
+		topology-preserving, encoding/decoding procedures using radial
+		basis functions.
+		This involves randomly chosen permutations for encoding and
+		their corresponding inverse for decoding, which is necessary
+		for the uniform distribution of signals in Fourier space where
+		embedding takes place.
+		These novel encoding schemes, together with the extended operation
+		pipeline, are akin to so-called \emph{clean-up modules after memory
+		retrieval} (e.g., self-organizing maps). Effectively, encoding
+		implicitly represents the symbol, so no further lookup is needed.
 
-		We show that this newly introduced encoding scheme didn't have a negative impact on memory capacity in comparison with the original author's capacity benchmark.
-We also test our memories in three different robotics tasks: mapping and recall of an area by a mobile agent, top-down visual attention shift and state machine scripting (holographic controllers). 
+		We show that our encoding scheme does not have a negative impact
+		on memory capacity in comparison to the original capacity
+		benchmark for HRRs by Plate
+		\cite{Plate:1995:HolographicReducedRepresentations}.
+		We also evaluate our memories in three different robotics tasks:
+		mapping and recall of an area by a mobile agent, top-down visual
+		attention shift and state machine scripting (holographic
+		controllers).
 	\end{abstract}

### 2016-12-13 papers/hrr-paper/paper.tex
Corrected and completed Chapter IIA - IV

@@
 		This involves randomly chosen permutations for encoding and
-		their corresponding inverse for decoding, which is necessary
+		their corresponding inverse for decoding. These are necessary
 		for the uniform distribution of signals in Fourier space where
@@
 	\begin{equation}
-	z_i=\sum_{j=0}^{N-1}{x_jy_{i-j}} 
+	a_i=\sum_{j=0}^{N-1}{x_j y_{i-j}} 
 	\end{equation}
 
-	where $z$ is the result of convolution, and $x$ and $y$ are symbolic vectors of size $N$.
-Superposition is implemented as a simple element-wise vector addition.
-Probing is implemented using inverse of circular convolution (circular correlation):
+	where \pmb a is the result of convolution, and \pmb x and \pmb y are symbolic vectors of size $N$.
+Superposition is implemented as a simple element-wise vector addition. Taking the result of the previously displayed convolution superposing it with some vector \pmb b is done as follows:
 
 	\begin{equation}
-	y_i=\sum_{j=0}^{N-1}{x_jz_{j+1}} 
+	m_i = a_i + b_i
 	\end{equation}
+
+The resulting vector of the superposition operation \pmb m can then be probed by using the inverse of circular convolution, which is circular correlation:
+
+	\begin{equation}
+	y'_i=\sum_{j=0}^{N-1}{x_jm_{j+1}} 
+	\end{equation}
+
+Following the previous formulas as a series of operations the vector \pmb y' will be very similar to vector \pmb y, but not entirely the same due to the noisy influence of vector \pmb b.
 
@@
 
-	\subsection{Encoding scalar symbol as p.d.f.}
+	\subsection{Encoding scalar symbol as radial basis functions}
 
 	Encoding scalars is a good example for the necessity of preserving topology.
-Depending on what dataset is in use it may be required to store mappings for any number of values.
-Furthermore, using random encoding, there would be no similarity in neighbouring values.
+Depending on what dataset is in use it may be required to store mappings for any number of values, which can drastically increase space requirements.
+Furthermore, using a separate random encoding for each scalar, regardless of whether they are very close to each other or not, there would be no similarity in neighbouring values.
 As such the following probe will yield no result:
@@
 	\begin{equation}
-	(10000 \otimes A) \oslash 10001
+	(10000 \otimes a) \oslash 10001
 	\end{equation}
 
-	To facilitate these two qualities scalar encoding can be achieved with the help of Gaussian distributions.
-The encoded vector will simply represent a Gaussian bell sampled over a fixed input range.
+	To facilitate these two qualities scalar encoding can be achieved with the help of radial basis functions. Among these functions one of the options are Gaussian distributions.
+The encoded vector can simply represent a Gaussian sampled over a fixed input range.
 Figure \ref{no-perm-a} shows how such an encoded vector looks like, and what the result of binding it to a generic random vector is.
-With this result it becomes obvious that lots of information is lost.
+With this result it becomes obvious that unfortunately lots of information is lost.
 If this result is probed with the same random vector used in binding something similar to the initial Gaussian bell is expected.
 And yet figure \ref{no-perm-b} presents no such outcome.
-While there is a peak at the initial value lots of other peaks also arise, making it impossible to detect which one is correct.
+While there is a peak at the initial value which is probed for lots of other peaks also arise, making it impossible to detect which one is correct.
 
@@
 Figure \ref{fft} highlights this.
-All the information of a Gaussian bell is crammed into the lowest and highest values of the Fourier transformation.
-In these circumstances, when probing for a scalar, the vector received is in turn recreated of too few frequencies and does not come close to resembling the original Gaussian.
+All the information of a Gaussian bell is crammed into the lowest and highest values of the Fourier transformation, resulting in a high loss.
+In these circumstances, when probing for a scalar, the vector received is in turn recreated of too few frequencies and will not come close to resembling the original Gaussian distribution.
 
@@
 	This inconvenience is removed with the help of permutations.
-Depending on the size of the memory vectors used a fixed permutation is generated.
-Whenever a scalar is encoded the Gaussian bell is first sampled over the range, after which the sampled values swap places accordingly.
+Depending on the size of the memory vectors used a fixed permutation is generated once.
+Whenever a scalar is encoded the Gaussian distribution is first sampled over the given range, after which the sampled values swap places accordingly.
 As such the resulting vector will present lots of jumps in value, which have a significant impact on the Fourier space, as can be seen in figure \ref{perm-fft}.
@@
 	Working with such a vector makes it possible to successfully probe for scalars and receive a Gaussian bell overlapped with some noise.
-All of this can be seen in figure \ref{perm}, which depicts the exact same operations as figure \ref{no-perm}, but using a permuted version of a Gaussian bell.
-The result in figure \ref{perm-b} clearly shows an according spike.
+All of this can be seen in figure \ref{perm}, which depicts the exact same operations as figure \ref{no-perm}, but using a permuted version of a Gaussian distribution.
+The result in figure \ref{perm-b} clearly shows a spike at the expected spot in the sample range.
 This vector can be smoothed out, after which the peak can easily be identified and the initial scalar can be recovered.
@@
 
-	On a technical note it became apparent that simply sampling Gaussian bells in a vector with all the values greater zero brought up a small issue.
+	On a technical note it became apparent that simply sampling Gaussian bells in a vector with all the values greater zero brought up an issue.
 Adding multiple such bindings on top of each other would constantly increase the values in the resulting vector.
@@
 
-	Vector Symbolic Architectures in general have following properties:
+	Vector Symbolic Architectures in general have the following properties:
 	\begin{itemize}
-		\item Number of items stored in a single memory vector is not known based only on it's content.
-		\item Existence of an item in memory cannot be explicitly checked.
-The closest equivalent is probing the memory for item of interest and comparing similarity of decoding result to anything meaningful.
-		\item Chances of successful recall depend on the actual data stored.
-		\item Memories can be changed in online fashion. There is no need to recreate memories from scratch - symbols can be appended to or removed from (if presents) already existing memory vectors.
+		\item The number of items stored in a single memory vector is not known based solely on it's content.
+		\item Existence of an item in memory cannot be checked explicitly.
+The closest equivalent is to probe the memory for the item of interest and to compare the similarity of the decoded result to anything meaningful.
+Even then it could be that the result of probing for anything might still require to be probed by a further symbol to retrieve the sought out item.
+		\item Chances of successful recall depend on the actual stored data.
+		\item Memories can be changed in an online fashion. There is no need to recreate memories from scratch - symbols can be appended to or removed from already existing memory vectors if present.
 	\end{itemize}
@@
 
-	As done by Plate et.
-al.
-in original HRR paper \cite{Plate:1995:HolographicReducedRepresentations} we have tested memory capacity in terms of accuracy of successful recall for variable number of bound pairs.
+	Just as Plate has done in the original HRR paper \cite{Plate:1995:HolographicReducedRepresentations} we have tested the memory capacity in terms of accuracy of successful recall for variable number of bound pairs.
 Results are show in figure \ref{fig:capacity}.
@@
 	As we can see, a 512 element vector starts decreasing accuracy of recall after 10 pairs stored in a single memory block.
-A 4096 and 8192 element vectors can almost perfectly recall 20 associated pairs, which matches the results of Plate using lookup table and cleanup process.
-As we can see, newly introduced perceptual symbol grounding did not have significant effect on memory capacity.
+A 4096 and 8192 element vectors can almost perfectly recall 20 associated pairs, which matches the results of Plate using a lookup table and a clean-up process.
+As we can see, newly introduced perceptual symbol grounding did not have a significant effect on memory capacity.
 

### 2016-12-14 papers/hrr-paper/paper.tex
Added pseudo code skeletons
Added pseudocode content

@@
 % have to be run twice to clear warning/error messages.
-
+\usepackage{algorithm}
+\usepackage{algpseudocode} 
 \usepackage{subcaption}
@@
 
+	Algorithms 1 and 2 show, respectively, pseudo code for pipeline before and after the suggested modification are introduced.
+
+	\begin{algorithm}
+		\caption{Original pipeline}
+		\begin{algorithmic}[1]
+			\ForAll{$symbol$}
+			\State $t_{symbol} \gets chooseRandomVector()$
+			\EndFor
+			\State $m \gets initEmptyMemory()$
+			\ForAll{$(symbol_1, symbol_2)$}
+			\State $enc_1 \gets FFT(t_{symbol_1})$
+			\State $enc_2 \gets FFT(t_{symbol_2})$
+			\State $m \gets m + enc_1 \otimes enc_2$
+			\EndFor		
+			\Function{ProbeMemory}{memory, operand}
+			\State $result \gets IFFT(memory \oslash operand)$
+			\ForAll{$symbol$}
+			\State $s \gets cosineSimilarity(t_{symbol}, result)$
+			\If {$s \geq cleanResultSimilarity$}
+			\State $cleanResultSimilarity \gets s$
+			\State $cleanResult \gets t_{symbol}$
+			\EndIf
+			\EndFor \\
+			\Return $cleanResult$
+			\EndFunction
+		\end{algorithmic}
+	\end{algorithm}
+
+	Lines 1-3 assign a random vector representation to each symbol known to the system prior to any other operations.
+This lookup table is stored in array $t$.
+Lines 4-9 initialize the memory $m$ with arbitrary amount of pairs of associated scalars.
+Function $ProbeMemory(memory, operand)$ returns symbol associated with provided $operand$.
+Line 11 performs circular correlation and stores noisy result of unbinding in $s$.
+Lines 12-18 loop through the whole lookup table and find the maximum similarity vector to $s$.
+
+		In contrast, Algorithm 2 shows pipeline with proposed changes.
+First line chooses a fixed random permutation of $N$ elements used throughout the whole process.
+It can bee seen that there is no initial loop to assign symbolic representations to all symbols.
+They are, instead, constructed according to need using function $enc(value, N)$, which returns discrete sampled normal distribution vector of N elements, centered around $value$.
+This perfectly sampled normal distribution is permuted using permutation $P$ in lines 4 and 5, so its frequency representation contains uniform spread over the whole spectrum, as explained earlier in this chapter.
+Probing operation consists of applying inverse permutation $P^{-1}$ after IFFT (line 9).
+Since this gives a noisy version of initial normal distribution (shown in figure \ref{perm-b}), the only thing that needs to be done is to identify the mean of the distribution.
+Complexity of this operation is linear w.r.t.
+length of the vector $N$, while in case of Algorithm 1 it is linear w.r.t.
+to number of symbols stored in the lookup table.
+
+	\begin{algorithm}
+		\caption{Modified pipeline}
+		\begin{algorithmic}[1]
+			\State $P \gets chooseRandomPermutation(N)$
+			\State $m \gets initEmptyMemory()$
+			\ForAll{$(symbol_1, symbol_2)$}
+			\State $enc_1 \gets FFT(permute(enc(symbol_1, N), P))$
+			\State $enc_2 \gets FFT(permute(enc(symbol_2, N), P))$
+			\State $m \gets m + enc_1 \otimes enc_2$
+			\EndFor	
+			\Function{ProbeMemory}{memory, operand}
+			\State $r \gets permute(IFFT(memory \oslash operand), P^{-1})$
+			\State $cleanResult \gets argmax(r)$
+
+			\Return $cleanResult$
+			\EndFunction
+		\end{algorithmic}
+	\end{algorithm}
+
 	On a technical note it became apparent that simply sampling Gaussian bells in a vector with all the values greater zero brought up an issue.

### 2016-12-14 vsa/helpers.py
Added accuracy experiments for scalars and coordinates. Added some images to paper.

@@ -177,7 +177,6 @@ def smoothWork(x,window_len=100,window='hanning'):
     else:
         w=eval('np.'+window+'(window_len)')
     y = np.convolve(w/w.sum(),s,mode='valid')
-    y = y[(window_len/2-1):-(window_len/2)]
-    
+    y = y[(window_len/2-1):(window_len/2-1)+l]
     assert(len(y) == l)
     return y

### 2016-12-14 vsa/hrr.py

@@ -27,7 +27,7 @@ class HRR(VSA):
     peak_min = 0                    # Absolute value used to detect Gaussian peaks
     peak_min_ratio =  10            # Minimum factor by which a gaussian peak needs be larger than the average of noise.
     window_ratio = 50		        # Ratio by which window length for smoothing is divided
-    valid_range = [0,100]           # Standard valid range for scalar or coordinate encoding
+    valid_range = zip([0],[100])    # Standard valid range for scalar or coordinate encoding
     
     ## The constructor.
     #
@@ -203,6 +203,8 @@ class HRR(VSA):
             decode_range = self.valid_range
         if decode_range is None:
             raise ValueError("Decoding scalar values requires valid range (valid_range or decode_range parameter)")
+               
+        
                 
         assert(len(decode_range) == dim)
                 
@@ -272,7 +274,7 @@ class HRR(VSA):
             result = np.empty(self.size, dtype=float)
          
             if isinstance(input_value, float) or isinstance(input_value, numbers.Integral):
-                result = self.permute(helpers.normalize(self.scalar_encoder(input_value, self.size, encode_range)))
+                result = self.permute(helpers.normalize(self.scalar_encoder(input_value, self.size, encode_range[0])))
             elif isinstance(input_value, (frozenset, list, np.ndarray, set, tuple)):
                 result = self.permute(helpers.normalize(self.coordinate_encoder(input_value, encode_range)))
             else:    

### 2016-12-15 papers/hrr-paper/paper.tex
Lots of new stuff

@@
 		\cite{Plate:1995:HolographicReducedRepresentations}.
-		We also evaluate our memories in three different robotics tasks:
-		mapping and recall of an area by a mobile agent, top-down visual
+		We also evaluate our memories in different robotics tasks: top-down visual
 		attention shift and state machine scripting (holographic
@@
 
-	Holographic Reduced Representations are VSAs which implement the operation of binding as circular convolution:
+	Holographic Reduced Representations are VSAs which implement the operation of binding as circular convolution.
+An option to calculating this is with the help of discrete Fast Fourier Transformations, in short FFTs.
+Taking $f(x)$ to describe an FFT, with $f^{-1}(x)$ as its inverse, circular convolution can be calculated as follows:
 
 	\begin{equation}
-	a_i=\sum_{j=0}^{N-1}{x_j y_{i-j}} 
+	\pmb a = f^{-1}(f(\pmb x) * f(\pmb y))
 	\end{equation}
@@
 	where \pmb a is the result of convolution, and \pmb x and \pmb y are symbolic vectors of size $N$.
-Superposition is implemented as a simple element-wise vector addition. Taking the result of the previously displayed convolution superposing it with some vector \pmb b is done as follows:
+Superposition is implemented as a simple element-wise vector addition. Taking the result of the previously displayed convolution and superposing it with some vector \pmb b is done as follows:
 
 	\begin{equation}
-	m_i = a_i + b_i
+	\pmb m = \pmb a + \pmb b
 	\end{equation}
 
-The resulting vector of the superposition operation \pmb m can then be probed by using the inverse of circular convolution, which is circular correlation:
+The resulting vector of the superposition operation \pmb m can then be probed by using the inverse of circular convolution, which is circular correlation.
+Plainly put probing can be viewed as binding with the "inverse" of a vector in Fourier space:
 
 	\begin{equation}
-	y'_i=\sum_{j=0}^{N-1}{x_jm_{j+1}} 
+	\pmb y' = f^{-1}(f(\pmb m) * f(\pmb x)^{-1})
 	\end{equation}
 
-Following the previous formulas as a series of operations the vector \pmb y' will be very similar to vector \pmb y, but not entirely the same due to the noisy influence of vector \pmb b.
+Following the previous formulas as a series of operations the vector \pmb y' will be similar to vector \pmb y, but not entirely the same due to the noisy influence of vector \pmb b.
+The inverse referred to here is gained by calculating the complex conjugate of the vector's entries.
+Complex conjugates are simply the same values with negated imaginary parts.
+
+	Performing FFTs has no invariant regarding the mean of the resulting vector entries and can produce all sorts of results.
+Due to this, when probing, we would receive vectors which had the correct relative distance between their values, i.e.
+the correct "shape", but would be shifted, stretched or squeezed on the Y-axis.This lead to vectors falsely being regarded as dissimilar to each other, and can be solved by performing two normalization steps:
+
+	\begin{equation}
+	x_i = x_i - \frac{\sum_{i=0}^n ||x_i||}{|x|}
+	\end{equation}
+
+	\begin{equation}
+	\pmb x = \frac{\pmb x }{ \| \pmb x \|}
+	\end{equation}
 
@@
 With this result it becomes obvious that unfortunately lots of information is lost.
-If this result is probed with the same random vector used in binding something similar to the initial Gaussian bell is expected.
+If this result is probed with the same random vector used in binding something similar to the initial Gaussian distribution is expected.
 And yet figure \ref{no-perm-b} presents no such outcome.
@@
 Figure \ref{no-perm-a} shows the binding of the value 8 on a scale to 10 with the symbolic representation of "ball", which is random.
-In figure \ref{no-perm-b} "ball" is being probed, and the expected result is a Gaussian bell for 8, mixed with some noise.}
+In figure \ref{no-perm-b} "ball" is being probed, and the expected result is a Gaussian distribution for 8, mixed with some noise.}
 		\label{no-perm}
@@
 Figure \ref{fft} highlights this.
-All the information of a Gaussian bell is crammed into the lowest and highest values of the Fourier transformation, resulting in a high loss.
+All the information of a Gaussian distribution is crammed into the lowest and highest values of the Fourier transformation, resulting in a high loss.
 In these circumstances, when probing for a scalar, the vector received is in turn recreated of too few frequencies and will not come close to resembling the original Gaussian distribution.
@@
 		\includegraphics[width=\columnwidth]{img/scalar-random-fft.png}
-		\caption{Fourier analysis of 1D symbols: radial basis kernel (top row) and same dimensional vector randomly sampled from normal distribution (bottom row).
+		\caption{Fourier analysis of 1D symbols: Gaussian distribution (top row) and same dimensional vector randomly sampled from normal distribution (bottom row).
 It is obvious that latter is uniformly spread across the whole vector, while the former is concentrated around 2 boundary values leading to increased interference between multiple items stored one over another (when added in Fourier space).}
@@
 		\includegraphics[width=\columnwidth]{img/scalar-perm-step-fft.png}
-		\caption{Plots on the effect of permuting a Gaussian bell, and the impact on Fourier space.}
+		\caption{Plots on the effect of permuting a Gaussian distribution, and the impact on Fourier space.}
 		\label{perm-fft}
@@
 
-	Working with such a vector makes it possible to successfully probe for scalars and receive a Gaussian bell overlapped with some noise.
+	Working with such a vector makes it possible to successfully probe for scalars and receive a Gaussian distribution overlapped with some noise.
 All of this can be seen in figure \ref{perm}, which depicts the exact same operations as figure \ref{no-perm}, but using a permuted version of a Gaussian distribution.
@@
 		\end{subfigure}
-		\caption{Figure \ref{perm-a} shows the binding of the permuted Gaussian for value 8 on a scale to 10 with the symbolic representation of "ball", which is random.
-In figure \ref{perm-b} "ball" is being probed, and the expected result is a Gaussian bell for 8, mixed with some noise.}
+		\caption{Figure \ref{perm-a} shows the binding of the permuted Gaussian distribution for value 8 on a scale to 10 with the symbolic representation of "ball", which is random.
+In figure \ref{perm-b} "ball" is being probed, and the expected result is a Gaussian distribution for 8, mixed with some noise.}
 		\label{perm}
@@
 			\State $enc_2 \gets FFT(t_{symbol_2})$
-			\State $m \gets m + enc_1 \otimes enc_2$
+			\State $m \gets m + IFFT(enc_1 \otimes enc_2$)
 			\EndFor		
 			\Function{ProbeMemory}{memory, operand}
-			\State $result \gets IFFT(memory \oslash operand)$
+			\State $result\gets IFFT(FFT(memory)\oslash FFT(operand))$
 			\ForAll{$symbol$}
@@
 
-	On a technical note it became apparent that simply sampling Gaussian bells in a vector with all the values greater zero brought up an issue.
-Adding multiple such bindings on top of each other would constantly increase the values in the resulting vector.
-Due to this, when probing, we would receive vectors which had the correct distance between their values, i.e.
-the correct "shape", but would be shifted on the Y-axis.
-This can be solved by editing the permuted Gaussian bell to have \(\sum_{i=0}^n x_i = 0\), and is achieved with this simple operation:
-
-	\[ \forall x_i \in x: x_i = x_i - \frac{\sum_{i=0}^n ||x_i||}{|x|} \]
-
 	\section{Properties of holographic memories}
@@
 
-	Just as Plate has done in the original HRR paper \cite{Plate:1995:HolographicReducedRepresentations} we have tested the memory capacity in terms of accuracy of successful recall for variable number of bound pairs.
-Results are show in figure \ref{fig:capacity}.
-
+	Just as Plate has done in the original HRR paper \cite{Plate:1995:HolographicReducedRepresentations} we have tested the memory capacity in terms of accuracy of successful recall for variable numbers of bound pairs.
+Results are shown in figure \ref{fig:capacity}.
 		\begin{figure}[th!]
+		\begin{subfigure}{\columnwidth}
 			\center
 			\includegraphics[width=0.8\columnwidth]{img/capacity.png}
-			\caption{Memory capacity analysis for storing variable number of pair associations in a single memory vector.
-Different lines show vector length, while horizontal axis shows number of pairs and vertical axis accuracy of successful recall.}
+			\caption{Memory capacity analysis for storing a variable number of pair associations in a single memory vector.
+Different lines show various vector lengths, the horizontal axis shows the number of pairs and vertical axis accuracy of successful recall.
+Both false positives and false negatives are regarded.}
 			\label{fig:capacity}
+		\end{subfigure}
+				\begin{subfigure}{\columnwidth}
+			\center
+			\includegraphics[width=0.8\columnwidth]{img/capacity_scalar_30.png}
+			\caption{Memory capacity analysis for binding pairs of one scalar and a random symbol, then probing for the scalar.}
+			\label{fig:capacity_scalar}
+		\end{subfigure}	
+		\begin{subfigure}{\columnwidth}
+			\center
+			\includegraphics[width=0.8\columnwidth]{img/capacity_coordinate.png}
+			\caption{Memory capacity analysis for binding pairs of one 2D coordinate and a random symbol, then probing for the scalar.}
+			\label{fig:capacity_coordinate}
+		\end{subfigure}	
 		\end{figure}	
-
 	As we can see, a 512 element vector starts decreasing accuracy of recall after 10 pairs stored in a single memory block.
 A 4096 and 8192 element vectors can almost perfectly recall 20 associated pairs, which matches the results of Plate using a lookup table and a clean-up process.
-As we can see, newly introduced perceptual symbol grounding did not have a significant effect on memory capacity.
+
+	The experiment was repeated for binding a random symbol to the encodings of both scalars and to 2D coordinates, to compare performance.
+Figure \ref{fig:capacity_scalar} shows the result for scalars.
+In this instance the probe was always done for the scalar value.
+The total accuracy of the result depends on new factors, the main of which will be the quality of the smoothing function used to clean up the noise from the resulting signal.
+This will determine how much the peaks position may shift in some direction.
+In our experiments a Hanning window smoothing technique was used and a 2\% deviance from the exact initial scalar was allowed.
+With these settings probing performed significantly better than solely among random symbols.
+Vectors of size 8192 even managed to maintain 100\% accuracy when storing 30 bindings.
+Intuitively this can be explained as follows: Gaussian distributions are far more noise tolerant than random vectors.
+Vectors need to maintain a high similarity to be declared identical, whereas Gaussian distributions only need to present peaks after smoothing.
+
+	Finally figure \ref{fig:capacity_coordinate} shows the accuracy of stacking bindings of 2D coordinates with random symbols.
+The same smoothing and deviance settings were used as for the previous experiment.
+As coordinates are encoded in a vector that is virtually cast to 2D its length would have to be squared to achieve similar performance to scalars.
+Due to this higher steps in between vector lengths have been used, and most lengths still perform rather poorly.
+However, increasing the length considerably, like in the case with 65536 elements, near-perfect accuracy can still be upheld up to 20 bindings.
 
@@
 				\includegraphics[width=\linewidth]{img/probe_for_pen.png}
-				\caption{Probing for "pen" return mixture of Gaussians}
+				\caption{Probing for "pen" return mixture of Gaussian distributions}
 				\label{fig:probing-double}
@@
 
-	\subsection{Localization and mapping}
-	- TBD
-
 \subsection{Symbolic scripting (holographic controllers)}

### 2016-12-15 vsa/hrr.py

@@ -274,9 +274,9 @@ class HRR(VSA):
             result = np.empty(self.size, dtype=float)
          
             if isinstance(input_value, float) or isinstance(input_value, numbers.Integral):
-                result = self.permute(helpers.normalize(self.scalar_encoder(input_value, self.size, encode_range[0])))
+                result = self.permute(self.scalar_encoder(input_value, self.size, encode_range[0]))
             elif isinstance(input_value, (frozenset, list, np.ndarray, set, tuple)):
-                result = self.permute(helpers.normalize(self.coordinate_encoder(input_value, encode_range)))
+                result = self.permute(self.coordinate_encoder(input_value, encode_range))
             else:    
                 result = self.generateVector() 
                 HRR.mapping[input_value] = result

### 2016-12-15 vsa/hrr.py
is None

@@ -146,7 +146,7 @@ class HRR(VSA):
     
     def decode(self, memory=None):
       
-        if memory == None:
+        if memory is None:
             memory = self.memory
             
         return VSA.decode(self, memory)
@@ -194,7 +194,7 @@ class HRR(VSA):
            
         assert(dim == 1 or dim == 2 or dim == 3)
         
-        if memory == None:
+        if memory is None:
             memory = self.memory
             
         memory = helpers.normalize(memory)
@@ -240,7 +240,7 @@ class HRR(VSA):
                 spot[i] = helpers.reverse_scale(spot[i], l, decode_range[i])
             
             result.append((spot, 1))
-            if return_list == False:
+            if return_list is False:
                 return spot
             memory = self.deductValue(memory,spot,HRR.valid_range,dim, np.max(memory))
             if self.visualize:

### 2016-12-16 papers/hrr-paper/paper.tex
Minor correction to text and image positioning and sizes.

@@
 
-	\begin{figure}
-		\center
-		\includegraphics[width=0.9\columnwidth]{img/scalar-probe.png}
-		\caption{Result of $(80 \otimes A) \oslash A$ for a 2000-element HRR encoding values from range [0,100].}
-	\end{figure}
-
 	Obtained values of similarity clearly distinguish the matching vectors. Concrete values that highlight this will be later presented in section \ref{sec:experiments}.
@@
 
-	- Implementation and building up of HRRs (similarity measures and cosine, lookup table...)
-
 	\section{Topology-preserving encoding}
-
-	- necessity (benefit of having it, querying smth that was not there)
-	- implementation
 
@@
 Furthermore, using a separate random encoding for each scalar, regardless of whether they are very close to each other or not, there would be no similarity in neighbouring values.
-As such the following probe will yield no result:
+For example, the following probe will yield no result:
 
@@
 
-	\begin{figure}
+	\begin{figure}[th!]
 		\begin{subfigure}{1\columnwidth}
@@
 
-	\begin{figure}
+\begin{figure}[th!]
 	\includegraphics[width=\columnwidth]{img/scalar-pre-perm-fft.png}
@@
 			\EndFor		
-			\Function{ProbeMemory}{memory, operand}
-			\State $result\gets IFFT(FFT(memory)\oslash FFT(operand))$
+			\Function{ProbeMemory}{memory, op}
+			\State $result\gets IFFT(FFT(memory)\oslash FFT(op))$
+
 			\ForAll{$symbol$}
@@
 Lines 4-9 initialize the memory $m$ with arbitrary amount of pairs of associated scalars.
-Function $ProbeMemory(memory, operand)$ returns symbol associated with provided $operand$.
+Function $ProbeMemory(memory, op)$ returns symbol associated with provided $op$.
 Line 11 performs circular correlation and stores noisy result of unbinding in $s$.
 Lines 12-18 loop through the whole lookup table and find the maximum similarity vector to $s$.
+
+		\begin{algorithm}
+			\caption{Modified pipeline}
+			\begin{algorithmic}[1]
+				\State $P \gets chooseRandomPermutation(N)$
+				\State $m \gets initEmptyMemory()$
+				\ForAll{$(symbol_1, symbol_2)$}
+				\State $enc_1 \gets FFT(permute(enc(symbol_1, N), P))$
+				\State $enc_2 \gets FFT(permute(enc(symbol_2, N), P))$
+				\State $m \gets m + enc_1 \otimes enc_2$
+				\EndFor	
+				\Function{ProbeMemory}{memory, op}
+				\State $r \gets permute(IFFT(memory \oslash op), P^{-1})$
+				\State $cleanResult \gets argmax(r)$
+
+				\Return $cleanResult$
+				\EndFunction
+			\end{algorithmic}
+		\end{algorithm}
 
@@
 to number of symbols stored in the lookup table.
-
-	\begin{algorithm}
-		\caption{Modified pipeline}
-		\begin{algorithmic}[1]
-			\State $P \gets chooseRandomPermutation(N)$
-			\State $m \gets initEmptyMemory()$
-			\ForAll{$(symbol_1, symbol_2)$}
-			\State $enc_1 \gets FFT(permute(enc(symbol_1, N), P))$
-			\State $enc_2 \gets FFT(permute(enc(symbol_2, N), P))$
-			\State $m \gets m + enc_1 \otimes enc_2$
-			\EndFor	
-			\Function{ProbeMemory}{memory, operand}
-			\State $r \gets permute(IFFT(memory \oslash operand), P^{-1})$
-			\State $cleanResult \gets argmax(r)$
-
-			\Return $cleanResult$
-			\EndFunction
-		\end{algorithmic}
-	\end{algorithm}
 
@@
 
+		\begin{figure}[th!]
+			\begin{subfigure}{0.45\columnwidth}
+				\center
+				\includegraphics[width=1\columnwidth]{img/capacity.png}
+				\caption{Binding of pairs of random vectors (original pipeline).}
+				\label{fig:capacity}
+			\end{subfigure}
+			\begin{subfigure}{0.45\columnwidth}
+				\center
+				\includegraphics[width=1\columnwidth]{img/capacity_scalar_30.png}
+				\caption{Binding pairs of one scalar and a random symbol, then probing for the scalar.}
+				\label{fig:capacity_scalar}
+			\end{subfigure}	
+			\center
+			\begin{subfigure}{0.45\columnwidth}
+				\center
+				\includegraphics[width=1\columnwidth]{img/capacity_coordinate.png}
+				\caption{Binding pairs of one 2D coordinate and a random symbol, then probing for the scalar.}
+				\label{fig:capacity_coordinate}
+			\end{subfigure}	
+			\caption{Memory capacity analysis for storing a variable number of pair associations in a single memory vector.
+Different lines show various vector lengths, the horizontal axis shows the number of pairs and vertical axis accuracy of successful recall.
+Both false positives and false negatives are regarded.}
+		\end{figure}
+
 	\subsection{Capacity}
@@
 Results are shown in figure \ref{fig:capacity}.
-		\begin{figure}[th!]
-		\begin{subfigure}{\columnwidth}
-			\center
-			\includegraphics[width=0.8\columnwidth]{img/capacity.png}
-			\caption{Memory capacity analysis for storing a variable number of pair associations in a single memory vector.
-Different lines show various vector lengths, the horizontal axis shows the number of pairs and vertical axis accuracy of successful recall.
-Both false positives and false negatives are regarded.}
-			\label{fig:capacity}
-		\end{subfigure}
-				\begin{subfigure}{\columnwidth}
-			\center
-			\includegraphics[width=0.8\columnwidth]{img/capacity_scalar_30.png}
-			\caption{Memory capacity analysis for binding pairs of one scalar and a random symbol, then probing for the scalar.}
-			\label{fig:capacity_scalar}
-		\end{subfigure}	
-		\begin{subfigure}{\columnwidth}
-			\center
-			\includegraphics[width=0.8\columnwidth]{img/capacity_coordinate.png}
-			\caption{Memory capacity analysis for binding pairs of one 2D coordinate and a random symbol, then probing for the scalar.}
-			\label{fig:capacity_coordinate}
-		\end{subfigure}	
-		\end{figure}	
+
 	As we can see, a 512 element vector starts decreasing accuracy of recall after 10 pairs stored in a single memory block.
@@
 		\center
-		\begin{subfigure}{0.8\columnwidth}
-			\includegraphics[width=\columnwidth]{img/map_original.jpg}
+		\begin{subfigure}{1.0\columnwidth}
+			\center
+			\includegraphics[width=0.6\columnwidth]{img/map_original.jpg}
 			\caption{Original scene and set of detected objects}
@@
 		\end{subfigure}
-
 				\begin{subfigure}{0.8\columnwidth}
 					\center
-					\includegraphics[width=\linewidth]{img/coord_example_3.png}
+					\includegraphics[width=0.8\linewidth]{img/coord_example_3.png}
 					\caption{Representation of the complete visual scene, containing information about all 7 objects and their locations scrambled together}
@@
 
-    			\caption{Test}
+    			\caption{Similarity test for each symbol from the lookup table after probing the entire scene memory for a specific location.}
     \end{figure}
@@
 
-	% use section* for acknowledgment
-	\section*{Acknowledgment}
-
-	% leaving this as is.
-	The authors would like to thank...
-Manchester developers. :slowclap:
-
 	%% Add entry to the table of contents for the bibliography

### 2016-12-17 robosim/robosim.py
Implement Braitenberg vehicle simulator

@@ -1,0 +1,666 @@
+import math
+import pygame
+import random
+
+from enum import Enum
+from pygame.locals import *
+
+import sys
+sys.path.append("../vsa/")
+from hrr import HRR
+
+
+class Space(Enum):
+	LOCAL = 1
+	WORLD = 2
+
+
+class Shape(Enum):
+	CIRCLE = 1
+	RECT = 2
+	HOUSE = 3
+	FAN = 4
+
+
+class WheelDir(Enum):
+	FORWARDS = "FORWARDS"
+	BACKWARDS = "BACKWARDS"
+	NONE = "NONE"
+
+
+Color = {
+	"WHITE"  : (255, 255, 255),
+	"BLACK"  : (  0,   0,   0),
+	"RED"    : (255,   0,   0),
+	"GREEN"  : (  0, 255,   0),
+	"BLUE"   : (  0,   0, 255),
+	"CYAN"   : (  0, 255, 255),
+	"MAGENTA": (255,   0, 255),
+	"YELLOW" : (255, 255,   0),
+};
+
+
+def approx_equal(a, b, tolerance):
+	return abs(a - b) <= max(abs(a), abs(b)) * tolerance
+
+
+class Vec2(object):
+	def __init__(self, x=0, y=0):
+		self.x = x
+		self.y = y
+
+	def __add__(self, other):
+		return Vec2(self.x + other.x, self.y + other.y)
+
+	def __sub__(self, other):
+		return Vec2(self.x - other.x, self.y - other.y)
+
+	def __mul__(self, other):
+		return Vec2(self.x * other, self.y * other)
+
+	def __neg__(self):
+		return Vec2(-self.x, -self.y)
+
+	def __str__(self):
+		return "{{ {}, {} }}".format(self.x, self.y)
+
+	@staticmethod
+	def dot(a, b):
+		return a.x * b.x + a.y * b.y
+
+	def length(self):
+		return math.sqrt(self.x * self.x + self.y * self.y)
+
+	def normalized(self):
+		l = self.length()
+		res = Vec2(self.x / l, self.y / l)
+		assert approx_equal(res.length(), 1.0, 0.000001)
+		return res
+
+	def rotated(self, angle):
+		# NOTE: rotation is counterclockwise
+		sa = math.sin(angle)
+		ca = math.cos(angle)
+		res = Vec2(self.x * ca - self.y * sa, self.x * sa + self.y * ca)
[…]

### 2016-12-17 robosim/robosim.py
Increase object visualization size

@@ -479,8 +479,8 @@ class Visualization(object):
 
 		col = Color[color]
 		if shape is Shape.CIRCLE:
-			r = 5.0
-			pygame.draw.circle(self.screen, col, center, 5)
+			r = 10
+			pygame.draw.circle(self.screen, col, center, r)
 		elif shape is Shape.RECT:
 			l = 5.0
 			v1 = (transform.position + -transform.right * l - transform.forward * l).to_int_array()

### 2016-12-18 robosim/robosim.py
Implement hack to slow down angular movement speed

@@ -298,6 +298,9 @@ class DiffSteer(object):
 		return res
 
 	def move(self, wheel_set, position, rotation, delta_time):
+		# NOTE: when moving forwards/backwards increase speed (hack)
+		if wheel_set.left.direction == wheel_set.right.direction:
+			delta_time *= 30.0
 		pos = self._pos(wheel_set, position, rotation, delta_time)
 		rot = self._rot(wheel_set, rotation, delta_time)
 		return pos, rot
@@ -369,12 +372,12 @@ class Sensor(VisObject):
 
 
 class Agent(VisObject):
-	def __init__(self, color):
+	def __init__(self, color, velocity=1.0):
 		super(Agent, self).__init__(Shape.HOUSE, color)
 		self.controller = None
 		self._sensors = []
 		self.steering = DiffSteer()
-		self.wheels = WheelSet(velocity=1.0)
+		self.wheels = WheelSet(velocity=velocity)
 
 	def __str__(self):
 		return super(Agent, self).__str__()
@@ -542,7 +545,7 @@ def main():
 	world = World(size=WORLD_SIZE)
 	vis = Visualization(world.size)
 
-	agent = Agent(color="RED")
+	agent = Agent(color="RED", velocity=0.05)
 	agent.transform.local_position = Vec2(10, 10)
 	#agent.transform.local_orientation = Rot2(-math.pi / 4.0)
 	agent.transform.local_orientation = Rot2(-math.pi / 3.0)

### 2016-12-18 robosim/robosim.py
Make vehicle rotate right by default

@@ -393,8 +393,8 @@ class Agent(VisObject):
 			self._sensors.append(sensor)
 
 	def step(self, objects, delta_time):
-		self.wheels.left = WheelDir.NONE
-		self.wheels.right = WheelDir.NONE
+		self.wheels.left = WheelDir.FORWARDS
+		self.wheels.right = WheelDir.BACKWARDS
 		max_similarity_left = 0.0
 		max_similarity_right = 0.0
 		for s in self._sensors:

### 2016-12-18 robosim/robosim.py
Store wheel direction instead of velocity and fix scenario

@@ -226,7 +226,7 @@ class Wheel(object):
 	def __init__(self, velocity, wheel_dir=WheelDir.NONE):
 		self.hrr = HRR(random.random())
 		self.velocity = velocity
-		self._value = self.value = wheel_dir
+		self._direction = self.direction = wheel_dir
 
 	def _dir_to_val(self, wheel_dir):
 		assert isinstance(wheel_dir, WheelDir)
@@ -240,12 +240,17 @@ class Wheel(object):
 			raise NotImplementedError
 
 	@property
-	def value(self):
-		return self._value * self.velocity
+	def direction(self):
+		return self._direction
 
-	@value.setter
-	def value(self, value):
-		self._value = self._dir_to_val(value)
+	@direction.setter
+	def direction(self, value):
+		assert isinstance(value, WheelDir)
+		self._direction = value
+
+	@property
+	def value(self):
+		return self._dir_to_val(self._direction) * self.velocity
 
 
 class WheelSet(object):
@@ -259,7 +264,7 @@ class WheelSet(object):
 
 	@left.setter
 	def left(self, value):
-		self._left.value = value
+		self._left.direction = value
 
 	@property
 	def right(self):
@@ -267,7 +272,7 @@ class WheelSet(object):
 
 	@right.setter
 	def right(self, value):
-		self._right.value = value
+		self._right.direction = value
 
 
 class DiffSteer(object):
@@ -405,27 +410,21 @@ class Agent(VisObject):
 			for obj, val in output:
 				obj_ctl = sensor_ctl % obj.hrr
 				actions = obj_ctl / self.wheels.left.hrr
-				print ("s {} actions o {}: {}".format(s.transform.local_position, obj.color, actions))
+				print("s: {} l: {}".format(s.transform.local_position, actions))
 				for a in actions:
 					if a[1] > max_similarity_left:
-						try:
-							self.wheels.left = WheelDir(a[0])
-							max_similarity_left = a[1]
-						except: pass
+						self.wheels.left = WheelDir(a[0])
+						max_similarity_left = a[1]
 				actions = obj_ctl / self.wheels.right.hrr
+				print("s: {} r: {}".format(s.transform.local_position, actions))
[…]

### 2016-12-18 robosim/robosim.py
Rotate vehicle randomly on start

@@ -547,8 +547,8 @@ def main():
 
 	agent = Agent(color="RED", velocity=0.05)
 	agent.transform.local_position = Vec2(10, 10)
-	#agent.transform.local_orientation = Rot2(-math.pi / 4.0)
-	agent.transform.local_orientation = Rot2(-math.pi / 3.0)
+	#agent.transform.local_orientation = Rot2(-math.pi / 3.0)
+	agent.transform.local_orientation = Rot2(random.random() * 2.0 * math.pi)
 	sensor1 = Sensor(color="GREEN", field_of_view=0.2*math.pi)
 	sensor1.transform.local_position = Vec2(-3, 0)
 	sensor1.transform.local_orientation = Rot2(0.08 * math.pi)

### 2016-12-18 papers/hrr-paper/paper.tex
Added Coordinate Encoding subsection

@@
 
-	\subsection{Encoding scalar symbol as radial basis functions}
+	\subsection{Encoding scalar symbols}
 
@@
 to number of symbols stored in the lookup table.
+
+	\subsection{Encoding coordinate symbols}
+
+		Encoding coordinate symbols works in a manner very similar to encoding scalar symbols.
+Depending on the number of coordinates the symbolic vectors shape is reinterpreted.
+2D coordinates, for instance, require a matrix.
+This matrix represents the entire coordinate space and on it 2D Gaussian distributions are sampled.
+It can be viewed as a heat map, as displayed in figure \ref{fig:encoding-coord}.	The matrix will still be treated as a vector when it comes to running operations on it and must also be permuted.
+Since the value space now has more dimensions the size of the vector has to be raised accordingly to achieve performance similar to that of scalar symbol encoding.
+
+		An attempt has been made to overcome the curse of dimensionality by splitting the vector up in the number of dimensions and simply encoding the value for each dimension in the resulting sub-vectors.
+Unfortunately it then becomes impossible to differentiate among multiple coordinates encoded in the same vector.
+Specifically, when decoding, there is no way to know which of the values in separate sub-vectors belong to each other and which don't.
+On the other hand if only a single coordinate needs to be bound to another symbol this approach is still feasible and will permit the use of smaller vectors for high accuracy.
+Concretely, for $d$ dimensions, splitting up the vector will require the size to be raised by a factor of $d$ to maintain the same accuracy.
+Reinterpreting the shape will require the size to increase exponentially by the power of $d$ to keep the accuracy.
 

### 2016-12-18 papers/hrr-paper/paper.tex
More Corections - semi-final

@@
 		In this paper we extend the HRR approach by introducing implicit,
-		topology-preserving, encoding/decoding procedures using radial
+		topology-preserving encoding/decoding procedures using radial
 		basis functions.
@@
 		\includegraphics[width=0.9\columnwidth]{img/probe_for_pen_w_img.png}
-		\caption{In-memory representation of top-down attention shift for visual scene short-term memory.
-Result shows attention distribution for a symbol "pen".
-In probabilistic sense it can be understood as probability of pen being at a certain position.}
+		\caption{In-memory representation of a top-down attention shift for visual scene short-term memory.
+The result shows attention distribution for a symbol "pen".
+In probabilistic sense it can be understood as the probability of a pen being at a certain position.}
 	\end{figure}
@@
 
-	\textbf{Association} (also called "binding") is an operation of linking two operands together, resulting in a vector of the same size which is dissimilar (or orthogonal) to the original vectors, but also contains scrambled information from both of them.
+	\textbf{Association} (also called "binding") is the operation of linking two operands together, resulting in a vector of the same size which is dissimilar (or orthogonal) to the original vectors, but also contains scrambled information from both of them.
 For instance, linking the property "red" to object "triangle" can be done using the binding operation as follows:
@@
 
-	\textbf{Superposition} is the operation of extending a set of items that have already been memorized with another item (or binding of two or more of them).
-As an example, a memory of "red triangle and blue circle" can be formed in following way:
+	\textbf{Superposition} is the operation of extending a set of items, regardless of what is already contained in them.
+As an example, a memory of "red triangle and blue circle" can be formed in the following way:
 	\begin{equation}
@@
 
-	The probing operation assumes the existence of an inverse element to association, so the previous equation can be interpreted and explained in following way:
+	The probing operation assumes the existence of inverse elements, so the previous equation can be interpreted and explained as such:
 	\begin{multline}
@@
 
-	where $triangle'$ represents inverse of $triangle$.
+	Here $triangle'$ represents the inverse of $triangle$.
 The resulting vector will be a composition of something that is very similar to $red$ and something that doesn't resemble anything meaningful from the symbol table, so it can be treated as negligible noise.	A usual way of computing similarity is the cosine distance, which for two vectors \pmb x and \pmb y is calculated as follows:
@@
 
-	The process of converting a noisy result of probing into the closest known symbol is called the \textbf{clean-up procedure}.
+	The process of converting the noisy result of probing into the closest known symbol is called the \textbf{clean-up procedure}.
 A straightforward way of implementing clean-up memory is using a lookup table, while other researchers show that any type of attractor network can be used (e.g. self-organizing maps).
@@
 With the help of a threshold for the similarity value false-positives can be excluded.
-A look-up requires O(M), where M is the number of symbols known to the system.
+A look-up requires O(n), where $n$ is the number of symbols known to the system.
 This approach works quite well for object identifiers (names), but has some non-desirable properties when used on scalar encoding.
-	//TODO Lookup Example
-
-	This will consequently increase space complexity and may become infeasible, depending on the type of input used.
-While looking for existing elements may not require the entire table to be checked probing for non-existent ones will always traverse all entries only to show up empty at the end.When handling scalars symbolic encoding can be done by discretization of the whole input range into bins and assigning a random vector to each discrete value.
+The space complexity will increase and may become infeasible, depending on the number of inputs needed.
+One way of handling symbolic scalar encoding is to discretize the whole input range into bins and assigning a random vector to each discrete value.
 This however may often prove to not satisfy the task needs any more.
@@
 	Holographic Reduced Representations are VSAs which implement the operation of binding as circular convolution.
-An option to calculating this is with the help of discrete Fast Fourier Transformations, in short FFTs.
+One option for calculating it is with the help of discrete Fast Fourier Transformations, in short FFTs.
 Taking $f(x)$ to describe an FFT, with $f^{-1}(x)$ as its inverse, circular convolution can be calculated as follows:
@@
 
-	where \pmb a is the result of convolution, and \pmb x and \pmb y are symbolic vectors of size $N$.
-Superposition is implemented as a simple element-wise vector addition. Taking the result of the previously displayed convolution and superposing it with some vector \pmb b is done as follows:
+	where $\pmb a$ is the result of convolution, and $\pmb x$ and $\pmb y$ are symbolic vectors of size $n$.
+Superposition is implemented as a simple element-wise vector addition. Taking the result of the previously displayed convolution and superposing it with some vector $\pmb b$ is done as follows:
 
@@
 
-The resulting vector of the superposition operation \pmb m can then be probed by using the inverse of circular convolution, which is circular correlation.
+The resulting vector of the superposition operation $\pmb m$ can then be probed by using the inverse of circular convolution, which is circular correlation.
 Plainly put probing can be viewed as binding with the "inverse" of a vector in Fourier space:
@@
 	\begin{equation}
-	\pmb y' = f^{-1}(f(\pmb m) * f(\pmb x)^{-1})
+	\pmb y^* = f^{-1}(f(\pmb m) * f(\pmb x)^{-1})
 	\end{equation}
 
-Following the previous formulas as a series of operations the vector \pmb y' will be similar to vector \pmb y, but not entirely the same due to the noisy influence of vector \pmb b.
-The inverse referred to here is gained by calculating the complex conjugate of the vector's entries.
+Following the previous formulas as a series of operations the vector $\pmb y^*$ will be similar to vector $\pmb y$, but not entirely the same due to the noisy influence of vector $\pmb b$.
+The inverse in Fourier space referred to here is gained by calculating the complex conjugate of the vector's entries.
 Complex conjugates are simply the same values with negated imaginary parts.
@@
 Due to this, when probing, we would receive vectors which had the correct relative distance between their values, i.e.
-the correct "shape", but would be shifted, stretched or squeezed on the Y-axis.This lead to vectors falsely being regarded as dissimilar to each other, and can be solved by performing two normalization steps:
+the correct "shape", but would be shifted, stretched or squeezed along the Y-axis.
+This lead to vectors falsely being regarded as dissimilar to each other, and can be solved by performing two normalization steps before comparing:
 
@@
 And yet figure \ref{no-perm-b} presents no such outcome.
-While there is a peak at the initial value which is probed for lots of other peaks also arise, making it impossible to detect which one is correct.
+While there is a peak at the initial value lots of other peaks also arise, making it impossible to detect which one is correct.
 
@@
 
-	This effect is due to the fact that circular convolution is based on Fourier transformations and the lack of frequencies present in encoded vectors becomes apparent in Fourier space as well.
-Figure \ref{fft} highlights this.
-All the information of a Gaussian distribution is crammed into the lowest and highest values of the Fourier transformation, resulting in a high loss.
+	This effect is due to the fact that circular convolution is based on Fourier transformations.
+A lack of frequencies in the Fourier space of the encoded scalar becomes apparent, as highlighted in figure \ref{fft}.
+All the information of a Gaussian distribution is crammed into the lowest and highest values of the Fourier transformation, resulting in a high loss of information.
 In these circumstances, when probing for a scalar, the vector received is in turn recreated of too few frequencies and will not come close to resembling the original Gaussian distribution.
@@
 	\includegraphics[width=\columnwidth]{img/scalar-random-fft.png}
-	\caption{Fourier analysis of 1D symbols: Gaussian distribution (top row) and same dimensional vector randomly sampled from normal distribution (bottom row).
-It is obvious that latter is uniformly spread across the whole vector, while the former is concentrated around 2 boundary values leading to increased interference between multiple items stored one over another (when added in Fourier space).}
+	\caption{Fourier analysis of 1D symbols: a Gaussian distribution (top row) and a randomly sampled vector of the same size (bottom row).
+It is obvious that the latter's information in Fourier space is uniformly spread across the whole length, while the former's is concentrated around 2 boundary points.}
 	\label{fft}
@@
 The result in figure \ref{perm-b} clearly shows a spike at the expected spot in the sample range.
-This vector can be smoothed out, after which the peak can easily be identified and the initial scalar can be recovered.
+This vector can now be smoothed out, after which the peak can easily be identified and the initial scalar can be recovered.
 
@@
 		\end{subfigure}
-		\caption{Figure \ref{perm-a} shows the binding of the permuted Gaussian distribution for value 8 on a scale to 10 with the symbolic representation of "ball", which is random.
-In figure \ref{perm-b} "ball" is being probed, and the expected result is a Gaussian distribution for 8, mixed with some noise.}
+		\caption{Figure \ref{perm-a} shows the binding of the permuted Gaussian distribution for the value 8 on a scale to 10 with the symbolic representation of "ball", which is random.
+In figure \ref{perm-b} "ball" is being probed, and the expected result is a Gaussian distribution for the value8, mixed with some noise.}
 		\label{perm}
@@
 
-	Algorithms 1 and 2 show, respectively, pseudo code for pipeline before and after the suggested modification are introduced.
+	Algorithms 1 and 2 show the operations pipeline before and after the suggested modification are introduced in pseudo code.
 
@@
 			\begin{algorithmic}[1]
-				\State $P \gets chooseRandomPermutation(N)$
+				\State $P \gets chooseRandomPermutation(n)$
 				\State $m \gets initEmptyMemory()$
 				\ForAll{$(symbol_1, symbol_2)$}
-				\State $enc_1 \gets FFT(permute(enc(symbol_1, N), P))$
-				\State $enc_2 \gets FFT(permute(enc(symbol_2, N), P))$
-				\State $m \gets m + enc_1 \otimes enc_2$
+				\State $enc_1 \gets FFT(permute(enc(symbol_1, n), P))$
+				\State $enc_2 \gets FFT(permute(enc(symbol_2, n), P))$
+				\State $m \gets m + IFFT(enc_1 \otimes enc_2)$
 				\EndFor	
 				\Function{ProbeMemory}{memory, op}
-				\State $r \gets permute(IFFT(memory \oslash op), P^{-1})$
+				\State $r \gets IFFT(FFT(memory) \oslash FFT(op))$
+				\State $r \gets permute(r, P^{-1})$
 				\State $cleanResult \gets argmax(r)$
@@
 		In contrast, Algorithm 2 shows pipeline with proposed changes.
-First line chooses a fixed random permutation of $N$ elements used throughout the whole process.
+First line chooses a fixed random permutation of $n$ elements used throughout the whole process.
 It can bee seen that there is no initial loop to assign symbolic representations to all symbols.
-They are, instead, constructed according to need using function $enc(value, N)$, which returns discrete sampled normal distribution vector of N elements, centered around $value$.
+They are, instead, constructed according to need using function $enc(value, n)$, which returns discrete sampled normal distribution vector of $n$ elements, centered around $value$.
 This perfectly sampled normal distribution is permuted using permutation $P$ in lines 4 and 5, so its frequency representation contains uniform spread over the whole spectrum, as explained earlier in this chapter.
@@
 				\includegraphics[width=1\columnwidth]{img/capacity.png}
-				\caption{Binding of pairs of random vectors (original pipeline).}
+				\caption{Binding pairs of random vectors (original pipeline).}
 				\label{fig:capacity}
@@
 	In this experiment a system is given a monocular stream as an input.
-An arbitrary algorithm is used to perform object detection and recognition, resulting in number of 2D coordinates associated with respective object names (figure \ref{fig:object-detection}).
-Object names are strings and are encoded as random vectors of length N, sampled from normal distribution (figure \ref{fig:encoding-object}).
-Locations of object in image plane are 2D coordinates $(x,y)$ and they are perceptually grounded symbols (figure \ref{fig:encoding-coord}).
+An arbitrary algorithm is used to perform object detection and recognition, resulting in a number of 2D coordinates associated with respective object names (figure \ref{fig:object-detection}).
+Object names are strings and are encoded as random vectors of length $n$, which are sampled from a normal distribution (figure \ref{fig:encoding-object}).
+The locations of objects in the image plane are 2D coordinates $(x,y)$ and they are perceptually grounded symbols (figure \ref{fig:encoding-coord}).
 
@@
 			\includegraphics[width=0.6\columnwidth]{img/map_original.jpg}
-			\caption{Original scene and set of detected objects}
+			\caption{Original scene and a set of detected objects}
 			\label{fig:object-detection}
@@
 			\includegraphics[width=\linewidth]{img/coord_example_1.png}
-			\caption{Encoding of (x,y) location for "watch"}
+			\caption{Encoding of location (x,y) for "watch"}
 			\label{fig:encoding-coord}
@@
 			\includegraphics[width=\linewidth]{img/coord_example_2.png}
-			\caption{Encoding of "watch" object ID as randomly sampled vector}
+			\caption{Encoding of the "watch" object ID as a randomly sampled vector}
 			\label{fig:encoding-object}
@@
 				\includegraphics[width=\linewidth]{img/probe_for_pen.png}
-				\caption{Probing for "pen" return mixture of Gaussian distributions}
+				\caption{Probing for "pen" returns location probability with two areas.}
 				\label{fig:probing-double}
@@
 However, even though this is the case, the similarity measure of bound symbols is consistently higher and can be clearly distinguished from others.
-Chart \ref{pgf:bar1} represents the result of probing at (19, -26.75), which is somewhere in between the keys and the red pen, as seen in figure \ref{fig:object-detection}.
+Chart \ref{pgf:bar1} represents the result of probing at $(19, -26.75)$, which is somewhere in between the keys and the red pen, as seen in figure \ref{fig:object-detection}.
 
-	 As we can see all symbols that are nowhere near the position present similarities well below 5 \%, while both close matches scored over 20 \%.
-Spot on probes may even attain values of over 50 \%.
-The example in chart \ref{pgf:bar2} is for a probe at(-13, 21.5), which is further away from the center of an object region.
+	 As we can see all symbols that are nowhere near the position present similarities well below $0.05$ (values may also be negative), while both close matches scored over $0.2$.
+Spot on probes may even attain values of over $0.5$.
+The example in chart \ref{pgf:bar2} is for a probe at $(-13, 21.5)$, which is further away from the center of an object region.
 But even though the dark pen and the wallet are further apart the result of probing still yields distinctly higher similarities for them as opposed to objects further away.
@@
                 (keys,   0.22827929349034107)
-                (mouse, 0.023035819302988644)
+                (mouse, -0.023035819302988644)
                 (mug, 0.025309361445942102)
@@
                 (wallet, 0.034187368731921304)
-                (watch, 0.018549398363469777)
+                (watch, -0.018549398363469777)
             };
@@
             \addplot[ybar,fill=blue] coordinates {
-                (keys,   0.020032173214673016)
+                (keys,   -0.020032173214673016)
                 (mouse, 0.027742071303527464)
@@
 
-We have used our system to demonstrate a mechanism for encoding neural programs and processes through series of associated action, perception and actuator symbols.
+We have used our system to demonstrate a mechanism for encoding neural programs and processes through a series of associated action, perception and actuator symbols.
 We call this mechanism for defining controllers using holographic memories "symbolic scripting".
@@
 
-An example of this kind of symbolic script is given on figure \ref{fig:symbolic-scripting}. Memory encodes light following behavior.
+An example of this kind of symbolic script is given in figure \ref{fig:symbolic-scripting}. Here the memory encodes a light following behaviour.
 
@@
 As a consequence, our approach eliminates the need for clean-up memories as they are described in literature.
-Instead, result of probing operation directly gives interpretable symbol, which can be decoded in constant computational time.
-In other words, time needed for encoding/decoding is completely ignorant of total number of symbols memorized, allowing memories that can store large corpus of different symbols.
-	A concrete biophysical evidence and theoretical model of implementation of convolution in brain is, unfortunately, still missing.
+Instead, results of probing operations directly give interpretable symbols, which can be decoded in constant computational time.
+In other words, time needed for encoding/decoding is completely ignorant of the total number of symbols memorized, allowing memories that can store a large corpus of different symbols.
+	A concrete biophysical evidence and theoretical model of implementation of convolution in the brain is, unfortunately, still missing.
 

### 2016-12-18 vsa/legend.py

@@ -7,5 +7,7 @@ def getLegend(v,start):
     for i in range(sh):
         plt.plot(v[i], linestyles[3-i*4/sh], label=start*pow(2,i))
     plt.axis([0,len(v[0]),0,1.01])
+    plt.xlabel('Bindings')
+    plt.ylabel('Accuracy')
     legend = plt.legend(loc='lower left', shadow=True, fontsize='x-large')
     plt.show()

### 2016-12-18 robosim/robosim.py
Switch to individual controllers for each sensor/wheel

@@ -224,7 +224,6 @@ class Transform(object):
 
 class Wheel(object):
 	def __init__(self, velocity, wheel_dir=WheelDir.NONE):
-		self.hrr = HRR(random.random())
 		self.velocity = velocity
 		self._direction = self.direction = wheel_dir
 
@@ -323,9 +322,6 @@ class VisObject(object):
 	def __init__(self, shape, color):
 		self.transform = Transform()
 
-		# use random value to uniquely identify this object in HRR
-		self.hrr = HRR(random.random())
-
 		assert isinstance(shape, Shape)
 		self.shape = shape
 		assert Color.has_key(color)
@@ -370,16 +366,23 @@ class Sensor(VisObject):
 			if pos_vs >= 0.0 and pos_vs <= 1.0:
 				#print("{} - {}: {}".format(self.transform.local_position, o.color, pos_vs))
 				if output is None:
-					output = o.hrr * pos_vs
+					output = HRR(o) * pos_vs
 				else:
-					output += o.hrr * pos_vs
-		return self.hrr * output if output is not None else self.hrr
+					output += HRR(o) * pos_vs
+		return HRR(self) * output if output is not None else HRR(self)
+
+
+class Controller(object):
+	def __init__(self, controller, sensor, wheel):
+		self.controller = controller
+		self.sensor = sensor
+		self.wheel = wheel
 
 
 class Agent(VisObject):
 	def __init__(self, color, velocity=1.0):
 		super(Agent, self).__init__(Shape.HOUSE, color)
-		self.controller = None
+		self.controllers = []
 		self._sensors = []
 		self.steering = DiffSteer()
 		self.wheels = WheelSet(velocity=velocity)
@@ -400,28 +403,22 @@ class Agent(VisObject):
 	def step(self, objects, delta_time):
 		self.wheels.left = WheelDir.FORWARDS
 		self.wheels.right = WheelDir.BACKWARDS
-		max_similarity_left = 0.0
-		max_similarity_right = 0.0
-		for s in self._sensors:
-			#print("S: {}".format(s))
-			output = s.read(objects)
-			# probe controller with sensed value for current sensor
-			sensor_ctl = self.controller % s.hrr
+
+		for c in self.controllers:
[…]

### 2016-12-18 vsa/hrr.py
Normalize vector after encoding

@@ -274,9 +274,9 @@ class HRR(VSA):
             result = np.empty(self.size, dtype=float)
          
             if isinstance(input_value, float) or isinstance(input_value, numbers.Integral):
-                result = self.permute(self.scalar_encoder(input_value, self.size, encode_range[0]))
+                result = self.permute(helpers.normalize(self.scalar_encoder(input_value, self.size, encode_range[0])))
             elif isinstance(input_value, (frozenset, list, np.ndarray, set, tuple)):
-                result = self.permute(self.coordinate_encoder(input_value, encode_range))
+                result = self.permute(helpers.normalize(self.coordinate_encoder(input_value, encode_range)))
             else:    
                 result = self.generateVector() 
                 HRR.mapping[input_value] = result

### 2016-12-18 papers/hrr-paper/paper.tex
New images, few corrections

@@
 		of symbolic concepts, represented as fixed-length vectors in
-		${\rm I\!R}^N$.
+		${\rm I\!R}^n$.
 		A subset of VSAs, Holographic Reduced Representations (HRRs),
@@
 
-	In the case of look-up tables, in order to decode a specific symbolic vector, the elements from a symbol table are iterated over, the similarity to each of the entries is calculated and the symbol which presented maximum similarity is returned.
+	In the case of lookup tables, in order to decode a specific symbolic vector, the elements from a symbol table are iterated over, the similarity to each of the entries is calculated and the symbol which presented maximum similarity is returned.
 With the help of a threshold for the similarity value false-positives can be excluded.
-A look-up requires O(n), where $n$ is the number of symbols known to the system.
+A lookup requires O(n), where $n$ is the number of symbols known to the system.
 This approach works quite well for object identifiers (names), but has some non-desirable properties when used on scalar encoding.
@@
 			\State $enc_2 \gets FFT(t_{symbol_2})$
-			\State $m \gets m + IFFT(enc_1 \otimes enc_2$)
+			\State $m \gets m + IFFT(enc_1 * enc_2$)
 			\EndFor		
 			\Function{ProbeMemory}{memory, op}
-			\State $result\gets IFFT(FFT(memory)\oslash FFT(op))$
+			\State $result\gets IFFT(FFT(memory)* FFT(op)^{-1})$
 
@@
 	Lines 1-3 assign a random vector representation to each symbol known to the system prior to any other operations.
-This lookup table is stored in array $t$.
-Lines 4-9 initialize the memory $m$ with arbitrary amount of pairs of associated scalars.
-Function $ProbeMemory(memory, op)$ returns symbol associated with provided $op$.
-Line 11 performs circular correlation and stores noisy result of unbinding in $s$.
+This lookup table is stored in an array $t$.
+Lines 4-9 initialize the memory $m$ with an arbitrary amount of pairs of associated scalars.
+Function $ProbeMemory(memory, op)$ returns a symbol associated with provided $op$.
+Line 11 performs circular correlation and stores the noisy result of unbinding in $s$.
 Lines 12-18 loop through the whole lookup table and find the maximum similarity vector to $s$.
@@
 				\State $enc_2 \gets FFT(permute(enc(symbol_2, n), P))$
-				\State $m \gets m + IFFT(enc_1 \otimes enc_2)$
+				\State $m \gets m + IFFT(enc_1 * enc_2)$
 				\EndFor	
 				\Function{ProbeMemory}{memory, op}
-				\State $r \gets IFFT(FFT(memory) \oslash FFT(op))$
+				\State $r \gets IFFT(FFT(memory) * FFT(op)^{-1})$
 				\State $r \gets permute(r, P^{-1})$
@@
 
-		In contrast, Algorithm 2 shows pipeline with proposed changes.
-First line chooses a fixed random permutation of $n$ elements used throughout the whole process.
-It can bee seen that there is no initial loop to assign symbolic representations to all symbols.
-They are, instead, constructed according to need using function $enc(value, n)$, which returns discrete sampled normal distribution vector of $n$ elements, centered around $value$.
-This perfectly sampled normal distribution is permuted using permutation $P$ in lines 4 and 5, so its frequency representation contains uniform spread over the whole spectrum, as explained earlier in this chapter.
-Probing operation consists of applying inverse permutation $P^{-1}$ after IFFT (line 9).
-Since this gives a noisy version of initial normal distribution (shown in figure \ref{perm-b}), the only thing that needs to be done is to identify the mean of the distribution.
-Complexity of this operation is linear w.r.t.
-length of the vector $N$, while in case of Algorithm 1 it is linear w.r.t.
+		In contrast, Algorithm 2 shows a pipeline with our proposed changes.
+The first line chooses a fixed random permutation of $n$ elements used throughout the whole process.
+There is no initial loop to assign symbolic representations to all symbols.
+They are, instead, constructed according to need using function $enc(value, n)$.
+This function returns a discrete sampled Gaussian distribution vector of $n$ elements, centred around a chosen $value$.
+The vector is then permuted using a permutation $P$ in lines 4 and 5, so its frequency representation contains uniform spread over the whole spectrum, as explained earlier in this chapter.
+The probing operation consists of applying an inverse permutation $P^{-1}$ after IFFT (line 10).
+Since this returns a noisy version of the initial Gaussian distribution (shown in figure \ref{perm-b}), the only thing that needs to be done is to identify the peak of the distribution.
+The complexity of this operation is linear w.r.t.
+length of the vector $n$, while in the case of Algorithm 1 it is linear w.r.t.
 to number of symbols stored in the lookup table.
@@
 				\includegraphics[width=1\columnwidth]{img/capacity.png}
-				\caption{Binding pairs of random vectors (original pipeline).}
+				\caption{Binding pairs of random vectors. Accuracy decreases with more bindings.}
 				\label{fig:capacity}
@@
 An arbitrary algorithm is used to perform object detection and recognition, resulting in a number of 2D coordinates associated with respective object names (figure \ref{fig:object-detection}).
-Object names are strings and are encoded as random vectors of length $n$, which are sampled from a normal distribution (figure \ref{fig:encoding-object}).
+Object names are strings and are encoded as random vectors of length $n$, which are sampled from a Gaussian distribution (figure \ref{fig:encoding-object}).
 The locations of objects in the image plane are 2D coordinates $(x,y)$ and they are perceptually grounded symbols (figure \ref{fig:encoding-coord}).

### 2016-12-18 vsa/legend.py

@@ -5,7 +5,7 @@ def getLegend(v,start):
     sh = len(v)
     linestyles = ['-', '--', '-.', ':']
     for i in range(sh):
-        plt.plot(v[i], linestyles[3-i*4/sh], label=start*pow(2,i))
+        plt.plot(v[i], linestyles[3-i*4/sh], label=start*pow(4,i))
     plt.axis([0,len(v[0]),0,1.01])
     plt.xlabel('Bindings')
     plt.ylabel('Accuracy')

### 2016-12-18 papers/hrr-paper/paper.tex
Corrected some paragraphs.

--- 2016-12-18 papers/hrr-paper/paper.tex
@@
 	% Do not put math or special symbols in the title.
-	\title{Perceptual Symbol Grounding in \\Holographic Memories}
+	\title{Making scalars work in  \\Holographic Memories}
 
@@
 		memory and are, as such, interesting for computational modeling.
-
 		In this paper we extend the HRR approach by introducing implicit,
-		topology-preserving, encoding/decoding procedures using radial
-		basis functions.
-		This involves randomly chosen permutations for encoding and
+		topology-preserving encoding and decoding procedures.
+		We propose moving away from traditional exact symbolic representation
+		to probabilistic one, replacing unique symbol identifiers with 
+		probability density function.
+		As we discover, this requires randomly chosen permutations for encoding and
 		their corresponding inverse for decoding. These are necessary
-		for the uniform distribution of signals in Fourier space where
+		for the uniform distribution of signals across Fourier space where
 		embedding takes place.
 		These novel encoding schemes, together with the extended operation
-		pipeline, are akin to so-called \emph{clean-up modules after memory
-		retrieval} (e.g., self-organizing maps). Effectively, encoding
-		implicitly represents the symbol, so no further lookup is needed.
-
-		We show that our encoding scheme does not have a negative impact
+		pipeline, are eliminating the need for so-called \emph{clean-up modules} after memory
+		retrieval (e.g., self-organizing maps). Effectively, encoding
+		implicitly represents the scalar symbol, so no further lookup is needed.
+		We show that our encoding scheme has a positive impact
 		on memory capacity in comparison to the original capacity
@@
 		\cite{Plate:1995:HolographicReducedRepresentations}.
-		We also evaluate our memories in different robotics tasks: top-down visual
+		We also evaluate our memories in two different robotics tasks: top-down visual
 		attention shift and state machine scripting (holographic
@@
 Authors in \cite{Golosio:2015:CognitiveNeuralArchitecture} have used them to solve word embedding problem for extremely large dataset by replacing computationally expensive big matrix factorization with an iterative estimation algorithm based on HRRs.
-Some of the other work is centered around pattern recognition \cite{Kleyko:2016:PatternRecognitionVector}, functional large-scale cognitive architecture models \cite{Eliasmith:2012:LargeScaleModel} and representing scene structure \cite{scene-structure}.
+Some of the other work is centered around pattern recognition \cite{Kleyko:2016:PatternRecognitionVector} and functional large-scale cognitive architecture models \cite{Eliasmith:2012:LargeScaleModel}.
 Preliminary theoretical assumptions have been made about the ability to use them as agent controllers \cite{Levy:2013:LearningBehaviorHierarchies}, where a symbolic program is represented with a set of combined symbolic actions associated with actuator symbols and symbolic sensing.
@@
 	The process of converting a noisy result of probing into the closest known symbol is called the \textbf{clean-up procedure}.
-A straightforward way of implementing clean-up memory is using a lookup table, while other researchers show that any type of attractor network can be used (e.g. self-organizing maps).
+A straightforward way of implementing clean-up memory is using a lookup table, while other researchers show that any type of attractor network can be used (e.g.
+self-organizing maps).
+//TODO REFERENCE NEEDED
 
@@
 A look-up requires O(M), where M is the number of symbols known to the system.
-This approach works quite well for object identifiers (names), but has some non-desirable properties when used on scalar encoding.
-	//TODO Lookup Example
-
-	This will consequently increase space complexity and may become infeasible, depending on the type of input used.
-While looking for existing elements may not require the entire table to be checked probing for non-existent ones will always traverse all entries only to show up empty at the end.When handling scalars symbolic encoding can be done by discretization of the whole input range into bins and assigning a random vector to each discrete value.
-This however may often prove to not satisfy the task needs any more.
+This approach works quite well for object identifiers (names), but has some non-desirable properties when used on scalar encoding, which will be discussed in the following chapters.
 
@@
 
-	\subsection{Encoding scalar symbols}
+	\subsection{Encoding scalar symbol as radial basis functions}
 
@@
 
-	\subsection{Encoding coordinate symbols}
-
-		Encoding coordinate symbols works in a manner very similar to encoding scalar symbols.
-Depending on the number of coordinates the symbolic vectors shape is reinterpreted.
-2D coordinates, for instance, require a matrix.
-This matrix represents the entire coordinate space and on it 2D Gaussian distributions are sampled.
-It can be viewed as a heat map, as displayed in figure \ref{fig:encoding-coord}.	The matrix will still be treated as a vector when it comes to running operations on it and must also be permuted.
-Since the value space now has more dimensions the size of the vector has to be raised accordingly to achieve performance similar to that of scalar symbol encoding.
-
-		An attempt has been made to overcome the curse of dimensionality by splitting the vector up in the number of dimensions and simply encoding the value for each dimension in the resulting sub-vectors.
-Unfortunately it then becomes impossible to differentiate among multiple coordinates encoded in the same vector.
-Specifically, when decoding, there is no way to know which of the values in separate sub-vectors belong to each other and which don't.
-On the other hand if only a single coordinate needs to be bound to another symbol this approach is still feasible and will permit the use of smaller vectors for high accuracy.
-Concretely, for $d$ dimensions, splitting up the vector will require the size to be raised by a factor of $d$ to maintain the same accuracy.
-Reinterpreting the shape will require the size to increase exponentially by the power of $d$ to keep the accuracy.
-
 	\section{Properties of holographic memories}
@@
 
-	In this experiment a system is given a monocular stream as an input.
-An arbitrary algorithm is used to perform object detection and recognition, resulting in number of 2D coordinates associated with respective object names (figure \ref{fig:object-detection}).
-Object names are strings and are encoded as random vectors of length N, sampled from normal distribution (figure \ref{fig:encoding-object}).
-Locations of object in image plane are 2D coordinates $(x,y)$ and they are perceptually grounded symbols (figure \ref{fig:encoding-coord}).
-
 	\begin{figure}[th!]
@@
 	\end{figure}
+
+	In this experiment a system is given a monocular stream as an input.
+An arbitrary algorithm is used to perform object detection and recognition, resulting in number of 2D coordinates associated with respective object names (figure \ref{fig:object-detection}).
+Object names are strings and are encoded as random vectors of length N, sampled from normal distribution (figure \ref{fig:encoding-object}).
+Locations of object in image plane are 2D coordinates $(x,y)$ and they are perceptually grounded symbols (figure \ref{fig:encoding-coord}).
 

### 2016-12-18 robosim/robosim.py
Switch to single sensor in agent

@@ -373,10 +373,9 @@ class Sensor(VisObject):
 
 
 class Controller(object):
-	def __init__(self, controller, sensor, wheel):
+	def __init__(self, controller, sensor):
 		self.controller = controller
 		self.sensor = sensor
-		self.wheel = wheel
 
 
 class Agent(VisObject):
@@ -406,16 +405,26 @@ class Agent(VisObject):
 
 		for c in self.controllers:
 			output = c.sensor.read(objects)
-			max_similarity = 0.1  # NOTE: 0.1 as a similarity threshold
+			max_similarity_left = 0.1  # NOTE: 0.1 as a similarity threshold
+			max_similarity_right = 0.1  # NOTE: 0.1 as a similarity threshold
 			for obj, val in output:
 				obj_ctl = c.controller % HRR(obj)
-				actions = obj_ctl / float(val)
-				print("s: {} {} a: {}".format(c.sensor.transform.local_position, val, actions))
+				actions_ctl = obj_ctl % float(val)
+				actions = actions_ctl / HRR(self.wheels.left)
+				print("{} {} al: {}".format(obj.color, val, actions))
 				for a in actions:
-					if a[1] > max_similarity:
+					if a[1] > max_similarity_left:
 						try:
-							c.wheel.direction = WheelDir(a[0])
-							max_similarity = a[1]
+							self.wheels.left.direction = WheelDir(a[0])
+							max_similarity_left = a[1]
+						except: pass
+				actions = actions_ctl / HRR(self.wheels.right)
+				print("{} {} ar: {}".format(obj.color, val, actions))
+				for a in actions:
+					if a[1] > max_similarity_right:
+						try:
+							self.wheels.right.direction = WheelDir(a[0])
+							max_similarity_right = a[1]
 						except: pass
 		print ("al: {} ar: {}".format(self.wheels.left.direction , self.wheels.right.direction))
 
@@ -545,18 +554,14 @@ def main():
 	world = World(size=WORLD_SIZE)
 	vis = Visualization(world.size)
 
-	agent = Agent(color="RED", velocity=0.05)
+	agent = Agent(color="RED", velocity=0.07)
[…]

### 2016-12-18 papers/hrr-paper/paper.tex

--- 2016-12-18 papers/hrr-paper/paper.tex
@@
 		memory and are, as such, interesting for computational modeling.
-
 		In this paper we extend the HRR approach by introducing implicit,
-		topology-preserving encoding/decoding procedures using radial
-		basis functions.
-		This involves randomly chosen permutations for encoding and
+		topology-preserving encoding and decoding procedures.
+		We propose moving away from traditional exact symbolic representation
+		to probabilistic one, replacing unique symbol identifiers with 
+		probability density function.
+		As we discover, this requires randomly chosen permutations for encoding and
 		their corresponding inverse for decoding. These are necessary
-		for the uniform distribution of signals in Fourier space where
+		for the uniform distribution of signals across Fourier space where
 		embedding takes place.
 		These novel encoding schemes, together with the extended operation
-		pipeline, are akin to so-called \emph{clean-up modules after memory
-		retrieval} (e.g., self-organizing maps). Effectively, encoding
-		implicitly represents the symbol, so no further lookup is needed.
-
-		We show that our encoding scheme does not have a negative impact
+		pipeline, are eliminating the need for so-called \emph{clean-up modules} after memory
+		retrieval (e.g., self-organizing maps). Effectively, encoding
+		implicitly represents the scalar symbol, so no further lookup is needed.
+		We show that our encoding scheme has a positive impact
 		on memory capacity in comparison to the original capacity
@@
 With the help of a threshold for the similarity value false-positives can be excluded.
-A lookup requires O(n), where $n$ is the number of symbols known to the system.
+A lookup requires $O(n)$, where $n$ is the number of symbols known to the system.
 This approach works quite well for object identifiers (names), but has some non-desirable properties when used on scalar encoding.
@@
 	\begin{figure}[th!]
-		\center
-		\begin{subfigure}{1.0\columnwidth}
-			\center
-			\includegraphics[width=0.6\columnwidth]{img/map_original.jpg}
-			\caption{Original scene and a set of detected objects}
-			\label{fig:object-detection}
-		\end{subfigure}
 
-		\begin{subfigure}{0.45\columnwidth}
-			\center
-			\includegraphics[width=\linewidth]{img/coord_example_1.png}
-			\caption{Encoding of location (x,y) for "watch"}
-			\label{fig:encoding-coord}
-		\end{subfigure}
-		\begin{subfigure}{0.45\columnwidth}
-			\center
-			\includegraphics[width=\linewidth]{img/coord_example_2.png}
-			\caption{Encoding of the "watch" object ID as a randomly sampled vector}
-			\label{fig:encoding-object}
-		\end{subfigure}
 		\begin{subfigure}{0.8\columnwidth}
@@
 			\includegraphics[width=\linewidth]{img/probe_for_pen.png}
-				\caption{Probing for "pen" returns location probability with two areas.}
+			\caption{Probing for "pen" return mixture of Gaussian distributions}
 			\label{fig:probing-double}

### 2016-12-18 papers/hrr-paper/paper.tex
Fixed missing graph images.
Corrected figure spacing.

@@
 	% Do not put math or special symbols in the title.
-	\title{Making scalars work in  \\Holographic Memories}
+	\title{Probabilistic symbol encoding for \\convolutional associative memories}
 
@@
 		${\rm I\!R}^n$.
-		A subset of VSAs, Holographic Reduced Representations (HRRs),
+		A specific instance of VSAs, Holographic Reduced Representations (HRRs),
 		have proven to exhibit properties similar to human short-term
@@
 		\cite{Plate:1995:HolographicReducedRepresentations}.
-		We also evaluate our memories in two different robotics tasks: top-down visual
-		attention shift and state machine scripting (holographic
-		controllers).
+		We also evaluate our memories in two different robotics tasks: visual scene memory and state machine scripting (holographic controllers).
 	\end{abstract}
@@
 		\includegraphics[width=0.9\columnwidth]{img/probe_for_pen_w_img.png}
-		\caption{In-memory representation of a top-down attention shift for visual scene short-term memory.
-The result shows attention distribution for a symbol "pen".
-In probabilistic sense it can be understood as the probability of a pen being at a certain position.}
+		\caption{In-memory representation of visual scene short-term memory. The result shows probability distribution for a symbol "pen" being at certain position in scene.}
 	\end{figure}
@@
 	\caption{Fourier analysis of 1D symbols: a Gaussian distribution (top row) and a randomly sampled vector of the same size (bottom row).
-It is obvious that the latter's information in Fourier space is uniformly spread across the whole length, while the former's is concentrated around 2 boundary points.}
+It is obvious that the latter's information in Fourier space is uniformly spread across the whole spectrum, while the former's is concentrated around 2 boundary points.}
 	\label{fft}
@@
 		\includegraphics[width=\columnwidth]{img/scalar-perm-step-fft.png}
-		\caption{Plots on the effect of permuting a Gaussian distribution, and the impact on Fourier space.}
+		\caption{Applying random permutation to a sampled Gaussian distribution results in more discrete changes in signal, which correspond to high-frequency components in Fourier space.
+This makes frequency spectrum spread more uniform, which is a desirable property for HRRs.
+Although this scrambling of initial signal makes it seem random, the fact that the same permutation is used in all encodings keeps two semantically close values having very similar representations, thus preserving their semantic proximity.
+}
 		\label{perm-fft}
@@
 		\end{subfigure}
-		\caption{Figure \ref{perm-a} shows the binding of the permuted Gaussian distribution for the value 8 on a scale to 10 with the symbolic representation of "ball", which is random.
-In figure \ref{perm-b} "ball" is being probed, and the expected result is a Gaussian distribution for the value8, mixed with some noise.}
+		\caption{Figure \ref{perm-a} shows the binding of the permuted Gaussian distribution for the value 8 from range [1, 10] with the symbolic representation of "ball", which is random.
+In figure \ref{perm-b} "ball" is being probed, and the result after inverse permutation is a Gaussian distribution for the value 8, mixed with some noise.}
 		\label{perm}
@@
 			\center
-			\begin{subfigure}{0.45\columnwidth}
+			\begin{subfigure}{1\columnwidth}
 				\center
-				\includegraphics[width=1\columnwidth]{img/capacity_coordinate.png}
+				\includegraphics[width=0.5\columnwidth]{img/capacity_coordinate.png}
 				\caption{Binding pairs of one 2D coordinate and a random symbol, then probing for the scalar.}
@@
 	\begin{figure}[th!]
+		\center
+		\begin{subfigure}{1.0\columnwidth}
+			\center
+			\includegraphics[width=0.6\columnwidth]{img/map_original.jpg}
+			\caption{Original scene and a set of detected objects}
+			\label{fig:object-detection}
+		\end{subfigure}
+
+		\begin{subfigure}{0.45\columnwidth}
+			\center
+			\includegraphics[width=\linewidth]{img/coord_example_1.png}
+			\caption{Encoding of location (x,y) for "watch"}
+			\label{fig:encoding-coord}
+		\end{subfigure}
+		\begin{subfigure}{0.45\columnwidth}
+			\center
+			\includegraphics[width=\linewidth]{img/coord_example_2.png}
+			\caption{Encoding of the "watch" object ID as a randomly sampled vector}
+			\label{fig:encoding-object}
+		\end{subfigure}
 

### 2016-12-18 vsa/hrr.py
Igor wants to go!

@@ -278,7 +278,7 @@ class HRR(VSA):
             elif isinstance(input_value, (frozenset, list, np.ndarray, set, tuple)):
                 result = self.permute(helpers.normalize(self.coordinate_encoder(input_value, encode_range)))
             else:    
-                result = self.generateVector() 
+                result = helpers.normalize(self.generateVector()) 
                 HRR.mapping[input_value] = result
             if self.visualize:    
                 print("Encoded ", input_value)    

### 2016-12-18 robosim/robosim.py
Add NO_OBJECT state for controller

@@ -39,7 +39,6 @@ Color = {
 	"YELLOW" : (255, 255,   0),
 };
 
-
 def approx_equal(a, b, tolerance):
 	return abs(a - b) <= max(abs(a), abs(b)) * tolerance
 
@@ -249,7 +248,8 @@ class Wheel(object):
 
 	@property
 	def value(self):
-		return self._dir_to_val(self._direction) * self.velocity
+		# NOTE: hack from Igor (always move forwards)
+		return self._dir_to_val(self._direction) * self.velocity + 0.2
 
 
 class WheelSet(object):
@@ -374,6 +374,7 @@ class Sensor(VisObject):
 
 class Controller(object):
 	def __init__(self, controller, sensor):
+		self.NO_OBJECT = None
 		self.controller = controller
 		self.sensor = sensor
 
@@ -381,6 +382,7 @@ class Controller(object):
 class Agent(VisObject):
 	def __init__(self, color, velocity=1.0):
 		super(Agent, self).__init__(Shape.HOUSE, color)
+		self.target = None
 		self.controllers = []
 		self._sensors = []
 		self.steering = DiffSteer()
@@ -400,32 +402,58 @@ class Agent(VisObject):
 			self._sensors.append(sensor)
 
 	def step(self, objects, delta_time):
-		self.wheels.left = WheelDir.FORWARDS
-		self.wheels.right = WheelDir.BACKWARDS
+		self.wheels.left = WheelDir.NONE
+		self.wheels.right = WheelDir.NONE
 
 		for c in self.controllers:
 			output = c.sensor.read(objects)
-			max_similarity_left = 0.1  # NOTE: 0.1 as a similarity threshold
-			max_similarity_right = 0.1  # NOTE: 0.1 as a similarity threshold
+
+			max_similarity_left = 0.1
+			wheel_dir_left = None
+			max_similarity_right = 0.1
+			wheel_dir_right = None
+
+			# TODO: make it more beautiful
 			for obj, val in output:
-				obj_ctl = c.controller % HRR(obj)
-				actions_ctl = obj_ctl % float(val)
+				if obj is self.target:
+					actions_ctl = c.controller % val
+					actions = actions_ctl / HRR(self.wheels.left)
+					print("val: {} l: {}".format(val, actions))
+					for a in actions:
+						if a[1] > max_similarity_left:
+							try:
[…]

### 2016-12-19 papers/hrr-paper/paper.tex
Corrected pseudocode.
Small Correction
Added images to experiment

@@
 	% Do not put math or special symbols in the title.
-	\title{Probabilistic symbol encoding for \\convolutional associative memories}
+	\title{Probabilistic Symbol Encoding for \\Convolutional Associative Memories}
 
@@
 			\center
-			\begin{subfigure}{1\columnwidth}
+			\begin{subfigure}{0.45\columnwidth}
 				\center
-				\includegraphics[width=0.5\columnwidth]{img/capacity_coordinate.png}
+				\includegraphics[width=1\columnwidth]{img/capacity_coordinate.png}
 				\caption{Binding pairs of one 2D coordinate and a random symbol, then probing for the scalar.}
@@
 
+		\begin{figure}[th!]
+			\begin{subfigure}{0.45\columnwidth}
+				\center
+				\includegraphics[width=1\columnwidth]{img/gaussianbar.png}
+				\caption{Gaussian distribution without permutation.}
+				\label{fig:gaussianbar}
+			\end{subfigure}
+			\begin{subfigure}{0.45\columnwidth}
+				\center
+				\includegraphics[width=1\columnwidth]{img/gaussianbarperm.png}
+				\caption{Gaussian distribution with permutation.\\
+				}
+				\label{fig:gaussianbarperm}
+			\end{subfigure}	
+		\caption{Sensory input of an objects positions in the visual field at two points in time. A comparison between the raw generated input and its permuted version can be seen.}
+		\label{gaussian}
+		\end{figure}
+
 	\section{Conclusions}

### 2016-12-19 papers/hrr-paper/paper.tex
Realigned two images
corrected some captions

@@
 
-	To facilitate these two qualities scalar encoding can be achieved with the help of radial basis functions. Among these functions one of the options are Gaussian distributions.
-The encoded vector can simply represent a Gaussian sampled over a fixed input range.
+	To facilitate these two qualities scalar encoding can be achieved using probabilistic instead of exact symbolic representation. 
+The encoded vector can simply be a Gaussian shaped probability distribution sampled over a fixed input range, with mean equal to the encoded value and arbitrarily chosen standard deviation.
 Figure \ref{no-perm-a} shows how such an encoded vector looks like, and what the result of binding it to a generic random vector is.
@@
 	\end{subfigure}
-	\caption{Symbolic scripting example for light following behavior of a two-wheeled robot}
+	\caption{Symbolic scripting illustration for object following behavior of a two-wheeled robot}
 	\label{fig:symbolic-scripting}
@@
 
-An example of this kind of symbolic script is given in figure \ref{fig:symbolic-scripting}. Here the memory encodes a light following behaviour.
+An example of this kind of symbolic script is given in figure \ref{fig:symbolic-scripting}. Here the memory encodes an object following behavior for left wheel.
 
@@
 				\includegraphics[width=1\columnwidth]{img/gaussianbar.png}
-				\caption{Gaussian distribution without permutation.}
+				\caption{Gaussian probability distribution for raw input value}
 				\label{fig:gaussianbar}
 			\end{subfigure}
-			\begin{subfigure}{0.45\columnwidth}
+			\begin{subfigure}{0.54\columnwidth}
 				\center
 				\includegraphics[width=1\columnwidth]{img/gaussianbarperm.png}
-				\caption{Gaussian distribution with permutation.\\
+				\caption{Probabilistic symbolic encoding suitable for HRR after permutation
 				}
@@
 			\end{subfigure}	
-		\caption{Sensory input of an objects positions in the visual field at two points in time. A comparison between the raw generated input and its permuted version can be seen.}
+		\caption{Sensory input encoding of target object position in the visual field at two successive points in time.
+Left graph shows original encodings for two adjacent values and right graph shows permuted encodings.
+It can be seen that semantically close input values result in similar HRR encodings.}
 		\label{gaussian}

### 2016-12-19 papers/hrr-paper/paper.tex
Added more text to second experiment

--- 2016-12-19 papers/hrr-paper/paper.tex
@@
 				\includegraphics[width=1\columnwidth]{img/gaussianbarperm.png}
-				\caption{Gaussian distribution with permutation.\\
+				\caption{Gaussian distribution with permutation.
 				}
@@
 		\caption{Sensory input of an objects positions in the visual field at two points in time. A comparison between the raw generated input and its permuted version can be seen.}
-		\label{gaussian}
+		\label{fig:gaussian}
 		\end{figure}
+
+	In our experiment we have extended the detection of light to a position along the visual field, reduced to the X-axis, rather than just binary statements like "light is visible to the left".
+To visualize the difference chart \ref{fig:gaussianbar} shows the position of light for two consecutive time steps.
+The value $0$ represents the far left corner of the sensor, and $1$ the far right one.
+The chart can be viewed as a (normalized) probability of light being at a certain position, and both cases show it being somewhere right of the center.
+Chart \ref{fig:gaussianbarperm} shows what the Gaussian distributions look like when they are permuted.
+This shape of theirs is then used as a symbol.
+Concretely, instead of encoding a random symbol for "light\_left" we encode a scalar representing the position of light along the visual field and bind it with the rest of the controller components.
+Accordingly, when running the experiment, once the light reaches a position encoded in the controller it will issue new commands to the vehicle.
 

### 2016-12-19 papers/hrr-paper/paper.tex

--- 2016-12-19 papers/hrr-paper/paper.tex
@@
 It can be seen that semantically close input values result in similar HRR encodings.}
-		\label{gaussian}
+		\label{fig:gaussian}
 		\end{figure}
+
+	In our experiment we have extended the detection of light to a position along the visual field, reduced to the X-axis, rather than just binary statements like "light is visible to the left".
+To visualize the difference chart \ref{fig:gaussianbar} shows the position of light for two consecutive time steps.
+The value $0$ represents the far left corner of the sensor, and $1$ the far right one.
+The chart can be viewed as a (normalized) probability of light being at a certain position, and both cases show it being somewhere right of the center.
+Chart \ref{fig:gaussianbarperm} shows what the Gaussian distributions look like when they are permuted.
+This shape of theirs is then used as a symbol.
+Concretely, instead of encoding a random symbol for "light\_left" we encode a scalar representing the position of light along the visual field and bind it with the rest of the controller components.
+Accordingly, when running the experiment, once the light reaches a position encoded in the controller it will issue new commands to the vehicle.
 

### 2016-12-19 robosim/robosim.py
Implement scatter plot for sensor result

@@ -2,8 +2,12 @@ import math
 import pygame
 import random
 
+import numpy as np
+import matplotlib.pyplot as plt
+
 from enum import Enum
 from pygame.locals import *
+from collections import deque
 
 import sys
 sys.path.append("../vsa/")
@@ -354,7 +358,7 @@ class Sensor(VisObject):
 			rel_pos = self.transform.local_transformed_vector(o.transform.position)
 			pos_vs = self._to_view_space(rel_pos.normalized())
 			if pos_vs >= 0.0 and pos_vs <= 1.0:
-				output.append((o, pos_vs))
+				output.append((o, pos_vs, rel_pos.length()))
 		return output
 
 	def read_hrr(self, objects):
@@ -388,6 +392,12 @@ class Agent(VisObject):
 		self.steering = DiffSteer()
 		self.wheels = WheelSet(velocity=velocity)
 
+		# state variables - read only
+		self.target_position_vs = np.NAN
+		self.target_distance = np.NAN
+		self.similarity_left = [np.NAN, np.NAN]
+		self.similarity_right = [np.NAN, np.NAN]
+
 	def __str__(self):
 		return super(Agent, self).__str__()
 
@@ -414,27 +424,46 @@ class Agent(VisObject):
 			wheel_dir_right = None
 
 			# TODO: make it more beautiful
-			for obj, val in output:
+			for obj, val, dist in output:
 				if obj is self.target:
+					self.target_position_vs = val
+					self.target_distance = dist
+
 					actions_ctl = c.controller % val
 					actions = actions_ctl / HRR(self.wheels.left)
 					print("val: {} l: {}".format(val, actions))
 					for a in actions:
-						if a[1] > max_similarity_left:
-							try:
-								wheel_dir_left = WheelDir(a[0])
-								max_similarity_left = a[1]
-							except: pass
+						wd = None
+						try: wd = WheelDir(a[0])
+						except: pass
+						if wd is not None and a[1] > max_similarity_left:
+							wheel_dir_left = wd
+							max_similarity_left = a[1]
+						if wd is WheelDir.FORWARDS:
+							self.similarity_left[0] = a[1]
+						elif wd is WheelDir.BACKWARDS:
+							self.similarity_left[1] = a[1]
 					actions = actions_ctl / HRR(self.wheels.right)
 					print("val: {} r: {}".format(val, actions))
[…]

### 2016-12-19 robosim/robosim.py
Add plots for similarity to direction of wheels

@@ -534,10 +534,8 @@ class Visualization(object):
 		self.screen = pygame.display.set_mode(size)
 		self.plot_pipeline = plot_pipeline
 
-		d1 = np.empty(num_pipeline_entries, dtype=np.float)
-		d1.fill(np.NAN)
-		d2 = np.empty(num_pipeline_entries, dtype=(np.float, np.float))
-		#d2.fill((np.NAN, np.NAN))
+		d1 = np.full(num_pipeline_entries, np.NAN, dtype='float32')
+		d2 = np.full(num_pipeline_entries, [np.NAN, np.NAN], dtype='2float32')
 		self._pipeline_inputs = deque(d1, num_pipeline_entries)
 		self._pipeline_similarity_l = deque(d2, num_pipeline_entries)
 		self._pipeline_similarity_r = deque(d2, num_pipeline_entries)
@@ -548,18 +546,60 @@ class Visualization(object):
 		pygame.display.flip()
 
 		plt.ion()
-		self.fig = plt.figure(figsize=(5,3))
-		self.ax = self.fig.add_axes([0, 0, 1, 1], frameon=False)
-		self.ax.set_xlim(0, 1)
-		self.ax.set_xticks([])
-		self.ax.set_ylim(0, num_pipeline_entries)
-		self.ax.set_yticks([])
-		self.scat = self.ax.scatter(
+
+		self.fig = plt.figure(figsize=(6,10))
+		self.ax1 = self.fig.add_subplot(4, 1, 1)
+		self.ax2 = self.fig.add_subplot(4, 1, 2)
+		self.ax3 = self.fig.add_subplot(4, 1, 3)
+		self.ax4 = self.fig.add_subplot(4, 1, 4)
+
+		#self.ax = self.fig.add_axes([0, 0, 1, 1], frameon=False)
+		self.ax1.set_xlim(0, 1)
+		#self.ax1.set_xticks([])
+		self.ax1.set_ylim(0, num_pipeline_entries)
+		self.ax1.set_ylim(self.ax1.get_ylim()[::-1])
+		self.ax1.set_yticks([])
+		self.scat1 = self.ax1.scatter(
 				self._pipeline_inputs,
 				np.arange(num_pipeline_entries),
 				linewidths=0.5,
 				alpha=0.5,
 				c=[[1.0, 0.31, 0.0]])
+
+		self.ax2.set_xlim(0, num_pipeline_entries)
+		self.ax2.set_xticks([])
+		self.ax2.set_xlabel("Similarity Left Wheel")
[…]

### 2016-12-19 robosim/robosim.py
Also plot similarity when no object is found

@@ -467,18 +467,28 @@ class Agent(VisObject):
 				actions_ctl = c.controller % c.NO_OBJECT
 				actions = actions_ctl / HRR(self.wheels.left)
 				for a in actions:
-					if a[1] > max_similarity_left:
-						try:
-							wheel_dir_left = WheelDir(a[0])
-							max_similarity_left = a[1]
-						except: pass
+					wd = None
+					try: wd = WheelDir(a[0])
+					except: pass
+					if wd is not None and a[1] > max_similarity_left:
+						wheel_dir_left = wd
+						max_similarity_left = a[1]
+					if wd is WheelDir.FORWARDS:
+						self.similarity_left[0] = a[1]
+					elif wd is WheelDir.BACKWARDS:
+						self.similarity_left[1] = a[1]
 				actions = actions_ctl / HRR(self.wheels.right)
 				for a in actions:
-					if a[1] > max_similarity_right:
-						try:
-							wheel_dir_right = WheelDir(a[0])
-							max_similarity_right = a[1]
-						except: pass
+					wd = None
+					try: wd = WheelDir(a[0])
+					except: pass
+					if wd is not None and a[1] > max_similarity_right:
+						wheel_dir_right = wd
+						max_similarity_right = a[1]
+					if wd is WheelDir.FORWARDS:
+						self.similarity_right[0] = a[1]
+					elif wd is WheelDir.BACKWARDS:
+						self.similarity_right[1] = a[1]
 
 			self.wheels.left = wheel_dir_left
 			self.wheels.right = wheel_dir_right
@@ -555,13 +565,15 @@ class Visualization(object):
 
 		#self.ax = self.fig.add_axes([0, 0, 1, 1], frameon=False)
 		self.ax1.set_xlim(0, 1)
-		#self.ax1.set_xticks([])
+		self.ax1.set_xticks([])
+		self.ax1.set_xlabel("Sensory Input Left to Right")
 		self.ax1.set_ylim(0, num_pipeline_entries)
 		self.ax1.set_ylim(self.ax1.get_ylim()[::-1])
 		self.ax1.set_yticks([])
 		self.scat1 = self.ax1.scatter(
 				self._pipeline_inputs,
 				np.arange(num_pipeline_entries),
+				s=3,
 				linewidths=0.5,
 				alpha=0.5,
[…]

### 2016-12-19 robosim/robosim.py
Rotate sensor input plot

@@ -564,15 +564,15 @@ class Visualization(object):
 		self.ax4 = self.fig.add_subplot(4, 1, 4)
 
 		#self.ax = self.fig.add_axes([0, 0, 1, 1], frameon=False)
-		self.ax1.set_xlim(0, 1)
+		self.ax1.set_xlim(0, num_pipeline_entries)
 		self.ax1.set_xticks([])
-		self.ax1.set_xlabel("Sensory Input Left to Right")
-		self.ax1.set_ylim(0, num_pipeline_entries)
-		self.ax1.set_ylim(self.ax1.get_ylim()[::-1])
-		self.ax1.set_yticks([])
+		self.ax1.set_xlabel("Sensory Input")
+		self.ax1.set_ylim(0, 1)
+		#self.ax1.set_ylim(self.ax1.get_ylim()[::-1])
+		#self.ax1.set_yticks([])
 		self.scat1 = self.ax1.scatter(
-				self._pipeline_inputs,
 				np.arange(num_pipeline_entries),
+				self._pipeline_inputs,
 				s=3,
 				linewidths=0.5,
 				alpha=0.5,
@@ -657,7 +657,7 @@ class Visualization(object):
 			v5[1] = self._flip_y(v5[1])
 			pygame.draw.polygon(self.screen, col, [v1, v2, v4, v5])
 		elif shape is Shape.HOUSE:
-			l = 5.0
+			l = 7.0
 			v1 = (transform.position + -transform.right * l - transform.forward * l).to_int_array()
 			v2 = (transform.position + -transform.right  * l + transform.forward * l).to_int_array()
 			v3 = (transform.position + transform.forward * l * 2.0).to_int_array()
@@ -690,7 +690,7 @@ class Visualization(object):
 		self._pipeline_distance.append(agent.target_distance)
 
 	def _update_symbolic_pipeline_plot(self):
-		self.scat1.set_offsets(zip(self._pipeline_inputs, np.arange(len(self._pipeline_inputs))))
+		self.scat1.set_offsets(zip(np.arange(len(self._pipeline_inputs)), self._pipeline_inputs))
 		self.scat21.set_offsets(zip(np.arange(len(self._pipeline_similarity_l)), [a for a,_ in self._pipeline_similarity_l]))
 		self.scat22.set_offsets(zip(np.arange(len(self._pipeline_similarity_l)), [b for _,b in self._pipeline_similarity_l]))
[…]

### 2016-12-19 robosim/robosim.py
Add random targets and remove/add targets when close

@@ -530,6 +530,19 @@ class World(object):
 	def add_object(self, obj):
 		obj.transform.parent = self._transform
 		self.objects.append(obj)
+		return obj
+
+	def add_random_object(self):
+		idx = int(1 + ((len(Color.keys()) - 1) * random.random()))
+		obj = Object(color=Color.keys()[idx])
+		x = random.random() * (self.size[0] - 1)
+		y = random.random() * (self.size[1] - 1)
+		obj.transform.local_position = Vec2(x, y)
+		return self.add_object(obj)
+
+	def remove_target_object(self, agent):
+		self.objects.remove(agent.target)
+		agent.target = None
 
 	def step(self, delta_time):
 		for a in self.agents:
@@ -737,23 +750,26 @@ def main():
 
 	agent = Agent(color="RED", velocity=0.07)
 	agent.transform.local_position = Vec2(10, 10)
-	agent.transform.local_orientation = Rot2(-math.pi / 3.0)
-	#agent.transform.local_orientation = Rot2(random.random() * 2.0 * math.pi)
+	#agent.transform.local_orientation = Rot2(-math.pi / 3.0)
+	agent.transform.local_orientation = Rot2(random.random() * 2.0 * math.pi)
 	sensor1 = Sensor(color="GREEN", field_of_view=0.2*math.pi)
 	#sensor1.transform.local_position = Vec2(3, 0)
 	#sensor1.transform.local_orientation = Rot2(0.08 * math.pi)
 	agent.add_sensor(sensor1)
 	world.add_agent(agent)
 
-	obj1 = Object(color="CYAN")
-	obj1.transform.local_position = Vec2(50, 50)
-	obj2 = Object(color="MAGENTA")
-	obj2.transform.local_position = Vec2(400, 70)
-	obj3 = Object(color="YELLOW")
-	obj3.transform.local_position = Vec2(80, 80)
-	world.add_object(obj1)
-	world.add_object(obj2)
-	world.add_object(obj3)
+	#obj1 = Object(color="CYAN")
+	#obj1.transform.local_position = Vec2(50, 50)
+	#obj2 = Object(color="MAGENTA")
+	#obj2.transform.local_position = Vec2(400, 70)
+	#obj3 = Object(color="YELLOW")
+	#obj3.transform.local_position = Vec2(80, 80)
+	#world.add_object(obj1)
+	#world.add_object(obj2)
+	#world.add_object(obj3)
+	world.add_random_object()
+	world.add_random_object()
[…]

### 2016-12-19 robosim/robosim.py
Add legends to plots

@@ -586,6 +586,7 @@ class Visualization(object):
 		self.scat1 = self.ax1.scatter(
 				np.arange(num_pipeline_entries),
 				self._pipeline_inputs,
+				label="Similarity",
 				s=3,
 				linewidths=0.5,
 				alpha=0.5,
@@ -598,6 +599,7 @@ class Visualization(object):
 		self.scat21 = self.ax2.scatter(
 				np.arange(num_pipeline_entries),
 				[a for a,_ in self._pipeline_similarity_l],
+				label="Forwards",
 				s=3,
 				linewidths=0.5,
 				alpha=0.5,
@@ -605,10 +607,12 @@ class Visualization(object):
 		self.scat22 = self.ax2.scatter(
 				np.arange(num_pipeline_entries),
 				[b for _,b in self._pipeline_similarity_l],
+				label="Backwards",
 				s=3,
 				linewidths=0.5,
 				alpha=0.5,
 				c=[[0.0, 0.31, 1.0]])
+		self.ax2.legend(loc="lower left", handles=[self.scat21, self.scat22])
 
 		self.ax3.set_xlim(0, num_pipeline_entries)
 		self.ax3.set_xticks([])
@@ -617,6 +621,7 @@ class Visualization(object):
 		self.scat31 = self.ax3.scatter(
 				np.arange(num_pipeline_entries),
 				[a for a,_ in self._pipeline_similarity_r],
+				label="Forwards",
 				s=3,
 				linewidths=0.5,
 				alpha=0.5,
@@ -624,10 +629,12 @@ class Visualization(object):
 		self.scat32 = self.ax3.scatter(
 				np.arange(num_pipeline_entries),
 				[b for _,b in self._pipeline_similarity_r],
+				label="Backwards",
 				s=3,
 				linewidths=0.5,
 				alpha=0.5,
 				c=[[0.0, 0.31, 1.0]])
+		self.ax3.legend(loc="lower left", handles=[self.scat31, self.scat32])
 
 		self.ax4.set_xlim(0, num_pipeline_entries)
 		self.ax4.set_xticks([])
@@ -638,6 +645,7 @@ class Visualization(object):
 		self.scat4 = self.ax4.scatter(
 				np.arange(num_pipeline_entries),
 				self._pipeline_distance,
+				label="Distance",
 				s=3,
 				linewidths=0.5,
 				alpha=0.5,

### 2017-01-13 papers/hrr-paper/paper.tex
Realigned images, again
Added axes to object detection image
corrected some figure captions, extended conclusion.

@@
 	% affiliations
-	\author{\IEEEauthorblockN{Igor Peric, Alexandru Lesi, Daniel Spies, Stefan Ulbrich, R{\"u}diger Dillman, Marius Z{\"o}llner}
+	\author{\IEEEauthorblockN{Igor Peric, Alexandru Lesi, Daniel Spies, Stefan Ulbrich, Arne R{\"o}nnau, Marius Z{\"o}llner, R{\"u}diger Dillman}
 		\IEEEauthorblockA{FZI Forschungszentrum Informatik\\
 			Karlsruhe, Germany\\
-			Email: $\{$peric, lesi, spies, ulbrich, dillmann, zoellner$\}$@fzi.de}
+			Email: $\{$peric, lesi, spies, ulbrich, roennau, zoellner, dillmann$\}$@fzi.de}
 	}
@@
 		\caption{Plot of vector values.
-Figure \ref{no-perm-a} shows the binding of the value 8 on a scale to 10 with the symbolic representation of "ball", which is random.
-In figure \ref{no-perm-b} "ball" is being probed, and the expected result is a Gaussian distribution for 8, mixed with some noise.}
+Figure \ref{no-perm-a} shows the binding of the value 8 from representational range [0,10] with the symbolic representation of "ball" (which is randomly chosen), giving a representation of association.
+In figure \ref{no-perm-b} this resulting representation is probed with "ball" and the expected result is a Gaussian distribution for 8, mixed with some noise.
+As it can be seen, result is far from expected and numeric value cannot be inferred.}
 		\label{no-perm}
@@
 		\caption{Applying random permutation to a sampled Gaussian distribution results in more discrete changes in signal, which correspond to high-frequency components in Fourier space.
-This makes frequency spectrum spread more uniform, which is a desirable property for HRRs.
+This makes frequency spectrum more uniformly spread, which is a desirable property for HRRs.
 Although this scrambling of initial signal makes it seem random, the fact that the same permutation is used in all encodings keeps two semantically close values having very similar representations, thus preserving their semantic proximity.
@@
 			\center
-			\includegraphics[width=0.6\columnwidth]{img/map_original.jpg}
+			\includegraphics[width=0.6\columnwidth]{img/map_ticks.jpg}
 			\caption{Original scene and a set of detected objects}
@@
 				\includegraphics[width=1\columnwidth]{img/gaussianbar.png}
-				\caption{Gaussian probability distribution for raw input value}
+				\caption{Gaussian probability distribution for raw input value\\}
 				\label{fig:gaussianbar}
 			\end{subfigure}
-			\begin{subfigure}{0.54\columnwidth}
+			\begin{subfigure}{0.45\columnwidth}
 				\center
@@
 Instead, results of probing operations directly give interpretable symbols, which can be decoded in constant computational time.
-In other words, time needed for encoding/decoding is completely ignorant of the total number of symbols memorized, allowing memories that can store a large corpus of different symbols.
+In other words, time needed for encoding/decoding is completely independent of the total number of symbols memorized.\\
 	A concrete biophysical evidence and theoretical model of implementation of convolution in the brain is, unfortunately, still missing.
+Nevertheless, our work assumes convolution as the basic computational substrate of higher level cognition and identifies random permutation as computational requirement without which association of probabilistically encoded symbols is not possible.
 

### 2017-01-18 robosim/robosim.py
Switch from scatter to line plots

@@ -583,58 +583,53 @@ class Visualization(object):
 		self.ax1.set_ylim(0, 1)
 		#self.ax1.set_ylim(self.ax1.get_ylim()[::-1])
 		#self.ax1.set_yticks([])
-		self.scat1 = self.ax1.scatter(
+		self.line1, = self.ax1.plot(
 				np.arange(num_pipeline_entries),
 				self._pipeline_inputs,
 				label="Similarity",
-				s=3,
-				linewidths=0.5,
-				alpha=0.5,
-				c=[[1.0, 0.31, 0.0]])
+				lw=1.5,
+				alpha=0.7,
+				c=[1.0, 0.31, 0.0])
 
 		self.ax2.set_xlim(0, num_pipeline_entries)
 		self.ax2.set_xticks([])
 		self.ax2.set_xlabel("Similarity Left Wheel")
-		self.ax2.set_ylim(-1, 1)
-		self.scat21 = self.ax2.scatter(
+		self.ax2.set_ylim(-0.4, 0.4)
+		self.line21, = self.ax2.plot(
 				np.arange(num_pipeline_entries),
 				[a for a,_ in self._pipeline_similarity_l],
 				label="Forwards",
-				s=3,
-				linewidths=0.5,
-				alpha=0.5,
-				c=[[1.0, 0.31, 0.0]])
-		self.scat22 = self.ax2.scatter(
+				lw=1.5,
+				alpha=0.7,
+				c=[1.0, 0.31, 0.0])
+		self.line22, = self.ax2.plot(
 				np.arange(num_pipeline_entries),
 				[b for _,b in self._pipeline_similarity_l],
 				label="Backwards",
-				s=3,
-				linewidths=0.5,
-				alpha=0.5,
-				c=[[0.0, 0.31, 1.0]])
-		self.ax2.legend(loc="lower left", handles=[self.scat21, self.scat22])
+				lw=1.5,
+				alpha=0.7,
+				c=[0.0, 0.31, 1.0])
+		self.ax2.legend(loc="lower left", handles=[self.line21, self.line22])
 
 		self.ax3.set_xlim(0, num_pipeline_entries)
 		self.ax3.set_xticks([])
 		self.ax3.set_xlabel("Similarity Right Wheel")
-		self.ax3.set_ylim(-1, 1)
-		self.scat31 = self.ax3.scatter(
+		self.ax3.set_ylim(-0.4, 0.4)
+		self.line31, = self.ax3.plot(
[…]

### 2017-01-18 robosim/robosim.py
Make distance plot continuous

@@ -609,7 +609,21 @@ class Visualization(object):
 				lw=1.5,
 				alpha=0.7,
 				c=[0.0, 0.31, 1.0])
-		self.ax2.legend(loc="lower left", handles=[self.line21, self.line22])
+		self.line23, = self.ax2.plot(
+				np.arange(num_pipeline_entries),
+				[a for a,_ in self._pipeline_similarity_r],
+				label="Forwards",
+				lw=1.5,
+				alpha=0.7,
+				c=[1.0, 0.31, 0.0])
+		self.line24, = self.ax2.plot(
+				np.arange(num_pipeline_entries),
+				[b for _,b in self._pipeline_similarity_r],
+				label="Backwards",
+				lw=1.5,
+				alpha=0.7,
+				c=[0.0, 0.31, 1.0])
+		self.ax2.legend(loc="lower left", handles=[self.line21, self.line22, self.line23, self.line24])
 
 		self.ax3.set_xlim(0, num_pipeline_entries)
 		self.ax3.set_xticks([])
@@ -702,12 +716,14 @@ class Visualization(object):
 		self._pipeline_inputs.append(agent.target_position_vs)
 		self._pipeline_similarity_l.append(agent.similarity_left)
 		self._pipeline_similarity_r.append(agent.similarity_right)
-		self._pipeline_distance.append(agent.target_distance)
+		self._pipeline_distance.append(Vec2.length(agent.transform.position - agent.target.transform.position))
 
 	def _update_symbolic_pipeline_plot(self):
 		self.line1.set_data(np.arange(len(self._pipeline_inputs)), self._pipeline_inputs)
 		self.line21.set_data(np.arange(len(self._pipeline_similarity_l)), [a for a,_ in self._pipeline_similarity_l])
 		self.line22.set_data(np.arange(len(self._pipeline_similarity_l)), [b for _,b in self._pipeline_similarity_l])
+		self.line23.set_data(np.arange(len(self._pipeline_similarity_r)), [a for a,_ in self._pipeline_similarity_r])
+		self.line24.set_data(np.arange(len(self._pipeline_similarity_r)), [b for _,b in self._pipeline_similarity_r])
 		self.line31.set_data(np.arange(len(self._pipeline_similarity_r)), [a for a,_ in self._pipeline_similarity_r])
 		self.line32.set_data(np.arange(len(self._pipeline_similarity_r)), [b for _,b in self._pipeline_similarity_r])
[…]

### 2017-01-18 robosim/robosim.py
Add vertical line to plot for new target

@@ -384,9 +384,11 @@ class Controller(object):
 
 
 class Agent(VisObject):
+	TARGET_NEW_TIME = 1
+
 	def __init__(self, color, velocity=1.0):
 		super(Agent, self).__init__(Shape.HOUSE, color)
-		self.target = None
+		self._target = self.target = 0
 		self.controllers = []
 		self._sensors = []
 		self.steering = DiffSteer()
@@ -397,9 +399,19 @@ class Agent(VisObject):
 		self.target_distance = np.NAN
 		self.similarity_left = [np.NAN, np.NAN]
 		self.similarity_right = [np.NAN, np.NAN]
+		self.target_new = 0
 
 	def __str__(self):
 		return super(Agent, self).__str__()
+
+	@property
+	def target(self):
+		return self._target
+
+	@target.setter
+	def target(self, value):
+		self.target_new = Agent.TARGET_NEW_TIME + 1
+		self._target = value
 
 	def add_sensor(self, sensor=None):
 		if sensor is None:
@@ -412,6 +424,8 @@ class Agent(VisObject):
 			self._sensors.append(sensor)
 
 	def step(self, objects, delta_time):
+		self.target_new = max(0, self.target_new - 1) # decrease "target new time"
+
 		self.wheels.left = WheelDir.NONE
 		self.wheels.right = WheelDir.NONE
 
@@ -563,6 +577,7 @@ class Visualization(object):
 		self._pipeline_similarity_l = deque(d2, num_pipeline_entries)
 		self._pipeline_similarity_r = deque(d2, num_pipeline_entries)
 		self._pipeline_distance = deque(d1, num_pipeline_entries)
+		self._pipleline_new_target = deque(d1, num_pipeline_entries)
 
 		pygame.display.set_caption("robosim")
 		self.screen.fill(Color["WHITE"])
@@ -648,8 +663,9 @@ class Visualization(object):
 		self.ax4.set_xlim(0, num_pipeline_entries)
 		self.ax4.set_xticks([])
 		self.ax4.set_xlabel("Distance to Target")
-		w, h = self.screen.get_width(), self.screen.get_height()
-		max_len = math.sqrt(w * w + h * h)
+		#w, h = self.screen.get_width(), self.screen.get_height()
+		#max_len = math.sqrt(w * w + h * h)
+		max_len = 500
 		self.ax4.set_ylim(0, max_len)
 		self.line4, = self.ax4.plot(
[…]

### 2017-01-18 robosim/robosim.py
Add partially working sensory plot for no-object value

@@ -598,13 +598,23 @@ class Visualization(object):
 		self.ax1.set_ylim(0, 1)
 		#self.ax1.set_ylim(self.ax1.get_ylim()[::-1])
 		#self.ax1.set_yticks([])
-		self.line1, = self.ax1.plot(
-				np.arange(num_pipeline_entries),
-				self._pipeline_inputs,
+		sens_series = np.array(self._pipeline_inputs).astype(np.double)
+		sens_mask1 = np.isfinite(sens_series)
+		sens_mask2 = np.isnan(sens_series)
+		self.line11, = self.ax1.plot(
+				np.arange(num_pipeline_entries)[sens_mask1],
+				sens_series[sens_mask1],
 				label="Similarity",
 				lw=1.5,
 				alpha=0.7,
 				c=[1.0, 0.31, 0.0])
+		self.line12, = self.ax1.plot(
+				np.arange(num_pipeline_entries)[sens_mask2],
+				sens_series[sens_mask2],
+				label="Similarity",
+				lw=1.5,
+				alpha=0.9,
+				c=[1.0, 0.0, 0.0])
 
 		self.ax2.set_xlim(0, num_pipeline_entries)
 		self.ax2.set_xticks([])
@@ -736,7 +746,12 @@ class Visualization(object):
 		self._pipleline_new_target.append(agent.target_new > 0)
 
 	def _update_symbolic_pipeline_plot(self):
-		self.line1.set_data(np.arange(len(self._pipeline_inputs)), self._pipeline_inputs)
+		sens_series = np.array(self._pipeline_inputs).astype(np.double)
+		sens_mask1 = np.isfinite(sens_series)
+		sens_mask2 = np.isnan(sens_series)
+		self.line11.set_data(np.arange(len(self._pipeline_inputs))[sens_mask1], sens_series[sens_mask1])
+		self.line12.set_data(np.arange(len(self._pipeline_inputs))[sens_mask2], sens_series[sens_mask2])
+
 		self.line21.set_data(np.arange(len(self._pipeline_similarity_l)), [a for a,_ in self._pipeline_similarity_l])
 		self.line22.set_data(np.arange(len(self._pipeline_similarity_l)), [b for _,b in self._pipeline_similarity_l])
 		self.line23.set_data(np.arange(len(self._pipeline_similarity_r)), [a for a,_ in self._pipeline_similarity_r])

### 2017-01-19 robosim/robosim.py
Use OrderedDict for colors to allow filtering

@@ -7,7 +7,7 @@ import matplotlib.pyplot as plt
 
 from enum import Enum
 from pygame.locals import *
-from collections import deque
+from collections import deque, OrderedDict
 
 import sys
 sys.path.append("../vsa/")
@@ -32,16 +32,16 @@ class WheelDir(Enum):
 	NONE = "NONE"
 
 
-Color = {
-	"WHITE"  : (255, 255, 255),
-	"BLACK"  : (  0,   0,   0),
-	"RED"    : (255,   0,   0),
-	"GREEN"  : (  0, 255,   0),
-	"BLUE"   : (  0,   0, 255),
-	"CYAN"   : (  0, 255, 255),
-	"MAGENTA": (255,   0, 255),
-	"YELLOW" : (255, 255,   0),
-};
+Color = OrderedDict([
+	("WHITE"  , (255, 255, 255)),
+	("BLACK"  , (  0,   0,   0)),
+	("RED"    , (255,   0,   0)),
+	("GREEN"  , (  0, 255,   0)),
+	("BLUE"   , (  0,   0, 255)),
+	("CYAN"   , (  0, 255, 255)),
+	("MAGENTA", (255,   0, 255)),
+	("YELLOW" , (255, 255,   0)),
+])
 
 def approx_equal(a, b, tolerance):
 	return abs(a - b) <= max(abs(a), abs(b)) * tolerance

### 2017-01-19 robosim/robosim.py
Reset target info only if there is not target

@@ -437,6 +437,9 @@ class Agent(VisObject):
 			max_similarity_right = 0.1
 			wheel_dir_right = None
 
+			self.target_position_vs = np.NAN
+			self.target_distance = np.NAN
+
 			# TODO: make it more beautiful
 			for obj, val, dist in output:
 				if obj is self.target:
@@ -472,8 +475,8 @@ class Agent(VisObject):
 							self.similarity_right[1] = a[1]
 
 			if wheel_dir_left is None or wheel_dir_right is None:
-				self.target_position_vs = np.NAN
-				self.target_distance = np.NAN
+				print("NO WHEEL ACTION FOUND! l {} r {} tp {}".format(wheel_dir_left, wheel_dir_right, self.target_position_vs))
+
 				self.similarity_left = [np.NAN, np.NAN]
 				self.similarity_right = [np.NAN, np.NAN]
 

### 2017-01-19 robosim/robosim.py
Improve NO_OBJECT style in plot

@@ -602,11 +602,10 @@ class Visualization(object):
 		#self.ax1.set_ylim(self.ax1.get_ylim()[::-1])
 		#self.ax1.set_yticks([])
 		sens_series = np.array(self._pipeline_inputs).astype(np.double)
-		sens_mask1 = np.isfinite(sens_series)
 		sens_mask2 = np.isnan(sens_series)
 		self.line11, = self.ax1.plot(
-				np.arange(num_pipeline_entries)[sens_mask1],
-				sens_series[sens_mask1],
+				np.arange(num_pipeline_entries),
+				self._pipeline_inputs,
 				label="Similarity",
 				lw=1.5,
 				alpha=0.7,
@@ -615,8 +614,8 @@ class Visualization(object):
 				np.arange(num_pipeline_entries)[sens_mask2],
 				sens_series[sens_mask2],
 				label="Similarity",
-				lw=1.5,
-				alpha=0.9,
+				lw=8.0,
+				alpha=0.6,
 				c=[1.0, 0.0, 0.0])
 
 		self.ax2.set_xlim(0, num_pipeline_entries)
@@ -750,10 +749,12 @@ class Visualization(object):
 
 	def _update_symbolic_pipeline_plot(self):
 		sens_series = np.array(self._pipeline_inputs).astype(np.double)
-		sens_mask1 = np.isfinite(sens_series)
-		sens_mask2 = np.isnan(sens_series)
-		self.line11.set_data(np.arange(len(self._pipeline_inputs))[sens_mask1], sens_series[sens_mask1])
-		self.line12.set_data(np.arange(len(self._pipeline_inputs))[sens_mask2], sens_series[sens_mask2])
+		sens_mask = np.isnan(sens_series)
+		sens_series[np.isfinite(sens_series)] = np.nan
+		sens_series[sens_mask] = 0.5
+
+		self.line11.set_data(np.arange(len(self._pipeline_inputs)), self._pipeline_inputs)
+		self.line12.set_data(np.arange(len(self._pipeline_inputs)), sens_series)
 
 		self.line21.set_data(np.arange(len(self._pipeline_similarity_l)), [a for a,_ in self._pipeline_similarity_l])
 		self.line22.set_data(np.arange(len(self._pipeline_similarity_l)), [b for _,b in self._pipeline_similarity_l])

### 2017-01-19 robosim/robosim.py
Remove all current and add three new objects on reaching target

@@ -898,9 +898,12 @@ def main():
 		world.step(delta_time=1.0)
 		vis.update(world)
 
-		# remove and add new target if agent is close
+		# remove all obj and add new target if agent is close
 		if agent.target_distance < 50:
 			world.remove_target_object(agent)
+			world.objects = []
+			world.add_random_object()
+			world.add_random_object()
 			target_obj = world.add_random_object()
 			agent.target = target_obj
 

### 2017-01-19 robosim/robosim.py
Fix NO_OBJECT plot

@@ -609,14 +609,15 @@ class Visualization(object):
 				label="Similarity",
 				lw=1.5,
 				alpha=0.7,
-				c=[1.0, 0.31, 0.0])
+				c=[0.0, 0.31, 1.0])
 		self.line12, = self.ax1.plot(
 				np.arange(num_pipeline_entries)[sens_mask2],
 				sens_series[sens_mask2],
 				label="Similarity",
-				lw=8.0,
-				alpha=0.6,
-				c=[1.0, 0.0, 0.0])
+				lw=300.0,
+				alpha=0.4,
+				c=[1.0, 0.0, 0.0],
+				solid_capstyle="butt")
 
 		self.ax2.set_xlim(0, num_pipeline_entries)
 		self.ax2.set_xticks([])

### 2017-01-19 robosim/robosim.py
Fix new-target bar in plot

@@ -384,7 +384,7 @@ class Controller(object):
 
 
 class Agent(VisObject):
-	TARGET_NEW_TIME = 1
+	TARGET_NEW_TIME = 4
 
 	def __init__(self, color, velocity=1.0):
 		super(Agent, self).__init__(Shape.HOUSE, color)
@@ -680,13 +680,22 @@ class Visualization(object):
 		#max_len = math.sqrt(w * w + h * h)
 		max_len = 500
 		self.ax4.set_ylim(0, max_len)
-		self.line4, = self.ax4.plot(
+		self.line41, = self.ax4.plot(
 				np.arange(num_pipeline_entries),
 				self._pipeline_distance,
 				label="Distance",
 				lw=1.5,
 				alpha=0.7,
 				c=[1.0, 0.31, 0.0])
+		self.line42, = self.ax4.plot(
+				np.arange(num_pipeline_entries),
+				self._pipleline_new_target,
+				label="New Target",
+				lw=300.0,
+				alpha=1.0,
+				#aa=False,
+				c=[0.0, 0.0, 0.0],
+				solid_capstyle="butt")
 
 		if self.plot_pipeline:
 			plt.show()
@@ -746,7 +755,7 @@ class Visualization(object):
 		self._pipeline_similarity_l.append(agent.similarity_left)
 		self._pipeline_similarity_r.append(agent.similarity_right)
 		self._pipeline_distance.append(Vec2.length(agent.transform.position - agent.target.transform.position))
-		self._pipleline_new_target.append(agent.target_new > 0)
+		self._pipleline_new_target.append(0.5 if agent.target_new > 0 else np.nan)
 
 	def _update_symbolic_pipeline_plot(self):
 		sens_series = np.array(self._pipeline_inputs).astype(np.double)
@@ -763,28 +772,29 @@ class Visualization(object):
 		self.line24.set_data(np.arange(len(self._pipeline_similarity_r)), [b for _,b in self._pipeline_similarity_r])
 		self.line31.set_data(np.arange(len(self._pipeline_similarity_r)), [a for a,_ in self._pipeline_similarity_r])
 		self.line32.set_data(np.arange(len(self._pipeline_similarity_r)), [b for _,b in self._pipeline_similarity_r])
-		#self.line4.set_data(np.arange(len(self._pipeline_distance)), self._pipeline_distance)
[…]

### 2017-01-19 robosim/robosim.py
Add bar chart for sensory input

@@ -570,7 +570,8 @@ class World(object):
 
 
 class Visualization(object):
-	def __init__(self, size, plot_pipeline=True, num_pipeline_entries=1000):
+	def __init__(self, size, plot_pipeline=True, num_pipeline_entries=1000,
+				num_sensor_hrr_bars=20):
 		self.screen = pygame.display.set_mode(size)
 		self.plot_pipeline = plot_pipeline
 
@@ -581,6 +582,7 @@ class Visualization(object):
 		self._pipeline_similarity_r = deque(d2, num_pipeline_entries)
 		self._pipeline_distance = deque(d1, num_pipeline_entries)
 		self._pipleline_new_target = deque(d1, num_pipeline_entries)
+		self._sensor_hrr = np.full(num_sensor_hrr_bars, np.NAN, dtype='float32')
 
 		pygame.display.set_caption("robosim")
 		self.screen.fill(Color["WHITE"])
@@ -621,57 +623,49 @@ class Visualization(object):
 
 		self.ax2.set_xlim(0, num_pipeline_entries)
 		self.ax2.set_xticks([])
-		self.ax2.set_xlabel("Similarity Left Wheel")
+		self.ax2.set_xlabel("Similarity Wheels")
 		self.ax2.set_ylim(-0.4, 0.4)
 		self.line21, = self.ax2.plot(
 				np.arange(num_pipeline_entries),
 				[a for a,_ in self._pipeline_similarity_l],
-				label="Forwards",
+				label="L Forwards",
 				lw=1.5,
 				alpha=0.7,
-				c=[1.0, 0.31, 0.0])
+				c=[1.0, 0.5, 0.1])
 		self.line22, = self.ax2.plot(
 				np.arange(num_pipeline_entries),
 				[b for _,b in self._pipeline_similarity_l],
-				label="Backwards",
+				label="L Backwards",
 				lw=1.5,
 				alpha=0.7,
-				c=[0.0, 0.31, 1.0])
+				c=[1.0, 0.1, 0.5])
 		self.line23, = self.ax2.plot(
 				np.arange(num_pipeline_entries),
 				[a for a,_ in self._pipeline_similarity_r],
-				label="Forwards",
+				label="R Forwards",
 				lw=1.5,
 				alpha=0.7,
-				c=[1.0, 0.31, 0.0])
+				c=[0.1, 0.5, 1.0])
 		self.line24, = self.ax2.plot(
 				np.arange(num_pipeline_entries),
[…]

### 2017-01-19 robosim/robosim.py
Implement plotting to disk

@@ -530,6 +530,7 @@ class Object(VisObject):
 
 class World(object):
 	def __init__(self, size):
+		self.tick = 0
 		self.size = size
 		self._transform = Transform()
 		self.agents = []
@@ -562,6 +563,7 @@ class World(object):
 		agent.target = None
 
 	def step(self, delta_time):
+		self.tick += 1
 		for a in self.agents:
 			a.step(self.objects, delta_time)
 			# check world space limits
@@ -571,7 +573,7 @@ class World(object):
 
 class Visualization(object):
 	def __init__(self, size, plot_pipeline=True, num_pipeline_entries=1000,
-				num_sensor_hrr_bars=20):
+				num_sensor_hrr_bars=20, plot_to_disk=False):
 		self.screen = pygame.display.set_mode(size)
 		self.plot_pipeline = plot_pipeline
 
@@ -583,6 +585,8 @@ class Visualization(object):
 		self._pipeline_distance = deque(d1, num_pipeline_entries)
 		self._pipleline_new_target = deque(d1, num_pipeline_entries)
 		self._sensor_hrr = np.full(num_sensor_hrr_bars, np.NAN, dtype='float32')
+
+		self.plot_to_disk = plot_to_disk
 
 		pygame.display.set_caption("robosim")
 		self.screen.fill(Color["WHITE"])
@@ -759,7 +763,7 @@ class Visualization(object):
 		self._pipeline_distance.append(Vec2.length(agent.transform.position - agent.target.transform.position))
 		self._pipleline_new_target.append(0.5 if agent.target_new > 0 else np.nan)
 
-	def _update_symbolic_pipeline_plot(self):
+	def _update_symbolic_pipeline_plot(self, tick=0):
 		sens_series = np.array(self._pipeline_inputs).astype(np.double)
 		sens_mask = np.isnan(sens_series)
 		sens_series[np.isfinite(sens_series)] = np.nan
@@ -801,6 +805,8 @@ class Visualization(object):
 		#		c=[1.0, 0.31, 0.0])
 
 		self.fig.canvas.draw()
+		if self.plot_to_disk:
+			plt.savefig("plot/{}.pdf".format(tick), bbox_inches="tight")
 
 	def update(self, world):
 		self.screen.fill(Color["WHITE"])
@@ -817,7 +823,7 @@ class Visualization(object):
 		if (self.plot_pipeline and len(world.agents) >= 1):
[…]

### 2017-01-19 papers/hrr-paper/paper.tex
Add a few changes from reviewer

@@
 		Vector Symbolic Architectures (VSAs) define a set of operations
-		for association, (compressed) storage, manipulation and retrieval
+		for association, storage, manipulation and retrieval
 		of symbolic concepts, represented as fixed-length vectors in
@@
 		on memory capacity in comparison to the original capacity
-		benchmark for HRRs by Plate
-		\cite{Plate:1995:HolographicReducedRepresentations}.
+		benchmark for HRRs \cite{Plate:1995:HolographicReducedRepresentations}.
 		We also evaluate our memories in two different robotics tasks: visual scene memory and state machine scripting (holographic controllers).
@@
 This however may often prove to not satisfy the task needs any more.
+In this paper, we present a probabilistic method for removing the necessity of
+using a clean-up procedure after decoding scalar values.
 
@@
 
-The resulting vector of the superposition operation $\pmb m$ can then be probed by using the inverse of circular convolution, which is circular correlation.
-Plainly put probing can be viewed as binding with the "inverse" of a vector in Fourier space:
+The resulting vector of the superposition operation $\pmb m$ can then be probed
+by using the inverse of circular convolution, which is circular correlation.
+Probing can be viewed as binding with the "inverse" of a vector in Fourier space:
 

### 2017-01-19 papers/hrr-paper/paper.tex
Switch to conference LaTeX template

@@
 
-\documentclass[conference]{IEEEtran}
+\documentclass[journal]{journal}
 % Some Computer Society conferences also require the compsoc mode option,
@@
 	% affiliations
-	\author{\IEEEauthorblockN{Igor Peric, Alexandru Lesi, Daniel Spies, Stefan Ulbrich, Arne R{\"o}nnau, Marius Z{\"o}llner, R{\"u}diger Dillman}
-		\IEEEauthorblockA{FZI Forschungszentrum Informatik\\
-			Karlsruhe, Germany\\
-			Email: $\{$peric, lesi, spies, ulbrich, roennau, zoellner, dillmann$\}$@fzi.de}
+	\author{Igor~Peric, Alexandru~Lesi, Daniel~Spies, Stefan~Ulbrich, Arne~R{\"o}nnau, Marius~Z{\"o}llner, R{\"u}diger~Dillman\\
+		FZI Forschungszentrum Informatik, Karlsruhe, Germany\\
+		Email: $\{$peric, lesi, spies, ulbrich, roennau, zoellner, dillmann$\}$@fzi.de
 	}

### 2017-01-19 papers/hrr-paper/paper.tex
Add keywords and change text

@@
 		probability density function.
-		As we discover, this requires randomly chosen permutations for encoding and
+		We show this requires randomly chosen permutations for encoding and
 		their corresponding inverse for decoding. These are necessary
@@
 
-	% no keywords
+% Note that keywords are not normally used for peerreview papers.
+\begin{IEEEkeywords}
+	Vector Symbolic Architectures, associative memories, symbol encoding, symbolic scripting
+\end{IEEEkeywords}
 

### 2017-01-19 papers/hrr-paper/paper.tex
Fix normalization formula
Fix sentence

@@
 One way of handling symbolic scalar encoding is to discretize the whole input range into bins and assigning a random vector to each discrete value.
-This however may often prove to not satisfy the task needs any more.
-In this paper, we present a probabilistic method for removing the necessity of
-using a clean-up procedure after decoding scalar values.
+This, however may often prove to not satisfy the task needs any more.
+In this paper, we present an intrinsic, probabilistic encoding and decoding
+method, which removes the necessity of using a symbol table.
 
@@
 
-	\begin{equation}
-	x_i = x_i - \frac{\sum_{i=0}^n ||x_i||}{|x|}
+	\begin{equation}\label{eq:norm1}
+		{x_i}' = x_i - \frac{\sum_j x_j}{|{\pmb x}|},
 	\end{equation}
-
-	\begin{equation}
-	\pmb x = \frac{\pmb x }{ \| \pmb x \|}
+and
+	\begin{equation}\label{eq:norm2}
+		{\pmb x}{'}{'} = \frac{{\pmb x}'}{ \| {\pmb x}'\|},
 	\end{equation}
+which normalize ${\pmb x}$ to a mean value of $0$ and a length of $1$.
 

### 2017-01-19 robosim/robosim.py
Split plot into multiple figures

@@ -594,16 +594,24 @@ class Visualization(object):
 
 		plt.ion()
 
-		self.fig = plt.figure(figsize=(6,10))
-		self.ax1 = self.fig.add_subplot(4, 1, 1)
-		self.ax2 = self.fig.add_subplot(4, 1, 2)
-		self.ax3 = self.fig.add_subplot(4, 1, 3)
-		self.ax4 = self.fig.add_subplot(4, 1, 4)
+		self.fig1 = plt.figure(figsize=(6,2.5))
+		self.fig2 = plt.figure(figsize=(6,2.5))
+		self.fig3 = plt.figure(figsize=(6,2.5))
+		self.fig4 = plt.figure(figsize=(6,2.5))
+		self.ax1 = self.fig1.add_subplot(1, 1, 1)
+		self.ax2 = self.fig2.add_subplot(1, 1, 1)
+		self.ax3 = self.fig3.add_subplot(1, 1, 1)
+		self.ax4 = self.fig4.add_subplot(1, 1, 1)
 
-		#self.ax = self.fig.add_axes([0, 0, 1, 1], frameon=False)
+		# compute ticks
+		interval = int(num_pipeline_entries / 5)
+		ticks = [interval * x for x in np.arange(6)]
+		labels = [-1 * x for x in ticks[::-1]]
+
 		self.ax1.set_xlim(0, num_pipeline_entries)
-		self.ax1.set_xticks([])
-		self.ax1.set_xlabel("Sensory Input")
+		self.ax1.set_xticks(ticks)
+		self.ax1.set_xticklabels(labels)
+		#self.ax1.set_xlabel("Sensory Input")
 		self.ax1.set_ylim(0, 1)
 		#self.ax1.set_ylim(self.ax1.get_ylim()[::-1])
 		#self.ax1.set_yticks([])
@@ -626,9 +634,10 @@ class Visualization(object):
 				solid_capstyle="butt")
 
 		self.ax2.set_xlim(0, num_pipeline_entries)
-		self.ax2.set_xticks([])
-		self.ax2.set_xlabel("Similarity Wheels")
-		self.ax2.set_ylim(-0.4, 0.4)
+		self.ax2.set_xticks(ticks)
+		self.ax2.set_xticklabels(labels)
+		#self.ax2.set_xlabel("Similarity Wheels")
+		self.ax2.set_ylim(-0.2, 0.3)
 		self.line21, = self.ax2.plot(
 				np.arange(num_pipeline_entries),
[…]

### 2017-01-19 robosim/robosim.py
Finish up figures

@@ -384,7 +384,7 @@ class Controller(object):
 
 
 class Agent(VisObject):
-	TARGET_NEW_TIME = 4
+	TARGET_NEW_TIME = 2
 
 	def __init__(self, color, velocity=1.0):
 		super(Agent, self).__init__(Shape.HOUSE, color)
@@ -594,10 +594,10 @@ class Visualization(object):
 
 		plt.ion()
 
-		self.fig1 = plt.figure(figsize=(6,2.5))
-		self.fig2 = plt.figure(figsize=(6,2.5))
-		self.fig3 = plt.figure(figsize=(6,2.5))
-		self.fig4 = plt.figure(figsize=(6,2.5))
+		self.fig1 = plt.figure(figsize=(6,2.8))
+		self.fig2 = plt.figure(figsize=(6,2.8))
+		self.fig3 = plt.figure(figsize=(6,2.8))
+		self.fig4 = plt.figure(figsize=(6,2.8))
 		self.ax1 = self.fig1.add_subplot(1, 1, 1)
 		self.ax2 = self.fig2.add_subplot(1, 1, 1)
 		self.ax3 = self.fig3.add_subplot(1, 1, 1)
@@ -606,13 +606,14 @@ class Visualization(object):
 		# compute ticks
 		interval = int(num_pipeline_entries / 5)
 		ticks = [interval * x for x in np.arange(6)]
-		labels = [-1 * x for x in ticks[::-1]]
+		ticklabels = [-1 * x for x in ticks[::-1]]
 
 		self.ax1.set_xlim(0, num_pipeline_entries)
 		self.ax1.set_xticks(ticks)
-		self.ax1.set_xticklabels(labels)
-		#self.ax1.set_xlabel("Sensory Input")
+		self.ax1.set_xticklabels(ticklabels)
+		self.ax1.set_xlabel("Time")
 		self.ax1.set_ylim(0, 1)
+		self.ax1.set_ylabel("Visual Field")
 		#self.ax1.set_ylim(self.ax1.get_ylim()[::-1])
 		#self.ax1.set_yticks([])
 		sens_series = np.array(self._pipeline_inputs).astype(np.double)
@@ -632,47 +633,53 @@ class Visualization(object):
 				alpha=0.4,
 				c=[1.0, 0.0, 0.0],
 				solid_capstyle="butt")
+		self.fig1.tight_layout()
 
 		self.ax2.set_xlim(0, num_pipeline_entries)
[…]

### 2017-01-20 papers/hrr-paper/paper.tex
Add experiment figure and text

@@
 
+The symbolic scripting experiment is set up using a single-sensor Braitenberg
+vehicle (see figures \ref{fig:experiment:agent1} and
+\ref{fig:experiment:agent2}).
+The sensor returns a list of objects in its field of view with their
+corresponding view space positions in $[0,1]$ (far left to far right).
+% note: it would be better if we probe with all returned objects and check the
+% result, but IIRC this did not work well. maybe figure it out?
+All returned objects are then compared to the agent's target object.
+If the target is found, the holographic controller is probed with its view space
+position which, due to the similarity of scalar values, yields results even for
+values that lie between the originally stored values and can consequently be
+probed with the symbols $left\_wheel$ and $right\_wheel$ to extract the symbolic
+actions $forwards$ or $backwards$.
+If the target is not found or no action could be determined, the agent defaults
+to probing the controller with the symbolic constant $no\_object$ which results
+a clockwise rotation when probing for wheel actions (see figure
+\ref{fig:experiment:similar2}).
+
+In the left column of figure \ref{fig:experiment}, the agent approaches the blue
+target (figure \ref{fig:experiment:agent1}). In the beginning (tick $-50$), the
+agent rotates right (default action) because the target is not visible.
+At tick $-30$, the object enters the agent's visual field and is consequently
+centered until tick $-19$.
+Then, with the sensory value of ${\sim}0.5$, the actions for both wheels switch
+to $forwards$ (figure \ref{fig:experiment:similar1}) and the agent approaches
+the target, constantly decreasing its distance
+(figure \ref{fig:experiment:distance1}).
+
+In the right column of figure \ref{fig:experiment}, the target is not currently
+in the visual field of the agent.
+This is due to reaching its old target at approximately tick $-13$ which leads
+to the removal of all current objects and random placement of new objects,
+including one target.
+As the new object is placed outside of the agent's field of view, the default
+action of probing $no\_object$ is performed constantly.
+As described, this then results in the encoded default actions $backwards$ for
+probing with $left\_wheel$ and $forwards$ for probing with $right\_wheel$---a
+clockwise rotation (see figure \ref{fig:experiment:similar2}).
+
+This experiment shows the effectiveness of our approach in a practical
+application by encoding symbolic sensing, actuators and actions in a symbolic
+controller.
+
+\begin{figure}%[th!]
+\center
+\begin{subfigure}{.47\columnwidth}
+	\center
+	{%
+	\setlength{\fboxsep}{0pt}%
+	%\setlength{\fboxrule}{1pt}%
+	\fbox{\includegraphics[width=.98\columnwidth]{img/exp_robot_139.png}}%
+	}%
+	\caption{Scene of Agent 1 with three randomly placed items, the blue
+	one being the target object.
+	The green fan represents the visual field.}
+	\label{fig:experiment:agent1}
+\end{subfigure}
+\begin{subfigure}{.47\columnwidth}
+	\center
+	{%
+	\setlength{\fboxsep}{0pt}%
+	%\setlength{\fboxrule}{1pt}%
+	\fbox{\includegraphics[width=.98\columnwidth]{img/robot_235.png}}%
+	}%
+	\caption{Scene of Agent 2 with three randomly placed items.
+	The agent does not have the target object in his field of view (green
+	fan).}
+	\label{fig:experiment:agent2}
+\end{subfigure}
+\begin{subfigure}{.49\columnwidth}
+	\center
+	\includegraphics[width=.98\columnwidth]{img/3_139.pdf}
+	\caption{Symbolic sensing with target in visual field results in scalar
+	value representing target direction (${\sim}0.55$, almost straight
+	forward).}
+	\label{fig:experiment:sensor1}
+\end{subfigure}
+\begin{subfigure}{.49\columnwidth}
+	\center
+	\includegraphics[width=.98\columnwidth]{img/3_235.pdf}
+	\caption{Symbolic sensing without target in visual field showing the
+	representation for the symbolic constant $no\_object$.}
+	\label{fig:experiment:sensor2}
+\end{subfigure}
+\begin{subfigure}{.49\columnwidth}
+	\center
+	\includegraphics[width=.98\columnwidth]{img/1_139.pdf}
+	\caption{Target position over time in the visual field of Agent 1.
+	At tick $-30$, it appears on the far right edge and then gradually
+	shifts towards the center.}
+	\label{fig:experiment:pos1}
+\end{subfigure}
+\begin{subfigure}{.49\columnwidth}
+	\center
+	\includegraphics[width=.98\columnwidth]{img/1_235.pdf}
+	\caption{Agent 2 lost track of the target object (red background).
+	In this case, the old target was reached and the new target is not in
+	the field of view yet.}
+	\label{fig:experiment:pos2}
+\end{subfigure}
+\begin{subfigure}{.49\columnwidth}
+	\center
+	\includegraphics[width=.98\columnwidth]{img/4_139.pdf}
+	\caption{Distance between Agent 1 and its target over time.
+	Here, the blue object in \subref{fig:experiment:agent1} is being
+	approached.}
+	\label{fig:experiment:distance1}
+\end{subfigure}
+\begin{subfigure}{.49\columnwidth}
+	\center
+	\includegraphics[width=.98\columnwidth]{img/4_235.pdf}
+	\caption{Distance between Agent 2 and its target over time.
+	At tick $-12$ a new target was added (black bar).}
+	\label{fig:experiment:distance2}
+\end{subfigure}
+\begin{subfigure}{.49\columnwidth}
+	\center
+	\includegraphics[width=.98\columnwidth]{img/2_139.pdf}
+	\caption{Similarities of $left\_wheel$ and $right\_wheel$ to
+	the $forwards$ and $backwards$ actions respectively.
+	Here, Agent 1 approaches its target because $forwards$ has the
+	highest similarity for both wheels.}
+	\label{fig:experiment:similar1}
+\end{subfigure}
+\begin{subfigure}{.49\columnwidth}
+	\center
+	\includegraphics[width=.98\columnwidth]{img/2_235.pdf}
+	\caption{Similarities as described in \subref{fig:experiment:similar1}
+	for Agent 2. As no target is in the visual field, the default action for
+	the symbol $no\_object$ is performed (rotate right).}
+	\label{fig:experiment:similar2}
+\end{subfigure}
+\caption{Excerpts from our symbolic scripting experiment, controlling a
+Braitenberg vehicle with one linear sensor.
+The left column (\protect\subref{fig:experiment:agent1},
+\protect\subref{fig:experiment:sensor1}, \protect\subref{fig:experiment:pos1},
+\protect\subref{fig:experiment:distance1} and
+\protect\subref{fig:experiment:similar1}) illustrates an agent approaching a
+target in its visual field.
+The right column (\protect\subref{fig:experiment:agent2},
+\protect\subref{fig:experiment:sensor2}, \protect\subref{fig:experiment:pos2},
+\protect\subref{fig:experiment:distance2},
+\protect\subref{fig:experiment:similar2}) shows an agent without a target in its
+visual field, rotating clockwise (\protect\subref{fig:experiment:similar2}) to
+find it.
+}
+\label{fig:experiment}
+\end{figure}
+
 	\section{Conclusions}

### 2017-01-20 papers/hrr-paper/paper.tex
Corrected Symbolic Scrypting Experiment, rearranged images as well.

@@
 
-We have used our system to demonstrate a mechanism for encoding neural programs and processes through a series of associated action, perception and actuator symbols.
+We have used our system to create a mechanism for encoding neural programs and processes through a series of associated action, perception and actuator symbols.
 We call this mechanism for defining controllers using holographic memories "symbolic scripting".
@@
 
-The basic idea is centered around symbolic representations of all three parts involved:
+The basic idea is centred around symbolic representations of all three parts involved:
 \begin{enumerate}
@@
 
-An example of this kind of symbolic script is given in figure \ref{fig:symbolic-scripting}. Here the memory encodes an object following behavior for left wheel.
+An example of this kind of symbolic script is given in figure \ref{fig:symbolic-scripting}. Here the memory encodes an object following behaviour for its left wheel.
 
@@
 			\end{subfigure}	
-		\caption{Sensory input encoding of target object position in the visual field at two successive points in time.
+		\caption{Sensory input encoding of a target objects position in the visual field at two successive points in time.
 Left graph shows original encodings for two adjacent values and right graph shows permuted encodings.
@@
 If the target is found, the holographic controller is probed with its view space
-position which, due to the similarity of scalar values, yields results even for
+position which, due to the similarity of scalars, yields results even for
 values that lie between the originally stored values and can consequently be
@@
 If the target is not found or no action could be determined, the agent defaults
-to probing the controller with the symbolic constant $no\_object$ which results
+to probing the controller with the symbolic constant $no\_object$ which results in
 a clockwise rotation when probing for wheel actions (see figure
@@
 agent rotates right (default action) because the target is not visible.
-At tick $-30$, the object enters the agent's visual field and is consequently
-centered until tick $-19$.
+At tick $-30$, the object enters the agent's visual field and continuously nears the fields center, which is reached at tick $-19$.
 Then, with the sensory value of ${\sim}0.5$, the actions for both wheels switch
@@
 
-In the right column of figure \ref{fig:experiment}, the target is not currently
+In the right column of figure \ref{fig:experiment}, the target is not yet
 in the visual field of the agent.
-This is due to reaching its old target at approximately tick $-13$ which leads
-to the removal of all current objects and random placement of new objects,
-including one target.
-As the new object is placed outside of the agent's field of view, the default
-action of probing $no\_object$ is performed constantly.
-As described, this then results in the encoded default actions $backwards$ for
-probing with $left\_wheel$ and $forwards$ for probing with $right\_wheel$---a
-clockwise rotation (see figure \ref{fig:experiment:similar2}).
+This is the result of the agent previously reaching an old target (at approximately tick $-13$) which lead
+to the removal of all current objects and random placement of new ones,
+including a new target.
+As the new target is placed outside of the agent's field of view, the default
+action of probing $no\_object$ is performed. The
+clockwise rotation can also be seen in figure \ref{fig:experiment:similar2}).
+Regardless of how many times the agent reaches its target it will continue to find and pursue new ones solely with the help of its symbolic controller.
 
 This experiment shows the effectiveness of our approach in a practical
-application by encoding symbolic sensing, actuators and actions in a symbolic
+application by encoding symbolic sensing, actuators and actions in a
 controller.
@@
 	}%
-	\caption{Scene of Agent 1 with three randomly placed items, the blue
+	\caption{Scene of Agent 1 (red) with three randomly placed items, the blue
 	one being the target object.
@@
 	\caption{Scene of Agent 2 with three randomly placed items.
-	The agent does not have the target object in his field of view (green
-	fan).}
+	The agent does not have the target object in his field of view yet.}
 	\label{fig:experiment:agent2}
@@
 	\includegraphics[width=.98\columnwidth]{img/3_139.pdf}
-	\caption{Symbolic sensing with target in visual field results in scalar
-	value representing target direction (${\sim}0.55$, almost straight
+	\caption{Symbolic sensing with the target in the visual field, which results in a scalar
+	value representing the target direction (${\sim}0.55$, almost straight
 	forward).}
@@
 	\includegraphics[width=.98\columnwidth]{img/3_235.pdf}
-	\caption{Symbolic sensing without target in visual field showing the
-	representation for the symbolic constant $no\_object$.}
+	\caption{Symbolic sensing without the target in the visual field showing the
+	representation for the symbolic constant $no\_object$.\\}
 	\label{fig:experiment:sensor2}
@@
 	\includegraphics[width=.98\columnwidth]{img/1_139.pdf}
-	\caption{Target position over time in the visual field of Agent 1.
-	At tick $-30$, it appears on the far right edge and then gradually
+	\caption{The targets position over time in the visual field of Agent 1.
+	At tick $-30$, the target enters the far right edge of the field of view and then gradually
 	shifts towards the center.}
@@
 	\caption{Agent 2 lost track of the target object (red background).
-	In this case, the old target was reached and the new target is not in
-	the field of view yet.}
+	This is due to it having been reached, which prompts a new target creation, which is not in
+	the field of view.}
 	\label{fig:experiment:pos2}
@@
 	\caption{Distance between Agent 1 and its target over time.
-	Here, the blue object in \subref{fig:experiment:agent1} is being
+	Here, the blue object in sub-figure \subref{fig:experiment:agent1} is being
 	approached.}
@@
 	\caption{Distance between Agent 2 and its target over time.
-	At tick $-12$ a new target was added (black bar).}
+	At tick $-12$ a new target was created (black bar).}
 	\label{fig:experiment:distance2}
@@
 	\includegraphics[width=.98\columnwidth]{img/2_235.pdf}
-	\caption{Similarities as described in \subref{fig:experiment:similar1}
+	\caption{Similarities as described in sub-figure \subref{fig:experiment:similar1}
 	for Agent 2. As no target is in the visual field, the default action for
-	the symbol $no\_object$ is performed (rotate right).}
+	the symbol $no\_object$ is performed (rotate right).\\}
 	\label{fig:experiment:similar2}
@@
 Braitenberg vehicle with one linear sensor.
-The left column (\protect\subref{fig:experiment:agent1},
+The left column (sub-figures \protect\subref{fig:experiment:agent1},
 \protect\subref{fig:experiment:sensor1}, \protect\subref{fig:experiment:pos1},
@@
 \protect\subref{fig:experiment:distance2},
-\protect\subref{fig:experiment:similar2}) shows an agent without a target in its
+\protect\subref{fig:experiment:similar2}) shows an agent with currently no target in its
 visual field, rotating clockwise (\protect\subref{fig:experiment:similar2}) to

### 2017-02-20 papers/hrr-paper-neurotechnix/Example.tex
Created Neurotechnix version of HRR paper

--- 2017-01-20 papers/hrr-paper/paper.tex
@@
-%% bare_conf.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
-%% conference paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-\documentclass[journal]{journal}
-% Some Computer Society conferences also require the compsoc mode option,
-% but others use the standard conference format.
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[conference]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
+\documentclass[a4paper,twoside]{article}
 \usepackage{algorithm}
 \usepackage{algpseudocode} 
+\usepackage[babel,german=quotes,english=american]{csquotes} 
+\usepackage[pdftex]{graphicx}
+\usepackage{url}
+\usepackage{pgfplots}
+
+\usepackage{epsfig}
 \usepackage{subcaption}
+\usepackage{calc}
+\usepackage{amssymb}
+\usepackage{amstext}
+\usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{multicol}
+\usepackage{pslatex}
+\usepackage{apalike}
+\usepackage{SCITEPRESS}     % Please add other packages that you may need BEFORE the SCITEPRESS.sty package.
 
-% *** CITATION PACKAGES ***
-%
-%% Use biber instead of BibTeX
-%\usepackage[citestyle=numeric,style=numeric,backend=biber]{biblatex}
-\usepackage[
-	hyperref=true,
-	%citestyle=alphabetic,
-	citestyle=numeric,
-	%style=alphabetic,
-	style=numeric,
-	sorting=none,
-	maxcitenames=3,
-	maxbibnames=100,
-	%backref=true,
-	backend=biber
-]{biblatex}
-\usepackage[babel,german=quotes,english=american]{csquotes}
+%\subfigtopskip=0pt
+%\subfigcapskip=0pt
+%\subfigbottomskip=0pt
 
-% disable unimportant stuff in bibliography
-\DeclareSourcemap{
-  \maps[datatype=bibtex, overwrite]{
-    \map{
-      \step[fieldset=language, null]
-      \step[fieldset=notes, null]
-      \step[fieldset=issn, null]
-      \step[fieldset=doi, null]
-      \step[fieldset=url, null]
-      \step[fieldset=eprint, null]
-      \step[fieldset=abstract, null]
-      \step[fieldset=pages, null]
-      \step[fieldset=address, null]
-      \step[fieldset=editors, null]
-    }
-  }
+\begin{document}
+
+\title{Probabilistic Symbol Encoding for \\Convolutional Associative Memories}
+
+\author{\authorname{Igor Peric, Alexandru Lesi, Daniel Spies, Stefan Ulbrich,\\ Arne R{\"o}nnau, Marius Z{\"o}llner and R{\"u}diger Dillman}
+\affiliation{FZI Forschungszentrum Informatik, Karlsruhe, Germany}
+\email{\{peric, lesi, spies, ulbrich, roennau, zoellner, dillmann\}@fzi.de}
 }
 
-%TODO check 
-%\appto{\bibsetup}{\raggedright}
-\appto{\bibsetup}{\sloppy}
-\addbibresource{paper.bib}
+\keywords{Vector Symbolic Architectures, Associative Memories, Symbol Encoding, Symbolic Scripting}
 
-%\DefineBibliographyStrings{english}{%
-%    backrefpage  = {see p.}, % for single page number
-%    backrefpages = {see pp.} % for multiple page numbers
-%}
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-\usepackage[pdftex]{graphicx}
-% declare the path(s) where your graphic files are
-% \graphicspath{{../pdf/}{../jpeg/}}
-% and their extensions so you won't have to specify these with
-% every instance of \includegraphics
-% \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-% or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-% will default to the driver specified in the system graphics.cfg if no
-% driver is specified.
-% \usepackage[dvips]{graphicx}
-% declare the path(s) where your graphic files are
-% \graphicspath{{../eps/}}
-% and their extensions so you won't have to specify these with
-% every instance of \includegraphics
-% \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-\usepackage{amsmath}
-\usepackage{mathabx}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
-%\usepackage{asmfonts}
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-\usepackage{pgfplots}
-
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-
-\begin{document}
-	%
-	% paper title
-	% Titles are generally capitalized except for words such as a, an, and, as,
-	% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-	% not capitalized unless they are the first or last word of the title.
-	% Linebreaks \\ can be used within to get better formatting as desired.
-	% Do not put math or special symbols in the title.
-	\title{Probabilistic Symbol Encoding for \\Convolutional Associative Memories}
-
-	% author names and affiliations
-	% use a multiple column layout for up to three different
-	% affiliations
-	\author{Igor~Peric, Alexandru~Lesi, Daniel~Spies, Stefan~Ulbrich, Arne~R{\"o}nnau, Marius~Z{\"o}llner, R{\"u}diger~Dillman\\
-		FZI Forschungszentrum Informatik, Karlsruhe, Germany\\
-		Email: $\{$peric, lesi, spies, ulbrich, roennau, zoellner, dillmann$\}$@fzi.de
-	}
-
-	% conference papers do not typically use \thanks and this command
-	% is locked out in conference mode. If really needed, such as for
-	% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-	% after \documentclass
-
-	% for over three affiliations, or if they all won't fit within the width
-	% of the page, use this alternative format:
-	% 
-	%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-	%Homer Simpson\IEEEauthorrefmark{2},
-	%James Kirk\IEEEauthorrefmark{3}, 
-	%Montgomery Scott\IEEEauthorrefmark{3} and
-	%Eldon Tyrell\IEEEauthorrefmark{4}}
-	%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-	%Georgia Institute of Technology,
-	%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-	%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-	%Email: homer@thesimpsons.com}
-	%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-	%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-	%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
-	% use for special paper notices
-	%\IEEEspecialpapernotice{(Invited Paper)}
-
-	% make the title area
-	\maketitle
-
-	% As a general rule, do not put math, special symbols or citations
-	% in the abstract
-	\begin{abstract}
-		Vector Symbolic Architectures (VSAs) define a set of operations
+\abstract{		Vector Symbolic Architectures (VSAs) define a set of operations
 		for association, storage, manipulation and retrieval
@@
 		benchmark for HRRs \cite{Plate:1995:HolographicReducedRepresentations}.
-		We also evaluate our memories in two different robotics tasks: visual scene memory and state machine scripting (holographic controllers).
-	\end{abstract}
+		We also evaluate our memories in two different robotics tasks: visual scene memory and state machine scripting (holographic controllers).}
 
-% Note that keywords are not normally used for peerreview papers.
-\begin{IEEEkeywords}
-	Vector Symbolic Architectures, associative memories, symbol encoding, symbolic scripting
-\end{IEEEkeywords}
-
-	% For peer review papers, you can put extra information on the cover
-	% page as needed:
-	% \ifCLASSOPTIONpeerreview
-	% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-	% \fi
-	%
-	% For peerreview papers, this IEEEtran command inserts a page break and
-	% creates the second title. It will be ignored for other modes.
-	\IEEEpeerreviewmaketitle
-
-	\section{Introduction}
+\onecolumn \maketitle \normalsize \vfill
+WS
+	\section{INTRODUCTION}
 
@@
 
+	\begin{figure}
+		\center
+		\includegraphics[width=0.9\columnwidth]{img/probe_for_pen_w_img.png}
+		\caption{In-memory representation of visual scene short-term memory. The result shows probability distribution for a symbol "pen" being at certain position in scene.}
+	\end{figure}
+
 	Depending on the way these three operations are implemented we can distinguish several popular VSAs, such as Holographic Reduced Representations \cite{Plate:1995:HolographicReducedRepresentations}, Circular HRRs \cite{DeVine:2010:Semanticoscillations}, Binary Spatter Codes \cite{Kanerva:1994:SpatterCodeEncoding}, Holographic Graph Neurons \cite{Kleyko:2016:HolographicGraphNeuron}, Geometric Algebras \cite{Patyk-Lonska:2011:DistributedRepresentationsBased} and Random Permutations \cite{Recchia:2015:EncodingSequentialInformation}.
@@
 Preliminary theoretical assumptions have been made about the ability to use them as agent controllers \cite{Levy:2013:LearningBehaviorHierarchies}, where a symbolic program is represented with a set of combined symbolic actions associated with actuator symbols and symbolic sensing.
-
-	\begin{figure}
-		\center
-		\includegraphics[width=0.9\columnwidth]{img/probe_for_pen_w_img.png}
-		\caption{In-memory representation of visual scene short-term memory. The result shows probability distribution for a symbol "pen" being at certain position in scene.}
-	\end{figure}
 
@@
 
-	\section{Vector Symbolic Architectures}
+	\section{VECTOR SYMBOLIC ARCHITECTURES}
 
@@
 
-	\subsection{Holographic reduced representations}
+	\subsection{Holographic Reduced Representations}
 	\label{sec:hrr}
@@
 
-	\section{Topology-preserving encoding}
+	\section{TOPOLOGY-PRESERVING ENCODING}
 
-	\subsection{Encoding scalar symbols}
+	\subsection{Encoding Scalar Symbols}
 
@@
 
-	\subsection{Encoding coordinate symbols}
+	\subsection{Encoding Coordinate Symbols}
 
@@
 
-	\section{Properties of holographic memories}
+	\section{PROPERTIES OF HOLOGRAPHIC MEMORIES}
 
@@
 
-	\section{Experiments}
+	\section{EXPERIMENTS}
 	\label{sec:experiments}
-	\subsection{Visual short term memory and top-down attention model}
+	\subsection{Visual Short Term Memory and Top-Down Attention Model}
 
@@
 
-\subsection{Symbolic scripting (holographic controllers)}
+\subsection{Symbolic Scripting (Holographic Controllers)}
 
@@
 
-	\section{Conclusions}
+	\section{CONCLUSIONS}
 	We have introduced a mechanism for intrinsic symbol encoding/decoding for Holographic Reduced Representations.
@@
 
-	%% Add entry to the table of contents for the bibliography
-	\printbibliography[heading=bibintoc]
+\vfill
+\bibliographystyle{apalike}
+{\small
+\bibliography{example}}
 
-	% that's all folks
+%\section*{\uppercase{Appendix}}
+%
+%\noindent If any, the appendix should appear directly after the
+%references without numbering, and not on a new page. To do so please use the following command:
+%\textit{$\backslash$section*\{APPENDIX\}}
+
+\vfill
 \end{document}

### 2017-02-23 papers/hrr-paper-neurotechnix/Example.tex
Further corrections to hrr neurotechnix paper

@@
 		have proven to exhibit properties similar to human short-term
-		memory and are, as such, interesting for computational modeling.
+		memory and as such are interesting for computational modelling.
 		In this paper we extend the HRR approach by introducing implicit,
 		topology-preserving encoding and decoding procedures.
-		We propose moving away from traditional exact symbolic representation
-		to probabilistic one, replacing unique symbol identifiers with 
-		probability density function.
-		We show this requires randomly chosen permutations for encoding and
-		their corresponding inverse for decoding. These are necessary
-		for the uniform distribution of signals across Fourier space where
+		We propose to replace unique symbolic representations with symbols based on
+		probability density functions.
+		These symbols must be randomly permuted to ensure the uniform distribution of signals across Fourier space where
 		embedding takes place.
-		These novel encoding schemes, together with the extended operation
-		pipeline, are eliminating the need for so-called \emph{clean-up modules} after memory
-		retrieval (e.g., self-organizing maps). Effectively, encoding
-		implicitly represents the scalar symbol, so no further lookup is needed.
-		We show that our encoding scheme has a positive impact
+		These novel encoding schemes eliminate the need for so-called \emph{clean-up modules} after memory
+		retrieval (e.g., self-organizing maps). Effectively each encoding
+		implicitly represents its scalar symbol, so no further lookup is needed.
+		We further show that our encoding scheme has a positive impact
 		on memory capacity in comparison to the original capacity
@@
 \onecolumn \maketitle \normalsize \vfill
-WS
+
 	\section{INTRODUCTION}
@@
 
-	In addition, every VSA can be considered as a lossy compression technique, since binary operations on N-element vectors return N-element vectors as well.
+	VSAs can be viewed as a lossy compression technique, since binary operations on N-element vectors return N-element vectors as well.
 These operations will be described in further detail in the following section.
@@
 		\includegraphics[width=0.9\columnwidth]{img/probe_for_pen_w_img.png}
-		\caption{In-memory representation of visual scene short-term memory. The result shows probability distribution for a symbol "pen" being at certain position in scene.}
+		\caption{In-memory probability for a symbol "pen"}
 	\end{figure}
@@
 The most widely used ones are HRRs and they are briefly explained in section \ref{sec:hrr}.
-Authors in \cite{Golosio:2015:CognitiveNeuralArchitecture} have used them to solve word embedding problem for extremely large dataset by replacing computationally expensive big matrix factorization with an iterative estimation algorithm based on HRRs.
+Authors in \cite{Golosio:2015:CognitiveNeuralArchitecture} have used them to solve word embedding problems for extremely large datasets by replacing computationally expensive big matrix factorizations with an iterative estimation algorithm.
 Some of the other work is centered around pattern recognition \cite{Kleyko:2016:PatternRecognitionVector} and functional large-scale cognitive architecture models \cite{Eliasmith:2012:LargeScaleModel}.
@@
 
-	Authors in \cite{Eliasmith:2012:LargeScaleModel} have demonstrated that the functional cognitive model Spaun is capable of performing 7 different cognitive tasks when implemented as HRRs using biologically plausible models of neuron dynamics.
+	Authors in \cite{Eliasmith:2012:LargeScaleModel} have demonstrated that the functional cognitive model Spaun is capable of performing $7$ different cognitive tasks when implemented as HRRs using biologically plausible models of neuron dynamics.
 They further show that in serial working memory tasks the model of forgetting exhibits similar behaviour as human working memory due to limited capacity.
@@
 These networks succeed due to training on big data and using convolution as the main architectural constraint.
-Although the description of the biophysical mechanism underlying convolution and concept of weight sharing are still missing, it is important to reuse proven concepts, such as convolutional filtering, in as general way as possible.
+Although the description of the biophysical mechanism underlying convolution and the concept of weight sharing are still missing, it is important to reuse proven concepts, such as convolutional filtering, in a way as general as possible.
 In other words, addressing multiple fundamentally different problems with similar computational principles can be considered a step towards a unified brain processing theory.
@@
 
-	\textbf{Superposition} is the operation of extending a set of items, regardless of what is already contained in them.
-As an example, a memory of "red triangle and blue circle" can be formed in the following way:
+	\textbf{Superposition} is the operation of extending a symbol, regardless of what it already contains.
+The memory "red triangle and blue circle" is formed as:
 	\begin{equation}
@@
 
-	\textbf{Probing} is the operation of extracting a noisy version of an associated item from a joint set memory.
-I.e. in this scenario the question "What color is the triangle?" could be asked like this:
+	\textbf{Probing} is the operation of extracting a noisy version of an associated item from a set memory.
+Asking "What color is the triangle?" works as follows:
 
@@
 	Here $triangle'$ represents the inverse of $triangle$.
-The resulting vector will be a composition of something that is very similar to $red$ and something that doesn't resemble anything meaningful from the symbol table, so it can be treated as negligible noise.	A usual way of computing similarity is the cosine distance, which for two vectors \pmb x and \pmb y is calculated as follows:
+The resulting vector will be a composition of something that is very similar to $red$ and something that doesn't resemble anything meaningful from the symbol table, so it can be treated as negligible noise.
+One similarity measure is the cosine distance, which for two vectors \pmb x and \pmb y is calculated as follows:
 
@@
 
-	Obtained values of similarity clearly distinguish the matching vectors. Concrete values that highlight this will be later presented in section \ref{sec:experiments}.
+	Obtained similarity values clearly distinguish the matching vectors. Concrete values that highlight this will be later presented in section \ref{sec:experiments}.
 
@@
 	Holographic Reduced Representations are VSAs which implement the operation of binding as circular convolution.
-One option for calculating it is with the help of discrete Fast Fourier Transformations, in short FFTs.
-Taking $f(x)$ to describe an FFT, with $f^{-1}(x)$ as its inverse, circular convolution can be calculated as follows:
+One option for calculating it is with the help of discrete Fast Fourier Transformations (FFTs).
+Taking $f(x)$ to describe an FFT, with its inverse $f^{-1}(x)$, circular convolution is calculated as:
 
@@
 
-	where $\pmb a$ is the result of convolution, and $\pmb x$ and $\pmb y$ are symbolic vectors of size $n$.
-Superposition is implemented as a simple element-wise vector addition. Taking the result of the previously displayed convolution and superposing it with some vector $\pmb b$ is done as follows:
+	Here $\pmb a$ is the result of convolution, and $\pmb x$ and $\pmb y$ are symbolic vectors of size $n$.
+Superposition is implemented as a simple element-wise vector addition. Taking the previous result and superposing it with some vector $\pmb b$ is done as follows:
 
@@
 by using the inverse of circular convolution, which is circular correlation.
-Probing can be viewed as binding with the "inverse" of a vector in Fourier space:
+Probing can be viewed as binding with the "inverse":
 
@@
 
-Following the previous formulas as a series of operations the vector $\pmb y^*$ will be similar to vector $\pmb y$, but not entirely the same due to the noisy influence of vector $\pmb b$.
-The inverse in Fourier space referred to here is gained by calculating the complex conjugate of the vector's entries.
-Complex conjugates are simply the same values with negated imaginary parts.
+Following this series of operations the vector $\pmb y^*$ will be similar to vector $\pmb y$, but not entirely the same due to the noisy influence of $\pmb b$.
+The inverse in Fourier space referred to here is gained by calculating the complex conjugate of the vector's entries, which is done by negating the imaginary parts.
 
@@
 	\begin{equation}\label{eq:norm1}
-		{x_i}' = x_i - \frac{\sum_j x_j}{|{\pmb x}|},
+		{x_i}' = x_i - \frac{\sum_j x_j}{|{\pmb x}|}\qquad {\pmb x}{'}{'} = \frac{{\pmb x}'}{ \| {\pmb x}'\|}
 	\end{equation}
-and
-	\begin{equation}\label{eq:norm2}
-		{\pmb x}{'}{'} = \frac{{\pmb x}'}{ \| {\pmb x}'\|},
-	\end{equation}
-which normalize ${\pmb x}$ to a mean value of $0$ and a length of $1$.
 
@@
 	To facilitate these two qualities scalar encoding can be achieved using probabilistic instead of exact symbolic representation. 
-The encoded vector can simply be a Gaussian shaped probability distribution sampled over a fixed input range, with mean equal to the encoded value and arbitrarily chosen standard deviation.
+The encoded vector can simply be a Gaussian shaped probability distribution sampled over a fixed input range, with a mean equal to the encoded value and arbitrarily chosen standard deviation.
 Figure \ref{no-perm-a} shows how such an encoded vector looks like, and what the result of binding it to a generic random vector is.
 With this result it becomes obvious that unfortunately lots of information is lost.
-If this result is probed with the same random vector used in binding something similar to the initial Gaussian distribution is expected.
+If this result is probed with the symbol for "ball" something similar to the initial Gaussian distribution for the value $8$ on a scale to $10$ is expected.
 And yet figure \ref{no-perm-b} presents no such outcome.
@@
 		\end{subfigure}
-		\caption{Plot of vector values.
-Figure \ref{no-perm-a} shows the binding of the value 8 from representational range [0,10] with the symbolic representation of "ball" (which is randomly chosen), giving a representation of association.
-In figure \ref{no-perm-b} this resulting representation is probed with "ball" and the expected result is a Gaussian distribution for 8, mixed with some noise.
-As it can be seen, result is far from expected and numeric value cannot be inferred.}
+		\caption{Binding 8 with "ball", then probing for "ball"}
 		\label{no-perm}
@@
 	\includegraphics[width=\columnwidth]{img/scalar-random-fft.png}
-	\caption{Fourier analysis of 1D symbols: a Gaussian distribution (top row) and a randomly sampled vector of the same size (bottom row).
-It is obvious that the latter's information in Fourier space is uniformly spread across the whole spectrum, while the former's is concentrated around 2 boundary points.}
+	\caption{Fourier analysis of scalars and random symbols}
 	\label{fft}
@@
 As such the resulting vector will present lots of jumps in value, which have a significant impact on the Fourier space, as can be seen in figure \ref{perm-fft}.
+Decoding scalar values will require a reverse permutations of the result of probing.
 
@@
 		\includegraphics[width=\columnwidth]{img/scalar-perm-step-fft.png}
-		\caption{Applying random permutation to a sampled Gaussian distribution results in more discrete changes in signal, which correspond to high-frequency components in Fourier space.
-This makes frequency spectrum more uniformly spread, which is a desirable property for HRRs.
-Although this scrambling of initial signal makes it seem random, the fact that the same permutation is used in all encodings keeps two semantically close values having very similar representations, thus preserving their semantic proximity.
-}
+		\caption{Fourier space of a permuted scalar encoding}
 		\label{perm-fft}
@@
 		\end{subfigure}
-		\caption{Figure \ref{perm-a} shows the binding of the permuted Gaussian distribution for the value 8 from range [1, 10] with the symbolic representation of "ball", which is random.
-In figure \ref{perm-b} "ball" is being probed, and the result after inverse permutation is a Gaussian distribution for the value 8, mixed with some noise.}
+		\caption{Operations of figure \ref{no-perm} with permutation}
 		\label{perm}
@@
 
-	Algorithms 1 and 2 show the operations pipeline before and after the suggested modification are introduced in pseudo code.
-
-	\begin{algorithm}
-		\caption{Original pipeline}
-		\begin{algorithmic}[1]
-			\ForAll{$symbol$}
-			\State $t_{symbol} \gets chooseRandomVector()$
-			\EndFor
-			\State $m \gets initEmptyMemory()$
-			\ForAll{$(symbol_1, symbol_2)$}
-			\State $enc_1 \gets FFT(t_{symbol_1})$
-			\State $enc_2 \gets FFT(t_{symbol_2})$
-			\State $m \gets m + IFFT(enc_1 * enc_2$)
-			\EndFor		
-			\Function{ProbeMemory}{memory, op}
-			\State $result\gets IFFT(FFT(memory)* FFT(op)^{-1})$
-
-			\ForAll{$symbol$}
-			\State $s \gets cosineSimilarity(t_{symbol}, result)$
-			\If {$s \geq cleanResultSimilarity$}
-			\State $cleanResultSimilarity \gets s$
-			\State $cleanResult \gets t_{symbol}$
-			\EndIf
-			\EndFor \\
-			\Return $cleanResult$
-			\EndFunction
-		\end{algorithmic}
-	\end{algorithm}
-
-	Lines 1-3 assign a random vector representation to each symbol known to the system prior to any other operations.
-This lookup table is stored in an array $t$.
-Lines 4-9 initialize the memory $m$ with an arbitrary amount of pairs of associated scalars.
-Function $ProbeMemory(memory, op)$ returns a symbol associated with provided $op$.
-Line 11 performs circular correlation and stores the noisy result of unbinding in $s$.
-Lines 12-18 loop through the whole lookup table and find the maximum similarity vector to $s$.
-
-		\begin{algorithm}
-			\caption{Modified pipeline}
-			\begin{algorithmic}[1]
-				\State $P \gets chooseRandomPermutation(n)$
-				\State $m \gets initEmptyMemory()$
-				\ForAll{$(symbol_1, symbol_2)$}
-				\State $enc_1 \gets FFT(permute(enc(symbol_1, n), P))$
-				\State $enc_2 \gets FFT(permute(enc(symbol_2, n), P))$
-				\State $m \gets m + IFFT(enc_1 * enc_2)$
-				\EndFor	
-				\Function{ProbeMemory}{memory, op}
-				\State $r \gets IFFT(FFT(memory) * FFT(op)^{-1})$
-				\State $r \gets permute(r, P^{-1})$
-				\State $cleanResult \gets argmax(r)$
-
-				\Return $cleanResult$
-				\EndFunction
-			\end{algorithmic}
-		\end{algorithm}
-
-		In contrast, Algorithm 2 shows a pipeline with our proposed changes.
-The first line chooses a fixed random permutation of $n$ elements used throughout the whole process.
-There is no initial loop to assign symbolic representations to all symbols.
-They are, instead, constructed according to need using function $enc(value, n)$.
-This function returns a discrete sampled Gaussian distribution vector of $n$ elements, centred around a chosen $value$.
-The vector is then permuted using a permutation $P$ in lines 4 and 5, so its frequency representation contains uniform spread over the whole spectrum, as explained earlier in this chapter.
-The probing operation consists of applying an inverse permutation $P^{-1}$ after IFFT (line 10).
-Since this returns a noisy version of the initial Gaussian distribution (shown in figure \ref{perm-b}), the only thing that needs to be done is to identify the peak of the distribution.
-The complexity of this operation is linear w.r.t.
-length of the vector $n$, while in the case of Algorithm 1 it is linear w.r.t.
-to number of symbols stored in the lookup table.
+		As such using the scalar encoder simplifies the operations pipeline of working with symbols.
+Encoding the same scalar over and over will always yield the same result, removing the need to store scalar symbols in a lookup table.
+Also, when probing for a scalar, the symbol doesn't need to be matched against all other known symbols to determine the highest similarity, which can be computationally expensive.
+Instead the result of probing is smoothed out and verified for the presence of a Gaussian distribution, which then determines the scalar it represents.
 
@@
 				\includegraphics[width=1\columnwidth]{img/capacity.png}
-				\caption{Binding pairs of random vectors. Accuracy decreases with more bindings.}
+				\caption{Symbols accuracy}
 				\label{fig:capacity}
@@
 				\includegraphics[width=1\columnwidth]{img/capacity_scalar_30.png}
-				\caption{Binding pairs of one scalar and a random symbol, then probing for the scalar.}
+				\caption{Scalars accuracy}
 				\label{fig:capacity_scalar}
@@
 				\includegraphics[width=1\columnwidth]{img/capacity_coordinate.png}
-				\caption{Binding pairs of one 2D coordinate and a random symbol, then probing for the scalar.}
+				\caption{Coordinates accuracy}
 				\label{fig:capacity_coordinate}
 			\end{subfigure}	
-			\caption{Memory capacity analysis for storing a variable number of pair associations in a single memory vector.
-Different lines show various vector lengths, the horizontal axis shows the number of pairs and vertical axis accuracy of successful recall.
-Both false positives and false negatives are regarded.}
+			\caption{Single vector memory capacity analysis}
 		\end{figure}
@@
 
-	As we can see, a 512 element vector starts decreasing accuracy of recall after 10 pairs stored in a single memory block.
-A 4096 and 8192 element vectors can almost perfectly recall 20 associated pairs, which matches the results of Plate using a lookup table and a clean-up process.
+	As we can see, a $512$ element vector starts decreasing accuracy of recall after $10$ pairs stored in a single memory block.
+A $4096$ and $8192$ element vectors can almost perfectly recall $20$ associated pairs, which matches the results of Plate using a lookup table and a clean-up process.
 
-	The experiment was repeated for binding a random symbol to the encodings of both scalars and to 2D coordinates, to compare performance.
+	The experiment was repeated for superposing bounded pairs of a random symbol and a scalar, as well as pairs of a random symbol and a 2D coordinate.
 Figure \ref{fig:capacity_scalar} shows the result for scalars.
@@
 This will determine how much the peaks position may shift in some direction.
-In our experiments a Hanning window smoothing technique was used and a 2\% deviance from the exact initial scalar was allowed.
+In our experiments a Hanning window smoothing technique was used and a $2\%$ deviance from the exact initial scalar was allowed.
 With these settings probing performed significantly better than solely among random symbols.
-Vectors of size 8192 even managed to maintain 100\% accuracy when storing 30 bindings.
+Vectors of size 8192 even managed to maintain $100\%$ accuracy when storing $30$ bindings.
 Intuitively this can be explained as follows: Gaussian distributions are far more noise tolerant than random vectors.
@@
 Due to this higher steps in between vector lengths have been used, and most lengths still perform rather poorly.
-However, increasing the length considerably, like in the case with 65536 elements, near-perfect accuracy can still be upheld up to 20 bindings.
+However, increasing the length considerably, like in the case with $65536$ elements, near-perfect accuracy can still be upheld up to $20$ bindings.
+In all $3$ experiments both fakse positives and false negatives are regarded.
 
@@
 An arbitrary algorithm is used to perform object detection and recognition, resulting in a number of 2D coordinates associated with respective object names (figure \ref{fig:object-detection}).
-Object names are strings and are encoded as random vectors of length $n$, which are sampled from a Gaussian distribution (figure \ref{fig:encoding-object}).
-The locations of objects in the image plane are 2D coordinates $(x,y)$ and they are perceptually grounded symbols (figure \ref{fig:encoding-coord}).
+Object names are strings and are encoded as random vectors of length $n$ (figure \ref{fig:encoding-object}).
+The locations of objects in the image plane are 2D coordinates $(x,y)$ and they are perceptually grounded symbols (figure \ref{fig:encoding-coord}, non-permuted).
 
@@
 			\includegraphics[width=\linewidth]{img/coord_example_1.png}
-			\caption{Encoding of location (x,y) for "watch"}
+			\caption{Location of "watch"}
 			\label{fig:encoding-coord}
@@
 			\includegraphics[width=\linewidth]{img/coord_example_2.png}
-			\caption{Encoding of the "watch" object ID as a randomly sampled vector}
+			\caption{Symbol of "watch"}
 			\label{fig:encoding-object}
@@
 			\includegraphics[width=0.8\linewidth]{img/coord_example_3.png}
-			\caption{Representation of the complete visual scene, containing information about all 7 objects and their locations scrambled together}
+			\caption{Entire  visual scene memory (7 pairs)}
 			\label{fig:encoding-scene}
@@
 			\includegraphics[width=\linewidth]{img/probe_for_mug.png}
-			\caption{Probing for "mug" returns location probability for a mug}
+			\caption{Probing for "mug"}
 			\label{fig:probing-single}
@@
 			\includegraphics[width=\linewidth]{img/probe_for_pen.png}
-			\caption{Probing for "pen" return mixture of Gaussian distributions}
+			\caption{Probing for "pen"}
 			\label{fig:probing-double}
@@
 
-		\caption{Representation of visual scene in short term symbolic memory. }
+		\caption{Representation of visual scene in memory. }
 
@@
 
-    			\caption{Similarity test for each symbol from the lookup table after probing the entire scene memory for a specific location.}
+    			\caption{Similarity test after probing for specific locations}
     \end{figure}
@@
 	\end{subfigure}
-	\caption{Symbolic scripting illustration for object following behavior of a two-wheeled robot}
+	\caption{Symbolic scripting illustration: object following}
 	\label{fig:symbolic-scripting}
@@
 				\includegraphics[width=1\columnwidth]{img/gaussianbar.png}
-				\caption{Gaussian probability distribution for raw input value\\}
+				\caption{Raw input distribution}
 				\label{fig:gaussianbar}
@@
 				\includegraphics[width=1\columnwidth]{img/gaussianbarperm.png}
-				\caption{Probabilistic symbolic encoding suitable for HRR after permutation
-				}
+				\caption{Permuted distribution}
 				\label{fig:gaussianbarperm}
 			\end{subfigure}	
-		\caption{Sensory input encoding of a target objects position in the visual field at two successive points in time.
-Left graph shows original encodings for two adjacent values and right graph shows permuted encodings.
-It can be seen that semantically close input values result in similar HRR encodings.}
+		\caption{Sensory input at two successive points in time}
 		\label{fig:gaussian}
@@
 In the left column of figure \ref{fig:experiment}, the agent approaches the blue
-target (figure \ref{fig:experiment:agent1}). In the beginning (tick $-50$), the
+target (figure \ref{fig:experiment:agent1}). Following figure {fig:experiment:pos1} in the beginning (tick $-50$), the
 agent rotates right (default action) because the target is not visible.
@@
 including a new target.
-As the new target is placed outside of the agent's field of view, the default
+As seen in figure {fig:experiment:pos2} since the new target is placed outside of the agent's field of view, the default
 action of probing $no\_object$ is performed. The
@@
 	}%
-	\caption{Scene of Agent 1 (red) with three randomly placed items, the blue
-	one being the target object.
-	The green fan represents the visual field.}
+	\caption{Blue target visible}
 	\label{fig:experiment:agent1}
@@
 	}%
-	\caption{Scene of Agent 2 with three randomly placed items.
-	The agent does not have the target object in his field of view yet.}
+	\caption{Blue target not visible}
 	\label{fig:experiment:agent2}
@@
 	\includegraphics[width=.98\columnwidth]{img/3_139.pdf}
-	\caption{Symbolic sensing with the target in the visual field, which results in a scalar
-	value representing the target direction (${\sim}0.55$, almost straight
-	forward).}
+	\caption{Successful sensing}
 	\label{fig:experiment:sensor1}
@@
 	\includegraphics[width=.98\columnwidth]{img/3_235.pdf}
-	\caption{Symbolic sensing without the target in the visual field showing the
-	representation for the symbolic constant $no\_object$.\\}
+	\caption{Unsuccessful sensing}
 	\label{fig:experiment:sensor2}
@@
 	\includegraphics[width=.98\columnwidth]{img/1_139.pdf}
-	\caption{The targets position over time in the visual field of Agent 1.
-	At tick $-30$, the target enters the far right edge of the field of view and then gradually
-	shifts towards the center.}
+	\caption{Agent 1 run}
 	\label{fig:experiment:pos1}
@@
 	\includegraphics[width=.98\columnwidth]{img/1_235.pdf}
-	\caption{Agent 2 lost track of the target object (red background).
-	This is due to it having been reached, which prompts a new target creation, which is not in
-	the field of view.}
+	\caption{Agent 2 run}
 	\label{fig:experiment:pos2}
@@
 	\includegraphics[width=.98\columnwidth]{img/4_139.pdf}
-	\caption{Distance between Agent 1 and its target over time.
-	Here, the blue object in sub-figure \subref{fig:experiment:agent1} is being
-	approached.}
+	\caption{Distance Agent 1}
 	\label{fig:experiment:distance1}
@@
 	\includegraphics[width=.98\columnwidth]{img/4_235.pdf}
-	\caption{Distance between Agent 2 and its target over time.
-	At tick $-12$ a new target was created (black bar).}
+	\caption{Distance Agent 2}
 	\label{fig:experiment:distance2}
@@
 	\includegraphics[width=.98\columnwidth]{img/2_139.pdf}
-	\caption{Similarities of $left\_wheel$ and $right\_wheel$ to
-	the $forwards$ and $backwards$ actions respectively.
-	Here, Agent 1 approaches its target because $forwards$ has the
-	highest similarity for both wheels.}
+	\caption{Symbol similarity Agent 1}
 	\label{fig:experiment:similar1}
@@
 	\includegraphics[width=.98\columnwidth]{img/2_235.pdf}
-	\caption{Similarities as described in sub-figure \subref{fig:experiment:similar1}
-	for Agent 2. As no target is in the visual field, the default action for
-	the symbol $no\_object$ is performed (rotate right).\\}
+	\caption{Symbol similarity Agent 2}
 	\label{fig:experiment:similar2}
 \end{subfigure}
-\caption{Excerpts from our symbolic scripting experiment, controlling a
-Braitenberg vehicle with one linear sensor.
-The left column (sub-figures \protect\subref{fig:experiment:agent1},
-\protect\subref{fig:experiment:sensor1}, \protect\subref{fig:experiment:pos1},
-\protect\subref{fig:experiment:distance1} and
-\protect\subref{fig:experiment:similar1}) illustrates an agent approaching a
-target in its visual field.
-The right column (\protect\subref{fig:experiment:agent2},
-\protect\subref{fig:experiment:sensor2}, \protect\subref{fig:experiment:pos2},
-\protect\subref{fig:experiment:distance2},
-\protect\subref{fig:experiment:similar2}) shows an agent with currently no target in its
-visual field, rotating clockwise (\protect\subref{fig:experiment:similar2}) to
-find it.
-}
+\caption{Controlling a vehicle with one linear sensor.}
 \label{fig:experiment}

### 2017-02-24 papers/hrr-paper-neurotechnix/Example.tex
Made further corrections to paper.

@@
 
+	\newpage
+
 	\section{PROPERTIES OF HOLOGRAPHIC MEMORIES}
@@
 		\item The number of items stored in a single memory vector is not known based solely on it's content.
-		\item Existence of an item in memory cannot be checked explicitly.
+		\item The existence of an item in memory cannot be checked explicitly.
 The closest equivalent is to probe the memory for the item of interest and to compare the similarity of the decoded result to anything meaningful.
@@
 Results are shown in figure \ref{fig:capacity}.
-
 As we can see, a $512$ element vector starts decreasing accuracy of recall after $10$ pairs stored in a single memory block.
@@
 The value $0$ represents the far left corner of the sensor, and $1$ the far right one.
-The chart can be viewed as a (normalized) probability of light being at a certain position, and both cases show it being somewhere right of the center.
+The chart can be viewed as a probability of light being at a certain position, and both cases show it being somewhere right of the center.
 Chart \ref{fig:gaussianbarperm} shows what the Gaussian distributions look like when they are permuted.
-This shape of theirs is then used as a symbol.
-Concretely, instead of encoding a random symbol for "light\_left" we encode a scalar representing the position of light along the visual field and bind it with the rest of the controller components.
+Instead of encoding a random symbol for "light\_left" we encode a scalar representing the position of light along the visual field and bind it with the rest of the controller components.
 Accordingly, when running the experiment, once the light reaches a position encoded in the controller it will issue new commands to the vehicle.
@@
 If the target is found, the holographic controller is probed with its view space
-position which, due to the similarity of scalars, yields results even for
-values that lie between the originally stored values and can consequently be
+position. This position yields results even for
+values that lie between the originally stored values due to the nature of scalar encoding and can consequently be
 probed with the symbols $left\_wheel$ and $right\_wheel$ to extract the symbolic
@@
 the target, constantly decreasing its distance
-(figure \ref{fig:experiment:distance1}).
-
-In the right column of figure \ref{fig:experiment}, the target is not yet
+(figure \ref{fig:experiment:distance1}). In the right column of figure \ref{fig:experiment}, the target is not yet
 in the visual field of the agent.

### 2017-08-01 ros_holographic/nodes/visual_memory_module.py
Added ROS Module. Refactored file hierarchy.

@@ -1,0 +1,71 @@
+#!/usr/bin/env python
+
+import rospy
+import sys
+from ros_holographic.srv import * 
+from vsa.hrr import HRR
+import numpy as np
+
+class HRR_Node: 
+
+  m = None
+
+  def handle_clear_memory(self, req):
+      self.m = None
+      return ClearMemoryResponse(True)
+      
+  def handle_new_object(self, req):
+      if not HRR.valid_range[0][0] < req.X < HRR.valid_range[0][1] or not HRR.valid_range[1][0] < req.X < HRR.valid_range[1][1]:
+	print "Coordinates outside valid range"
+	return NewObjectResponse(False)
+      if self.m is None:
+	self.m = HRR(req.Label) * (req.X, req.Y)
+      else:
+	self.m += HRR(req.Label) * (req.X, req.Y)
+      return NewObjectResponse(True)
+
+  def handle_coordinate_probe(self, req):
+      if not HRR.valid_range[0][0] < req.X < HRR.valid_range[0][1] or not HRR.valid_range[1][0] < req.X < HRR.valid_range[1][1]:
+	print "Coordinates outside valid range"
+	return ProbeCoordinateResponse(False, None)
+      elif self.m is None:
+	print "Memory is empty"
+	return ProbeCoordinateResponse(False, None)
+      d = self.m / (req.X, req.Y)
+      l = []
+      for s, v in d:
+	if v >= HRR.distance_threshold:
+	  l.append(s)
+      return ProbeCoordinateResponse(True, l)
+
+  def handle_label_probe(self, req):
+      if self.m is None:
+	print "Memory is empty"
+	return ProbeLabelResponse(False, None)
+      out = self.m % req.Label
+      d = out.decodeCoordinate(dim=2, return_list=True)
+      l1 = []
+      l2 = []
+      for s, v in d:
+	if v == 1:
+	  l1.append(s[0])
+	  l2.append(s[1])
+      return ProbeLabelResponse(True, l1, l2)
+    
+  def visual_scene_memory_server(self):
+      rospy.init_node('visual_scene_memory_server')
+      s0 = rospy.Service('clear_memory', ClearMemory, self.handle_clear_memory)
+      s1 = rospy.Service('new_object', NewObject, self.handle_new_object)
+      s2 = rospy.Service('probe_coordinate', ProbeCoordinate, self.handle_coordinate_probe)
[…]

### 2017-08-01 ros_holographic/setup.py

@@ -1,0 +1,22 @@
+"""
+VSA package
+"""
+
+# Always prefer setuptools over distutils
+from setuptools import setup, find_packages
+# To use a consistent encoding
+from codecs import open
+from os import path
+
+here = path.abspath(path.dirname(__file__))
+
+setup(
+    name = "ros_holographic",
+    version = "0.0.1",
+    description = ("HRR ROS package"),
+    keywords = "ROS HRR",
+    packages=find_packages(exclude=['contrib', 'docs', 'tests']),
+    # Choose your license
+    license='FZI',
+    install_requires=['numpy']
+)

### 2017-08-01 vsa/setup.py

@@ -1,0 +1,24 @@
+"""
+VSA package
+"""
+
+# Always prefer setuptools over distutils
+from setuptools import setup, find_packages
+# To use a consistent encoding
+from codecs import open
+from os import path
+
+here = path.abspath(path.dirname(__file__))
+
+setup(
+    name = "vsa",
+    version = "0.0.1",
+    author = "Alexandru Lesi",
+    author_email = "lesi@fzi.de",
+    description = ("VSA and HRR package"),
+    keywords = "VSA HRR",
+    packages=find_packages(exclude=['contrib', 'docs', 'tests']),
+    # Choose your license
+    license='FZI',
+    install_requires=['numpy']
+)

### 2017-08-01 papers/hrr-paper-neurotechnix/Example.tex

@@
 All returned objects are then compared to the agent's target object.
-If the target is found, the holographic controller is probed with its view space
+If the target is found, the holographic controller is probed with the targets
 position. This position yields results even for
@@
 In the left column of figure \ref{fig:experiment}, the agent approaches the blue
-target (figure \ref{fig:experiment:agent1}). Following figure {fig:experiment:pos1} in the beginning (tick $-50$), the
+target (figure \ref{fig:experiment:agent1}). Following figure \ref{fig:experiment:pos1} in the beginning (tick $-50$), the
 agent rotates right (default action) because the target is not visible.
@@
 including a new target.
-As seen in figure {fig:experiment:pos2} since the new target is placed outside of the agent's field of view, the default
+As seen in figure \ref{fig:experiment:pos2}, since the new target is placed outside of the agent's field of view, the default
 action of probing $no\_object$ is performed. The
 clockwise rotation can also be seen in figure \ref{fig:experiment:similar2}).
+
 Regardless of how many times the agent reaches its target it will continue to find and pursue new ones solely with the help of its symbolic controller.
-
 This experiment shows the effectiveness of our approach in a practical
@@
 In other words, time needed for encoding/decoding is completely independent of the total number of symbols memorized.\\
-	A concrete biophysical evidence and theoretical model of implementation of convolution in the brain is, unfortunately, still missing.
-Nevertheless, our work assumes convolution as the basic computational substrate of higher level cognition and identifies random permutation as computational requirement without which association of probabilistically encoded symbols is not possible.
+	While concrete biophysical evidence and a theoretical model of convolution in the brain is not yet available our work assumes convolution as the basic computational substrate of higher level cognition and identifies random permutation as a solution for a computational requirement without which association of probabilistically encoded symbols is not possible.
 
